### 2020-02-24 infiniteci.tex
Initial Overleaf Import

\documentclass{article}

\usepackage{arxiv}
\usepackage{natbib}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true, citecolor = blue]{hyperref}      % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx, subfigure}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{import}
\usepackage{enumitem}
\usepackage{csquotes}
\usepackage{todonotes}
\usepackage{xfrac}

%%% ============================================================================
%%% Theorems.
%%% ============================================================================
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\theoremstyle{plain}
\newtheorem{lem}{\protect\lemmaname}
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}
\theoremstyle{definition}
\newtheorem{example}[thm]{\protect\examplename}
\theoremstyle{plain}
\newtheorem{cor}[thm]{\protect\corollaryname}
\theoremstyle{plain}
\newtheorem{prop}[thm]{\protect\propositionname}
\theoremstyle{definition}
\newtheorem{xca}[thm]{\protect\exercisename}
\ifx\proof\undefined
\newenvironment{proof}[1][\protect\proofname]{\par
	\normalfont\topsep6\p@\@plus6\p@\relax
	\trivlist
	\itemindent\parindent
	\item[\hskip\labelsep\scshape #1]\ignorespaces
}{%
	\endtrivlist\@endpefalse
}
\providecommand{\proofname}{Proof}
\fi

\providecommand{\corollaryname}{Corollary}
\providecommand{\definitionname}{Definition}
\providecommand{\propositionname}{Proposition}
\providecommand{\examplename}{Example}
\providecommand{\exercisename}{Exercise}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}
\providecommand{\lemmaname}{Lemma}

%%% ============================================================================
%%% Macros.
%%% ============================================================================
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\Cor}{Cor}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\diag}{diag}

\DeclareMathOperator{\argmax}{argmax}
\newcommand{\geomean}{NA}

\title{Please avoid the standardized alpha}

\author{
  Jonas Moss \\
  Department of Mathematics, University of Oslo\\
  PB 1053, Blindern, NO-0316, Oslo, Norway \\
  \it{jonasmgj@math.uio.no}
}

\begin{document}
\maketitle
\begin{abstract}
Meta-analysis is the quantitative combination of results from different studies. The assumptions of classical meta-analysis models are not satisfied whenever publication bias is present, which causes inconsistent parameter estimates. A popular method to account for publication bias in meta-analysis is the selection function model, but it has been noted that frequentist estimation of this model is problematic. This paper shows there is no confidence set of guaranteed finite diameter for the mean and heterogeneity parameters in the selection function model where the selection function is a step function. The proof is based on a generalization of the Gleser-Hwang theorem.
\end{abstract}

\section{Introduction}

Meta-analysis is the quantitative combination of results from different studies \citep{lipsey2001practical} with the goal of reducing sampling error.
Publication bias occurs when the published research literature is
not representative of the all the research that has actually been
done \citep{rothstein2006publication}. An important case of publication
bias is when publication decisions are made based on \emph{p}-values
\citep{sterling1959publication}, which (and its sister phenomenon, \emph{p}-hacking \citep{simmons2011false})
can cause seriously biased conclusions when not accounted
for \citep{simmons2011false,moss2019modelling}.

One of the most important models for meta-analysis is the normal random effects
model with normal likelihoods where the
standard deviations are assumed to be known \citep{hedges1998fixed}.
The likelihood for an observation in this model is $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$,
where $\phi(x\mid\mu,\sigma)$ is the normal density with
mean $\mu$ and standard deviation $\sigma$. The parameter $\tau$ is the standard deviation of the random effects distribution, and is known as the heterogeneity parameter, while $\sigma_i$ are the study specific standard errors and $\theta_0$ is the mean of the effect size distribution. A modification of the random
effects meta-analysis model essentially due to \citet{hedges1984estimation}
allows us to account for \emph{p}-value based publication bias.

Let $u=\Phi(-x_{i}/\sigma_{i})$ be the standard one-sided
\emph{p}-value for the null hypothesis $\theta_{i}=0$, and $w(u)$
a probability for each $u$. The selection function meta-analysis
model \citep{hedges1984estimation,hedges1992modeling} based on
the\emph{ p}-value $u$ is
\begin{equation}
f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})\propto\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u)\label{eq:Publication bias model}
\end{equation}
The model is also known as the weighting function publication bias
model. Here is an interpretation of it:
\begin{quote}
Alice is an editor who receives a study with \emph{p}-value $u$.
Her publication decision is a random function of this \emph{p}-value. That is, 
she will publish the study with some probability $w(u)$.
Every study you will ever read in Alice's journal has survived this
selection mechanism, the rest are lost forever.
\end{quote}
This is a rejection sampling \citep{von1951various,flury1990acceptance}
procedure. The publication probability function is likely to be well
approximated by a step function, with cutoffs such as $0.01,0.025$
and $0.05$ being especially important. To model this, let $\alpha$
be a vector with $0=\alpha_{0}<\alpha_{1}<\cdots<\alpha_{J}=1$ and
$\rho$ be a non-negative vector in $[0,1]^{J}$ with $\rho_{1}=1$.
Now define $w(u\mid\rho,\alpha)=\sum_{j=1}^{J}\rho_{j}1_{(\alpha_{j-1},\alpha_{j}]}(u)$.
This is a step function where the value of $w$ on each step $(\alpha_{j-1},\alpha_{j}]$
is the probability of acceptance for a study with a\emph{ p}-value
$u$ falling inside the interval $(\alpha_{j-1},\alpha_{j}]$. I will
call the density proportional to $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u;\rho,\alpha)$
the step function publication bias model and denote it $f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$.

The step function publication bias model was first used by \citet{hedges1984estimation},
who used an $F$ distribution instead of a the normal distribution
and a single step in $w(u\mid\rho,\alpha)$. \citet{iyengar1988selection}
studied other choices of $w$ while \citet{citkowicz2017parsimonious}
used a beta density publication probability function instead of a
step function. \citet{hedges1992modeling} is an accessible paper
about the model.

Frequentist estimation of the step function publication bias model
is problematic, as noted by for instance \citet[appendix, 1]{mcshane2016adjusting}.
The purpose of this paper is to formalize and prove exactly how bad frequentist estimation of this model can be. I do this by proving there are no confidence sets of guaranteed finite diameter for the mean parameter $\theta_{0}$
and the heterogeneity parameter $\tau$ for any coverage $1-\alpha$.
This is a problematic result for two reasons: (i) It would be hopeless
to report confidence sets for $\tau^{2}$ like $[0.5,\infty)$,
as they have no practical value. (2) It shows that the automatic confidence
sets procedures that are guaranteed to yield finite confidence sets
of some positive nominal coverage, such as bootstrapped confidence
sets, likelihood-ratio based confidence sets, and subsampling confidence
sets never have true coverage greater than $0$ \citep[see][]{gleser996bootstrap}.

The main result of this paper is the following theorem.
\begin{thm}
\label{prop:p-hacking infinite confidence interval}Let $h(x)=\prod_{i=1}^{n}f(x_{i}\mid\theta_{0},\tau,\sigma_{i})$
be the density of a $n$ independent observations from a step function
publication bias model. Then $h$ has no almost surely finite diameter
confidence set for $\left|\theta\right|$ or $\sigma$ of non-zero
coverage.
\end{thm}

\section{Definitions and Proofs}

Let $P_{\theta},\theta\in\Theta$ be a family of dominated probability
measures with densities $p_{\theta}$. Let $g:\Theta\to E$ for some
set $E$ equipped with a positive function $\left\Vert \cdot\right\Vert :E\to[0,\infty)$.
Here $g$ maps $\theta$ to the parameter we wish to form a confidence
set for. The function $\left\Vert \cdot\right\Vert $ is a distance
measure and could be a norm if $E$ is a vector space. Below it is the
absolute value $\left|\cdot\right|$. A random set $C$ is a confidence
set for $g(\theta)$ with coverage probability $1-\alpha$
if $P_{\theta}(g(\theta)\in C)\geq1-\alpha$
for all $\theta$. An\emph{ }acceptance set with level $\alpha$ has
the property than $P_{\theta}(A_{g(\theta)})\geq1-\alpha$.
There is a well known duality between confidence sets and acceptance
sets: For each confidence set $C$ there is a collection of acceptance
sets $A_{g(\theta)}$ satisfying $\omega\in A_{g(\theta)}\iff g(\theta)\in C(\omega)$.
The classical reference for these concepts is \citep[chapter 3.5]{lehmann2006testing}.

We will need terminology for the diameter of the confidence set according
to the function $\left\Vert \cdot\right\Vert $. The diameter is
a random variable, $D=\textrm{sup}_{\eta\in C}\left\Vert \eta\right\Vert $.
A confidence set has infinite diameter at $\theta$ with positive
probability if $P_{\theta}(D=\infty)>0$. If $P_{\theta}(D=\infty)>0$
for all $\theta$, we will say that $D$ has infinite diameter with
positive probability.

The main ingredient in the proof of Theorem \ref{prop:p-hacking infinite confidence interval}
is Theorem \ref{thm:Infinite diameter main theorem}, an extension
and reformulation of the Gleser-Hwang theorem \citep{gleser1987nonexistence},
a result they used to prove the non-existence of confidence sets with
guaranteed finite diameter for models such as the errors-in-variables
regression model and Fieller's ratio of means problem. \citet[theorem 1]{berger1999integrated}
is a similar extension of the Gleser-Hwang theorem.

The problem with non-existence
of confidence sets with guaranteed finite diameter for finite-dimensional
parameters has not received much attention in the statistical literature,
as lamented by \citet{gleser996bootstrap}. Some references in this
area are \citet{bahadur1956nonexistence}, who studied infinitely
large confidence sets in non-parametric estimation of the mean, \citeauthor{romano2004non}'s
(2004) extension of their results, \citet{Donoho1988-hg} and \citet{Pfanzagl1998-fe}.
\begin{lem}
Let $C$ be a confidence set and $A_{g(\theta)}$ its associated
acceptance sets. If there exists a sequence $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$
with $\left\Vert g(\theta_{n})\right\Vert \to\infty$ such
that $\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0,$then
the diameter of $C$ at $\theta$ is infinite with positive probability.
\end{lem}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$
for each $n$; such a sequence can always be found by appropriately
filtering the original $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$.
Since $\left\{ D\geq n\right\} $ is a decreasing sequence of sets,
$P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)$
for each $\theta$. From $A_{g(\theta_{n})}\subseteq\left\{ D\geq n\right\} $
it follows that $P_{\theta}(A_{g(\theta_{n})})\leq P_{\theta}(D\geq n)$,
thus $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)\geq\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0$.
\end{proof}
This is the extension of the Gleser-Hwang theorem.
\begin{thm}
\label{thm:Infinite diameter main theorem}If there exists a sequence
$\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$ with $\left\Vert g(\theta_{i})\right\Vert \to\infty$
such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\textrm{supp}p_{\theta}=\textrm{supp}f^{\star}$
for each $\theta$, then every confidence set with coverage $1-\alpha>0$
has infinite diameter with positive probability.
\end{thm}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$.
By a variant of the dominated convergence theorem \citep[exercise 16.4a]{billingsley1995probability},$\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\} $,
$1-\alpha\leq\int_{A_{g(\theta_{n})}}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
for all $n$, thus $\int_{D=\infty}f^{\star}d\mu>1-\alpha>0$. The
result follows from $P_{\theta}(D\geq n)=\int_{D\geq n}(p_{\theta}/p_{\theta_{n}})p_{\theta_{n}}d\mu>\int_{D=\infty}(p_{\theta}/f^{\star})f^{\star}d\mu>0$.
\end{proof}
This an extension of Theorem \ref{thm:Infinite diameter main theorem}
to mixture distributions.
\begin{prop}
\label{cor:Mixture model corollary}Let $f_{\theta}^{1},f_{\theta}^{2},\ldots$
be a finite or infinite sequence of densities, $\pi(\theta)$
a countable probability vector and $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
a mixture distribution. Assume there is a sequence $\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$
with $\left\Vert g(\theta_{i})\right\Vert \to\infty$ such
that $f_{\theta_{i}}^{1}\to f^{\star}$ pointwise and $\textrm{supp}f_{\theta}^{1} = \textrm{supp}f^{\star}$
for each $\theta$ . If there is a parameter $\theta'\in\Theta$ satisfying
$\pi_{1}(\theta')>\alpha$, the mixture $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
admits no almost surely finite diameter confidence set of coverage
$1-\alpha$ for $g(\theta)$.
\end{prop}

\begin{proof}
Let $C$ be confidence set for $g(\theta)$ with coverage
$1-\alpha$. Since $\pi_{1}(\theta')>\alpha$ by assumption,
$C$ must include a confidence $C_{1}$ for $f_{\theta}^{1}$ of some
positive coverage. But by Theorem \ref{thm:Infinite diameter main theorem},
$C_{1}$ has infinite diameter with positive probability for all $\theta$.
Since $C\supseteq C_{1}$, $C$ has infinite diameter with positive
probability too.
\end{proof}
The following lemma is a proof of proposition \ref{prop:p-hacking infinite confidence interval}
for the special case when no non-significant studies are published.
Let $\phi_{[a,b)}(x\mid\theta,\sigma)$ denote
the density of a normal variable with mean $\theta$ and standard
deviation $\sigma$ truncated to $[a,b)$.
\begin{lem}
\label{lem:One-sided normal limit}Let $f$ be a normal density truncated
to $[c,\infty)$ with underlying mean $\theta_{n}=-n-c$
and standard deviation $\sigma_{n}=n^{1/2}$. Then $\phi_{[c,\infty)}(x\mid\theta_{n},\sigma_{n})$
converges pointwise to $\exp(-x-c)$, the density of a
shifted exponential.
\end{lem}

\begin{proof}
The formula for $\phi_{[c,\infty)}(x;\theta_{n},\sigma_{n})$
is $\Phi(-\frac{n+c}{n^{1/2}})^{-1}\phi(x;-n-c,n^{1/2})1_{x>c}$.
The normal density part equals 
\[
(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp\left(\frac{-n^{2}-2n(c+x)+[2cx-c^{2}-x^{2}]}{2n}\right)
\]
When $n$ is large compared to $x$ and $c$, $[2cx-c^{2}-x^{2}]/2n$
is negligible, hence 
\[
\phi(x;\theta_{n},\sigma_{n})\approx(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp(-n/2)\exp(-x-c)
\]
which equals $\exp(-x-c)\phi(n^{1/2})/n^{1/2}$.
Since $\Phi(-(\theta_{n}+c)/\sigma_{n})=\Phi(n^{1/2})\approx n^{1/2}/\phi(n^{1/2})$
as $n$ grows (see e.g. \citet[equation 5]{borjesson1979simple}),
we end up with $$\Phi(-(\theta_{n}+c)/\sigma_{n})^{-1}\phi(x;\theta_{n},\sigma_{n})1_{x>c}\to\exp(-x-c)$$
\end{proof}
%
This lemma gives a mixture representation of the publication bias
model. The proof is omitted.
\begin{lem}
\label{prop:Mixture representation} The density of an observation
from the step function publication bias model with parameters $\theta_{0},\tau,\sigma_{i}$
is
\begin{equation}
f(x\mid\theta_{0},\tau,\sigma_{i})=\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\Phi^{-1}(1-\alpha_{j-1}))}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})\label{eq:Random effects, publication bias}
\end{equation}
where 
\[
\pi_{j}(\theta,\tau,\sigma_{i})=\rho_{j}\frac{\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})}{\sum_{j=1}^{J}\rho_{j}[\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]}
\]
\end{lem}

\begin{proof}[Proof of Theorem \ref{prop:p-hacking infinite confidence interval}]
Using the representation \ref{eq:Random effects, publication bias}
of lemma \ref{prop:Mixture representation} and \ref{cor:Mixture model corollary}
it is enough to show the result for $\phi_{[\Phi^{-1}(1-\alpha_{j}),\infty)}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})$
where $\alpha_{j+1}=1$. To this end, let $c=\Phi(1-\alpha_{j})$.
Then $\theta_{n}=-n-c$ and $\tau_{n}^{2}=n$ does the trick by lemma
\ref{lem:One-sided normal limit}. For the case with more than one
observation, observe that 
\[
\prod_{i=1}^{n}\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\infty)}(x_{i}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})
\]
is mixture model. (Just expand it.) The component belonging to the
mixture probability $\pi_{j}^{n}$ fulfills the demands of proposition
\ref{cor:Mixture model corollary} for $\alpha_{j}$ when $\alpha_{j+1}=1$,
as its density is a product of densities converging to shifted exponentials.
\end{proof}

\section*{Acknowledgements}
I am grateful to Riccardo De Bin and Emil Aas Stoltenberg for reading through the manuscript and giving helpful comments.

%\printbibliography

\bibliographystyle{apalike}
\bibliography{infiniteci}
\end{document}

### 2020-04-24 infiniteci.tex
:pear: Fixed title.
:fish: Changed layout.

@@
-\documentclass{article}
-
+\documentclass[twoside]{article}
 \usepackage{arxiv}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage[colorlinks=true, citecolor = blue]{hyperref}      % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx, subfigure}
-\usepackage{lipsum}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{import}
-\usepackage{enumitem}
-\usepackage{csquotes}
-\usepackage{todonotes}
-\usepackage{xfrac}
-
-%%% ============================================================================
-%%% Theorems.
-%%% ============================================================================
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}
-\theoremstyle{plain}
-\newtheorem{lem}{\protect\lemmaname}
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{\protect\definitionname}
-\theoremstyle{remark}
-\newtheorem{rem}[thm]{\protect\remarkname}
-\theoremstyle{definition}
-\newtheorem{example}[thm]{\protect\examplename}
-\theoremstyle{plain}
-\newtheorem{cor}[thm]{\protect\corollaryname}
-\theoremstyle{plain}
-\newtheorem{prop}[thm]{\protect\propositionname}
-\theoremstyle{definition}
-\newtheorem{xca}[thm]{\protect\exercisename}
-\ifx\proof\undefined
-\newenvironment{proof}[1][\protect\proofname]{\par
-	\normalfont\topsep6\p@\@plus6\p@\relax
-	\trivlist
-	\itemindent\parindent
-	\item[\hskip\labelsep\scshape #1]\ignorespaces
-}{%
-	\endtrivlist\@endpefalse
-}
-\providecommand{\proofname}{Proof}
-\fi
-
-\providecommand{\corollaryname}{Corollary}
-\providecommand{\definitionname}{Definition}
-\providecommand{\propositionname}{Proposition}
-\providecommand{\examplename}{Example}
-\providecommand{\exercisename}{Exercise}
-\providecommand{\remarkname}{Remark}
-\providecommand{\theoremname}{Theorem}
-\providecommand{\lemmaname}{Lemma}
+% \usepackage{natbib}
+% \usepackage[utf8]{inputenc} % allow utf-8 input
+% \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+% \usepackage[colorlinks=true, citecolor = blue]{hyperref}      % hyperlinks
+% \usepackage{url}            % simple URL typesetting
+% \usepackage{booktabs}       % professional-quality tables
+% \usepackage{amsfonts}       % blackboard math symbols
+% \usepackage{nicefrac}       % compact symbols for 1/2, etc.
+% \usepackage{microtype}      % microtypography
+% \usepackage{graphicx, subfigure}
+% \usepackage{lipsum}
+% \usepackage{amsmath}
+% \usepackage{amsthm}
+% \usepackage{amssymb}
+% \usepackage{import}
+% \usepackage{enumitem}
+% \usepackage{csquotes}
+% \usepackage{todonotes}
+% \usepackage{xfrac}
 
@@
 
-\title{Please avoid the standardized alpha}
+\title{Infinite diameter confidence sets in a model for publication bias}
 
 \author{
-  Jonas Moss \\
+  Jonas Moss \orcid{0000-0002-6876-6964} \\
   Department of Mathematics, University of Oslo\\
@@
 }
+
+\titletag{An arXiv preprint, v1.1}
+\makeatletter
+\titlerunning{\@title}
+\makeatother
+\authorrunning{Jonas Moss}
 
@@
 Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$.
-By a variant of the dominated convergence theorem \citep[exercise 16.4a]{billingsley1995probability},$\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
+By a variant of the dominated convergence theorem \citep[exercise 16.4a]{billingsley1995probability}, $\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
 Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\} $,
@@
 
-\bibliographystyle{apalike}
 \bibliography{infiniteci}

### 2020-04-24 infiniteci.tex
:fish: Added DOIs to references; using paperpile.

@@
 \usepackage{arxiv}
-% \usepackage{natbib}
-% \usepackage[utf8]{inputenc} % allow utf-8 input
-% \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-% \usepackage[colorlinks=true, citecolor = blue]{hyperref}      % hyperlinks
-% \usepackage{url}            % simple URL typesetting
-% \usepackage{booktabs}       % professional-quality tables
-% \usepackage{amsfonts}       % blackboard math symbols
-% \usepackage{nicefrac}       % compact symbols for 1/2, etc.
-% \usepackage{microtype}      % microtypography
-% \usepackage{graphicx, subfigure}
-% \usepackage{lipsum}
-% \usepackage{amsmath}
-% \usepackage{amsthm}
-% \usepackage{amssymb}
-% \usepackage{import}
-% \usepackage{enumitem}
-% \usepackage{csquotes}
-% \usepackage{todonotes}
-% \usepackage{xfrac}
 
@@
 \DeclareMathOperator{\diag}{diag} 
-
 \DeclareMathOperator{\argmax}{argmax}
-\newcommand{\geomean}{NA}
 
@@
 This paper shows there is no confidence set of guaranteed finite diameter for the mean and heterogeneity parameters in the selection function model where the selection function is a step function.
-The proof is based on a generalization of the Gleser-Hwang theorem.
+The proof is based on a generalization of the Gleser--Hwang theorem.
 \end{abstract}
@@
 done \citep{rothstein2006publication}. An important case of publication
-bias is when publication decisions are made based on \emph{p}-values
-\citep{sterling1959publication}, which (and its sister phenomenon, \emph{p}-hacking \citep{simmons2011false})
+bias is when publication decisions are made based on \textit{p}-values
+\citep{sterling1959publication}, which (and its sister phenomenon, \textit{p}-hacking \citep{simmons2011false})
 can cause seriously biased conclusions when not accounted
@@
 effects meta-analysis model essentially due to \citet{hedges1984estimation}
-allows us to account for \emph{p}-value based publication bias.
+allows us to account for \textit{p}-value based publication bias.
 
 Let $u=\Phi(-x_{i}/\sigma_{i})$ be the standard one-sided
-\emph{p}-value for the null hypothesis $\theta_{i}=0$, and $w(u)$
+\textit{p}-value for the null hypothesis $\theta_{i}=0$, and $w(u)$
 a probability for each $u$. The selection function meta-analysis
@@
 \begin{quote}
-Alice is an editor who receives a study with \emph{p}-value $u$.
-Her publication decision is a random function of this \emph{p}-value. That is, 
+Alice is an editor who receives a study with \textit{p}-value $u$.
+Her publication decision is a random function of this \textit{p}-value. That is, 
 she will publish the study with some probability $w(u)$.
@@
 Here $g$ maps $\theta$ to the parameter we wish to form a confidence
-set for. The function $\left\Vert \cdot\right\Vert $ is a distance
-measure and could be a norm if $E$ is a vector space. Below it is the
-absolute value $\left|\cdot\right|$. A random set $C$ is a confidence
-set for $g(\theta)$ with coverage probability $1-\alpha$
+set for, sometimes called a \textit{focus parameter} ((cite Nils)).
+For instance, $g(\theta) = \theta$ or $g(\theta) = E_\theta(X)$, the expectation of some random variable $X$ calculated under $P_\theta$.
+
+The function $\left\Vert \cdot\right\Vert$ measures the \textit{size} of each $e \in E$. It could be a norm if $E$ is a vector space, and below it is the
+absolute value $\left|\cdot\right|$.
+
+A random set $C$ is a confidence set for $g(\theta)$ with coverage probability $1-\alpha$
 if $P_{\theta}(g(\theta)\in C)\geq1-\alpha$
@@
 sets: For each confidence set $C$ there is a collection of acceptance
-sets $A_{g(\theta)}$ satisfying $\omega\in A_{g(\theta)}\iff g(\theta)\in C(\omega)$.
-The classical reference for these concepts is \citep[chapter 3.5]{lehmann2006testing}.
+sets $A_{g(\theta)}$ satisfying $\omega\in A_{g(\theta)}$ if and only if $g(\theta)\in C(\omega)$. The classical reference for these concepts is of \citet[chapter 3.5]{lehmann2006testing}
 
@@
 is Theorem \ref{thm:Infinite diameter main theorem}, an extension
-and reformulation of the Gleser-Hwang theorem \citep{gleser1987nonexistence},
-a result they used to prove the non-existence of confidence sets with
+and reformulation of the Gleser--Hwang theorem \citep{gleser1987nonexistence}. 
+They used their theorem o prove the non-existence of confidence sets with
 guaranteed finite diameter for models such as the errors-in-variables
-regression model and Fieller's ratio of means problem. \citet[theorem 1]{berger1999integrated}
-is a similar extension of the Gleser-Hwang theorem.
+regression model ((cite)) and Fieller's ratio of means problem ((cite)). \citet[theorem 1]{berger1999integrated}
+is a similar extension of the Gleser--Hwang theorem.
 
@@
 \end{proof}
-This is the extension of the Gleser-Hwang theorem.
+This is the extension of the Gleser--Hwang theorem.
 \begin{thm}
@@
 Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$.
-By a variant of the dominated convergence theorem \citep[exercise 16.4a]{billingsley1995probability}, $\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
-Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\} $,
+By a variant of the dominated convergence theorem \citep[Exercise 16.4a]{billingsley1995probability}, $\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
+Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\}$, we have 
 $1-\alpha\leq\int_{A_{g(\theta_{n})}}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
@@
 Since $\Phi(-(\theta_{n}+c)/\sigma_{n})=\Phi(n^{1/2})\approx n^{1/2}/\phi(n^{1/2})$
-as $n$ grows (see e.g. \citet[equation 5]{borjesson1979simple}),
+as $n$ grows \citep[equation 5]{borjesson1979simple},
 we end up with $$\Phi(-(\theta_{n}+c)/\sigma_{n})^{-1}\phi(x;\theta_{n},\sigma_{n})1_{x>c}\to\exp(-x-c)$$
@@
 \begin{equation}
-f(x\mid\theta_{0},\tau,\sigma_{i})=\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\Phi^{-1}(1-\alpha_{j-1}))}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})\label{eq:Random effects, publication bias}
+f(x\mid\theta_{0},\tau,\sigma_{i})=\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\Phi^{-1}(1-\alpha_{j-1}))}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})\label{eq:Random effects publication bias}
 \end{equation}
@@
 \[
-\pi_{j}(\theta,\tau,\sigma_{i})=\rho_{j}\frac{\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})}{\sum_{j=1}^{J}\rho_{j}[\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]}
+\pi_{j}(\theta,\tau,\sigma_{i})=\rho_{j}\frac{\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})}{\sum_{j=1}^{J}\rho_{j}[\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]}.
 \]
@@
 \begin{proof}[Proof of Theorem \ref{prop:p-hacking infinite confidence interval}]
-Using the representation \ref{eq:Random effects, publication bias}
-of lemma \ref{prop:Mixture representation} and \ref{cor:Mixture model corollary}
+Using the representation of \cref{eq:Random effects publication bias}
+of Lemma \ref{prop:Mixture representation} and Corollary \ref{cor:Mixture model corollary}, 
 it is enough to show the result for $\phi_{[\Phi^{-1}(1-\alpha_{j}),\infty)}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})$

### 2020-04-24 infiniteci.tex
:pear: Some small changes.

@@
 
-\title{Infinite diameter confidence sets in a model for publication bias}
+\title{Infinite diameter confidence sets in the selection function model for publication bias}
 
@@
 
-\titletag{An arXiv preprint, v1.1}
+\titletag{An arXiv preprint, v2}
 \makeatletter
@@
 The assumptions of classical meta-analysis models are not satisfied whenever publication bias is present, which causes inconsistent parameter estimates.
-A popular method to account for publication bias in meta-analysis is the selection function model, but it has been noted that frequentist estimation of this model is problematic.
-This paper shows there is no confidence set of guaranteed finite diameter for the mean and heterogeneity parameters in the selection function model where the selection function is a step function.
+A popular method to account for publication bias in meta-analysis is the selection function model, but frequentist estimation of this model is problematic.
+This paper shows there is no confidence set of guaranteed finite diameter for the mean and heterogeneity parameters in the selection function model.
 The proof is based on a generalization of the Gleser--Hwang theorem.
@@
 
+\keywords{meta-analysis \and publication bias \and selection function model \and p-hacking}
+
 \section{Introduction}
 
-Meta-analysis is the quantitative combination of results from different studies \citep{lipsey2001practical} with the goal of reducing sampling error.
+Meta-analysis is the quantitative combination of results from different studies with the goal of reducing sampling error \citep{lipsey2001practical}.
 Publication bias occurs when the published research literature is
@@
 bias is when publication decisions are made based on \textit{p}-values
-\citep{sterling1959publication}, which (and its sister phenomenon, \textit{p}-hacking \citep{simmons2011false})
+\citep{sterling1959publication}, which, along its sister phenomenon \textit{p}-hacking \citep{simmons2011false},
 can cause seriously biased conclusions when not accounted
@@
 mean $\mu$ and standard deviation $\sigma$.
-The parameter $\tau$ is the standard deviation of the random effects distribution, and is known as the heterogeneity parameter, while $\sigma_i$ are the study specific standard errors and $\theta_0$ is the mean of the effect size distribution.
-A modification of the random
-effects meta-analysis model essentially due to \citet{hedges1984estimation}
+The parameter $\tau$ is the standard deviation of the random effects distribution, known as the heterogeneity parameter.
+The $\sigma_i$s are the study-specific standard errors, and $\theta_0$ is the mean of the effect size distribution.
+A modification of the random effects meta-analysis model due to \citet{hedges1984estimation}
 allows us to account for \textit{p}-value based publication bias.
@@
 Frequentist estimation of the step function publication bias model
-is problematic, as noted by for instance \citet[appendix, 1]{mcshane2016adjusting}.
+is problematic, as noted by \citet[Appendix, 1]{mcshane2016adjusting}.
 The purpose of this paper is to formalize and prove exactly how bad frequentist estimation of this model can be.
@@
 to report confidence sets for $\tau^{2}$ like $[0.5,\infty)$,
-as they have no practical value. (2) It shows that the automatic confidence
+as they have no practical value. (ii) It shows that the automatic confidence
 sets procedures that are guaranteed to yield finite confidence sets
@@
 \section{Definitions and Proofs}
-
 Let $P_{\theta},\theta\in\Theta$ be a family of dominated probability
@@
 \end{proof}
-This an extension of Theorem \ref{thm:Infinite diameter main theorem}
+This is an extension of Theorem \ref{thm:Infinite diameter main theorem}
 to mixture distributions.

### 2020-04-24 infiniteci.tex
:apple: Some changes.

@@
 \DeclareMathOperator{\argmax}{argmax}
+\DeclareMathOperator{\supp}{supp}
 
@@
 \end{proof}
-This is the extension of the Gleser--Hwang theorem.
+This is the extension of the Gleser--Hwang theorem. Here $\supp f = \{x\mid f(x) \neq 0\}$ denotes the support of $f$.
 \begin{thm}
@@
 $\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$ with $\left\Vert g(\theta_{i})\right\Vert \to\infty$
-such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\textrm{supp}p_{\theta}=\textrm{supp}f^{\star}$
+such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\supp p_{\theta}=\supp f^{\star}$
 for each $\theta$, then every confidence set with coverage $1-\alpha>0$
@@
 with $\left\Vert g(\theta_{i})\right\Vert \to\infty$ such
-that $f_{\theta_{i}}^{1}\to f^{\star}$ pointwise and $\textrm{supp}f_{\theta}^{1} = \textrm{supp}f^{\star}$
+that $f_{\theta_{i}}^{1}\to f^{\star}$ pointwise and $\supp f_{\theta}^{1} = \supp f^{\star}$
 for each $\theta$ . If there is a parameter $\theta'\in\Theta$ satisfying

### 2020-07-01 infiniteci.tex
:pear: Update.

@@
 
-\title{Infinite diameter confidence sets in the selection function model for publication bias}
+\title{Infinite diameter confidence sets in Hedges' publication bias model}
 
@@
 The assumptions of classical meta-analysis models are not satisfied whenever publication bias is present, which causes inconsistent parameter estimates.
-A popular method to account for publication bias in meta-analysis is the selection function model, but frequentist estimation of this model is problematic.
+A popular method to account for publication bias in meta-analysis is Hedges' selection function model, but frequentist estimation of this model is problematic.
 This paper shows there is no confidence set of guaranteed finite diameter for the mean and heterogeneity parameters in the selection function model.
@@
 
-\keywords{meta-analysis \and publication bias \and selection function model \and p-hacking}
+\keywords{meta-analysis \and publication bias \and selection function model \and p-hacking \and selection models \and random effects models \and weight function models}
 
 \section{Introduction}
-
 Meta-analysis is the quantitative combination of results from different studies with the goal of reducing sampling error \citep{lipsey2001practical}. 
@@
 not representative of the all the research that has actually been
-done \citep{rothstein2006publication}. An important case of publication
+done \citep{Rothstein2006-cq}. An important case of publication
 bias is when publication decisions are made based on \textit{p}-values
@@
 
-One of the most important models for meta-analysis is the normal random effects
-model with normal likelihoods where the
-standard deviations are assumed to be known \citep{hedges1998fixed}.
+The most important model for meta-analysis is the normal random effects
+model with normal likelihoods \citep{hedges1998fixed}.
 The likelihood for an observation in this model is $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$,
@@
 mean $\mu$ and standard deviation $\sigma$.
-The parameter $\tau$ is the standard deviation of the random effects distribution, known as the heterogeneity parameter.
-The $\sigma_i$s are the study-specific standard errors, and $\theta_0$ is the mean of the effect size distribution.
+The parameter $\tau$ is the standard deviation of the random effects distribution, known as the \textit{heterogeneity parameter}.
+The $\sigma_i$s are the study-specific standard errors, assumed known, and $\theta_0$ is the mean of the effect size distribution.
+
 A modification of the random effects meta-analysis model due to \citet{hedges1984estimation}
-allows us to account for \textit{p}-value based publication bias.
-
-Let $u=\Phi(-x_{i}/\sigma_{i})$ be the standard one-sided
-\textit{p}-value for the null hypothesis $\theta_{i}=0$, and $w(u)$
-a probability for each $u$. The selection function meta-analysis
-model \citep{hedges1984estimation,hedges1992modeling} based on
-the\emph{ p}-value $u$ is
+allows us to account for \textit{p}-value based publication bias. Let $u=\Phi(-x_{i}/\sigma_{i})$ be the standard one-sided
+\textit{p}-value for the null hypothesis $\theta_{i}=0$, and $0\leq w(u)\leq 1$ be
+a probability for each $u$. The \textit{selection function meta-analysis
+model} \citep{hedges1984estimation,hedges1992modeling} based on
+the \emph{p}-value $u$ is
 \begin{equation}
@@
 \end{equation}
-The model is also known as the weighting function publication bias
-model. Here is an interpretation of it:
+The model is also known as the \textit{weighting function publication bias
+model}. The interpretation of this model is straightforward:
 \begin{quote}
@@
 Her publication decision is a random function of this \textit{p}-value. That is, 
-she will publish the study with some probability $w(u)$.
+she will publish the study with some probability $w(u)$ and reject it with probability $1-w(u)$.
 Every study you will ever read in Alice's journal has survived this
@@
 \end{quote}
-This is a rejection sampling \citep{von1951various,flury1990acceptance}
-procedure. The publication probability function is likely to be well
-approximated by a step function, with cutoffs such as $0.01,0.025$
-and $0.05$ being especially important. To model this, let $\alpha$
+
+This is a rejection sampling procedure \citep{von1951various,flury1990acceptance} where $\phi$ serves as a proposal distribution for $f$.
+((Too abrupt.)) The publication probability function is likely to be well approximated by a step function, with cutoffs such as $0.01,0.025$
+and $0.05$ being especially important. ((cite something)).
+
+To model this, let $\alpha$
 be a vector with $0=\alpha_{0}<\alpha_{1}<\cdots<\alpha_{J}=1$ and
 $\rho$ be a non-negative vector in $[0,1]^{J}$ with $\rho_{1}=1$.
-Now define $w(u\mid\rho,\alpha)=\sum_{j=1}^{J}\rho_{j}1_{(\alpha_{j-1},\alpha_{j}]}(u)$.
+Now define 
+\begin{equation}
+w(u\mid\rho,\alpha)=\sum_{j=1}^{J}\rho_{j}1_{(\alpha_{j-1},\alpha_{j}]}(u).
+\end{equation}
 This is a step function where the value of $w$ on each step $(\alpha_{j-1},\alpha_{j}]$
-is the probability of acceptance for a study with a\emph{ p}-value
-$u$ falling inside the interval $(\alpha_{j-1},\alpha_{j}]$. I will
-call the density proportional to $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u;\rho,\alpha)$
-the step function publication bias model and denote it $f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$.
+is the probability of acceptance for a study with a \textit{p}-value
+$u$ falling inside the interval $(\alpha_{j-1},\alpha_{j}]$.
+\citet{hedges1992modeling} discussed this variant of the selection function publication model, and we will refer to it as Hedges' publication bias model.
+%$\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u;\rho,\alpha)$ the step function publication bias model and denote it $f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$.
 
-The step function publication bias model was first used by \citet{hedges1984estimation},
+The selection function publication bias model is due to \citet{hedges1984estimation},
 who used an $F$ distribution instead of a the normal distribution
@@
 used a beta density publication probability function instead of a
-step function. \citet{hedges1992modeling} is an accessible paper
-about the model.
+step function.
 
 Frequentist estimation of the step function publication bias model
-is problematic, as noted by \citet[Appendix, 1]{mcshane2016adjusting}.
+is difficult, as noted by \citet[Appendix 1]{mcshane2016adjusting}.
+
+(( Add something about ridges in the likelihood, maybe a plot.))
 The purpose of this paper is to formalize and prove exactly how bad frequentist estimation of this model can be.
-I do this by proving there are no confidence sets of guaranteed finite diameter for the mean parameter $\theta_{0}$
+This is done by proving there are no confidence sets of guaranteed finite diameter for the mean parameter $\theta_{0}$
 and the heterogeneity parameter $\tau$ for any coverage $1-\alpha$.
-This is a problematic result for two reasons: (i) It would be hopeless
-to report confidence sets for $\tau^{2}$ like $[0.5,\infty)$,
-as they have no practical value. (ii) It shows that the automatic confidence
+This is a problematic result for two reasons. 
+\begin{enumerate}[label=(\roman*)]
+\item It would be hopeless to report confidence sets for $\tau^{2}$ like $[0.5,\infty)$, as they have no practical value. 
+\item It shows that the automatic confidence
 sets procedures that are guaranteed to yield finite confidence sets
@@
 sets never have true coverage greater than $0$ \citep[see][]{gleser996bootstrap}.
-
+\end{enumerate}
 The main result of this paper is the following theorem.
 \begin{thm}
-\label{prop:p-hacking infinite confidence interval}Let $h(x)=\prod_{i=1}^{n}f(x_{i}\mid\theta_{0},\tau,\sigma_{i})$
-be the density of a $n$ independent observations from a step function
-publication bias model. Then $h$ has no almost surely finite diameter
-confidence set for $\left|\theta\right|$ or $\sigma$ of non-zero
-coverage.
+\label{thm:p-hacking infinite confidence interval}Let $h(x)=\prod_{i=1}^{n}f(x_{i}\mid\theta_{0},\tau,\sigma_{i},\rho)$ be the density of $n$ independent observations from a publication bias model.
+Then $h$ has no almost surely finite diameter confidence set for $\theta$ or $\sigma$ of non-zero coverage.
 \end{thm}
 
-\section{Definitions and Proofs}
-Let $P_{\theta},\theta\in\Theta$ be a family of dominated probability
-measures with densities $p_{\theta}$. Let $g:\Theta\to E$ for some
-set $E$ equipped with a positive function $\left\Vert \cdot\right\Vert :E\to[0,\infty)$.
-Here $g$ maps $\theta$ to the parameter we wish to form a confidence
-set for, sometimes called a \textit{focus parameter} ((cite Nils)).
-For instance, $g(\theta) = \theta$ or $g(\theta) = E_\theta(X)$, the expectation of some random variable $X$ calculated under $P_\theta$.
-
-The function $\left\Vert \cdot\right\Vert$ measures the \textit{size} of each $e \in E$. It could be a norm if $E$ is a vector space, and below it is the
-absolute value $\left|\cdot\right|$.
-
-A random set $C$ is a confidence set for $g(\theta)$ with coverage probability $1-\alpha$
-if $P_{\theta}(g(\theta)\in C)\geq1-\alpha$
-for all $\theta$. An\emph{ }acceptance set with level $\alpha$ has
-the property than $P_{\theta}(A_{g(\theta)})\geq1-\alpha$.
-There is a well known duality between confidence sets and acceptance
-sets: For each confidence set $C$ there is a collection of acceptance
-sets $A_{g(\theta)}$ satisfying $\omega\in A_{g(\theta)}$ if and only if $g(\theta)\in C(\omega)$. The classical reference for these concepts is of \citet[chapter 3.5]{lehmann2006testing}
-
-We will need terminology for the diameter of the confidence set according
-to the function $\left\Vert \cdot\right\Vert $. The diameter is
-a random variable, $D=\textrm{sup}_{\eta\in C}\left\Vert \eta\right\Vert $.
-A confidence set has infinite diameter at $\theta$ with positive
-probability if $P_{\theta}(D=\infty)>0$. If $P_{\theta}(D=\infty)>0$
-for all $\theta$, we will say that $D$ has infinite diameter with
-positive probability.
-
-The main ingredient in the proof of Theorem \ref{prop:p-hacking infinite confidence interval}
-is Theorem \ref{thm:Infinite diameter main theorem}, an extension
+The main ingredient in the proof of \cref{thm:p-hacking infinite confidence interval}
+is \cref{thm:Infinite diameter main theorem}, an extension
 and reformulation of the Gleser--Hwang theorem \citep{gleser1987nonexistence}. 
-They used their theorem o prove the non-existence of confidence sets with
+They used their theorem to prove the non-existence of confidence sets with
 guaranteed finite diameter for models such as the errors-in-variables
-regression model ((cite)) and Fieller's ratio of means problem ((cite)). \citet[theorem 1]{berger1999integrated}
+regression model ((cite)) and Fieller's ratio of means problem ((cite)). Theorem 1 of \citet{berger1999integrated}
 is a similar extension of the Gleser--Hwang theorem.
@@
 (2004) extension of their results, \citet{Donoho1988-hg} and \citet{Pfanzagl1998-fe}.
+
+\section{Definitions and Proofs}
+Let $P_{\theta},\theta\in\Theta$ be a parameterized family of dominated probability
+measures with densities $p_{\theta}$. Let $g:\Theta\to E$ for some
+set $E$ equipped with a positive function $\left\Vert \cdot\right\Vert :E\to[0,\infty)$.
+Here $g$ maps $\theta$ to the parameter we wish to form a confidence
+set for, sometimes called a \textit{focus parameter} ((cite Nils)).
+For instance, $g(\theta) = \theta$ or $g(\theta) = E_\theta(X)$, the expectation of some random variable $X$ calculated under $P_\theta$.
+
+The function $\left\Vert \cdot\right\Vert$ measures the size of each $e \in E$.
+It could be a norm if $E$ is a vector space.
+In \cref{thm:Infinite diameter main theorem} it is the absolute value $\left|\cdot\right|$.
+
+Recall the definition of confidence sets. A set $C$ is a confidence set for $g(\theta)$ with coverage probability $1-\alpha$
+if $P_{\theta}(g(\theta)\in C)\geq1-\alpha$
+for all $\theta$.
+
+Let ${A[g(\theta)]}$ be a family of level $\alpha$ acceptance sets. An acceptance set for $C$ with level $\alpha$ has the property than $P_{\theta}(A[g(\theta)])\geq1-\alpha$.
+There is a well known duality between confidence sets and acceptance
+sets. For each confidence set $C$ there is a collection of acceptance
+sets $A[g(\theta)]$ satisfying $\omega\in A[g(\theta)]$ if and only if $g(\theta)\in C(\omega)$. The classical reference for these concepts is the book by \citet[Chapter 3.5]{lehmann2006testing}
+
+We will need terminology for the diameter of the confidence set according
+to the function $\left\Vert \cdot\right\Vert $. Define the diameter of $C$ as a random variable, $D=\textrm{sup}_{\eta\in C}\left\Vert \eta\right\Vert$.
+A confidence set has infinite diameter at $\theta$ with positive
+probability if $P_{\theta}(D=\infty)>0$. If $P_{\theta}(D=\infty)>0$
+for all $\theta$, we will say that $D$ has infinite diameter with
+positive probability.
+
 \begin{lem}
-Let $C$ be a confidence set and $A_{g(\theta)}$ its associated
+Let $C$ be a level $\alpha$ confidence set and $A[g(\theta)]$ its associated
 acceptance sets. If there exists a sequence $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$
 with $\left\Vert g(\theta_{n})\right\Vert \to\infty$ such
-that $\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0,$then
+that $\lim_{n\to\infty}P_{\theta}(A[g(\theta_{n})])>0,$then
 the diameter of $C$ at $\theta$ is infinite with positive probability.
@@
 $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)$
-for each $\theta$. From $A_{g(\theta_{n})}\subseteq\left\{ D\geq n\right\} $
-it follows that $P_{\theta}(A_{g(\theta_{n})})\leq P_{\theta}(D\geq n)$,
-thus $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)\geq\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0$.
+for each $\theta$. From $A[g(\theta_{n})]\subseteq\left\{ D\geq n\right\} $
+it follows that $P_{\theta}(A[g(\theta_{n})])\leq P_{\theta}(D\geq n)$,
+thus $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)\geq\lim_{n\to\infty}P_{\theta}(A[g(\theta_{n})])>0$.
 \end{proof}
@@
 $\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$ with $\left\Vert g(\theta_{i})\right\Vert \to\infty$
-such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\supp p_{\theta}=\supp f^{\star}$
-for each $\theta$, then every confidence set with coverage $1-\alpha>0$
+such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\supp p_{\theta_i}=\supp f^{\star}$
+for each $\theta_i$, then every confidence set with coverage $1-\alpha>0$
 has infinite diameter with positive probability.
@@
 By a variant of the dominated convergence theorem \citep[Exercise 16.4a]{billingsley1995probability}, $\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
-Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\}$, we have 
-$1-\alpha\leq\int_{A_{g(\theta_{n})}}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
+Since $A[g(\theta_{n})]\subseteq\left\{ D\leq n\right\}$, we have 
+$1-\alpha\leq\int_{A[g(\theta_{n})]}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
 for all $n$, thus $\int_{D=\infty}f^{\star}d\mu>1-\alpha>0$. The
@@
 \end{proof}
-This is an extension of Theorem \ref{thm:Infinite diameter main theorem}
+This is an extension of \cref{thm:Infinite diameter main theorem}
 to mixture distributions.
-\begin{prop}
+\begin{cor}
 \label{cor:Mixture model corollary}Let $f_{\theta}^{1},f_{\theta}^{2},\ldots$
@@
 $1-\alpha$ for $g(\theta)$.
-\end{prop}
+\end{cor}
 
@@
 $C$ must include a confidence $C_{1}$ for $f_{\theta}^{1}$ of some
-positive coverage. But by Theorem \ref{thm:Infinite diameter main theorem},
+positive coverage. But by \cref{thm:Infinite diameter main theorem},
 $C_{1}$ has infinite diameter with positive probability for all $\theta$.
@@
 \end{proof}
-The following lemma is a proof of proposition \ref{prop:p-hacking infinite confidence interval}
-for the special case when no non-significant studies are published.
-Let $\phi_{[a,b)}(x\mid\theta,\sigma)$ denote
-the density of a normal variable with mean $\theta$ and standard
-deviation $\sigma$ truncated to $[a,b)$.
+The following lemma is a proof of \cref{thm:p-hacking infinite confidence interval} for the special case when no non-significant studies are published.
+
+% Let $\phi_{[a,b)}(x\mid\theta,\sigma)$ denote the density of a normal variable with mean $\theta$ and standard deviation $\sigma$ truncated to $[a,b)$.
+
+\begin{lem} \label{lem:One-sided normal limit}
+Let $f_n$ be a normal density truncated to $[c,\infty)$ with underlying mean $\theta_{n}=-n+c$ and standard deviation $\sigma_{n}=n^{1/2}$.
+Then $f_n(x)$ converges pointwise to $\exp(-x+c)$, the density of a shifted exponential.
+\end{lem}
+\begin{proof}
+Using the well-known formula for the truncated normal we find that 
+\begin{align*}
+f_n(x) & = \phi(x; \theta_n, \sigma_n)\Phi\left(\frac{\theta_n - c}{\sigma_n}\right)^{-1}1[x>c], \\
+ & = \phi(x;-n+c,n^{1/2})\Phi(-n^{1/2})^{-1}1[x>c].
+\end{align*}
+The normal density part equals 
+\[
+(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp\left(\frac{-n^{2}-2n(x-c)+[2cx-c^{2}-x^{2}]}{2n}\right)
+\]
+When $n$ is large compared to $x$ and $c$, the term $(2cx-c^{2}-x^{2})/2n$
+is negligible, hence 
+\[
+\phi(x;-n+c,n^{1/2})\approx(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp(-n/2)\exp(-x+c)
+\]
+which equals $\exp(-x+c)\phi(n^{1/2})/n^{1/2}$.
+Since $\Phi(-n^{1/2})\approx \phi(n^{1/2})/n^{1/2}$
+as $n$ grows \citep[Equation 5]{borjesson1979simple},
+we end up with $$\Phi(n^{1/2})^{-1}\phi(x;-n-c,n^{1/2})1_{x>c}\to\exp(-x+c),$$
+the density of a shifted exponential.
+\end{proof}
+
+we will prove \cref{thm:p-hacking infinite confidence interval} by connecting \cref{cor:Mixture model corollary} about mixture distributions to \cref{lem:One-sided normal limit} above.
+To do this, we will need a mixture distribution representation of the publication bias model, which is given in the following lemma.
+We omit the proof as it is based purely on straight-forward calculations.
 \begin{lem}
-\label{lem:One-sided normal limit}Let $f$ be a normal density truncated
-to $[c,\infty)$ with underlying mean $\theta_{n}=-n-c$
-and standard deviation $\sigma_{n}=n^{1/2}$. Then $\phi_{[c,\infty)}(x\mid\theta_{n},\sigma_{n})$
-converges pointwise to $\exp(-x-c)$, the density of a
-shifted exponential.
+\label{lem:Mixture representation} The density of an observation
+from the publication bias model with parameter vector $(\theta_{0},\tau,\sigma_{i},\rho)$ can be written in a mixture form as
+\begin{equation}
+f(x;\theta_{0},\tau,\sigma_{i})=\sum_{j=1}^{N}\pi_{j}f_j(x;\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2}).\label{eq:Random effects publication bias}
+\end{equation}
+Here $f_j$ is a normal truncated to ${[\Phi^{-1}(1-\alpha_{j}),\Phi^{-1}(1-\alpha_{j-1}))}$. The mixture probabilities are
+\[
+\pi_{j}=\rho_{j}\frac{\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})}{\sum_{j=1}^{J}\rho_{j}[\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]},
+\]
+where $c_i = \Phi^{-1}(1-\alpha_{i})$.
 \end{lem}
 
-\begin{proof}
-The formula for $\phi_{[c,\infty)}(x;\theta_{n},\sigma_{n})$
-is $\Phi(-\frac{n+c}{n^{1/2}})^{-1}\phi(x;-n-c,n^{1/2})1_{x>c}$.
-The normal density part equals 
-\[
-(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp\left(\frac{-n^{2}-2n(c+x)+[2cx-c^{2}-x^{2}]}{2n}\right)
-\]
-When $n$ is large compared to $x$ and $c$, $[2cx-c^{2}-x^{2}]/2n$
-is negligible, hence 
-\[
-\phi(x;\theta_{n},\sigma_{n})\approx(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp(-n/2)\exp(-x-c)
-\]
-which equals $\exp(-x-c)\phi(n^{1/2})/n^{1/2}$.
-Since $\Phi(-(\theta_{n}+c)/\sigma_{n})=\Phi(n^{1/2})\approx n^{1/2}/\phi(n^{1/2})$
-as $n$ grows \citep[equation 5]{borjesson1979simple},
-we end up with $$\Phi(-(\theta_{n}+c)/\sigma_{n})^{-1}\phi(x;\theta_{n},\sigma_{n})1_{x>c}\to\exp(-x-c)$$
-\end{proof}
-%
-This lemma gives a mixture representation of the publication bias
-model. The proof is omitted.
-\begin{lem}
-\label{prop:Mixture representation} The density of an observation
-from the step function publication bias model with parameters $\theta_{0},\tau,\sigma_{i}$
-is
-\begin{equation}
-f(x\mid\theta_{0},\tau,\sigma_{i})=\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\Phi^{-1}(1-\alpha_{j-1}))}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})\label{eq:Random effects publication bias}
-\end{equation}
-where 
-\[
-\pi_{j}(\theta,\tau,\sigma_{i})=\rho_{j}\frac{\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})}{\sum_{j=1}^{J}\rho_{j}[\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]}.
-\]
-\end{lem}
+\begin{proof}[Proof of \cref{thm:p-hacking infinite confidence interval}]
+When $n=1$, the result follows by applying \cref{cor:Mixture model corollary} and \cref{lem:One-sided normal limit} to the mixture components $f_j(x;\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})$ of \cref{eq:Random effects publication bias}.
 
-\begin{proof}[Proof of Theorem \ref{prop:p-hacking infinite confidence interval}]
-Using the representation of \cref{eq:Random effects publication bias}
-of Lemma \ref{prop:Mixture representation} and Corollary \ref{cor:Mixture model corollary}, 
-it is enough to show the result for $\phi_{[\Phi^{-1}(1-\alpha_{j}),\infty)}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})$
-where $\alpha_{j+1}=1$. To this end, let $c=\Phi(1-\alpha_{j})$.
-Then $\theta_{n}=-n-c$ and $\tau_{n}^{2}=n$ does the trick by lemma
-\ref{lem:One-sided normal limit}. For the case with more than one
-observation, observe that 
+For the case with more than one observation, observe that 
 \[
@@
 \]
-is mixture model. (Just expand it.) The component belonging to the
-mixture probability $\pi_{j}^{n}$ fulfills the demands of proposition
-\ref{cor:Mixture model corollary} for $\alpha_{j}$ when $\alpha_{j+1}=1$,
-as its density is a product of densities converging to shifted exponentials.
+is mixture model, which can be verified by expanding the expression.
+The component belonging to the mixture probability $\pi_{j}^{n}$ fulfills the demands of Proposition \ref{cor:Mixture model corollary} for $\alpha_{j}$ when $\alpha_{j+1}=1$, as its density is a product of densities converging to shifted exponentials.
 \end{proof}

### 2020-07-02 R/graph.R
:pig2: Some work

@@ -1,0 +1,128 @@
+### ============================================================================
+### Sampling
+### ============================================================================
+
+set.seed(313)
+n = 300
+theta0 = 0
+tau = 0.1
+sigma = 1/sqrt(runif(n, 10, 80))
+eta = c(1, 0, 0)
+
+samples = publipha::rmpsnorm(
+  n = n, 
+  theta0 = theta0, 
+  tau = tau, 
+  sigma = sigma, 
+  eta = eta)
+
+### ============================================================================
+### Plotting
+### ============================================================================
+
+x = seq(10, 80)
+
+plot(
+  x = 1/sigma^2, 
+  y = samples, 
+  log = "x", 
+  xlab = expression(1/sigma),
+  ylab = "Effect size estimate"
+  )
+lines(x, 1.96/sqrt(x))
+
+### ============================================================================
+### Maximum likelihood estimation
+### ============================================================================
+
+objective = function(p) {
+  theta0 = p[1]
+  tau_sq = p[2]^2
+  sum(-publipha::dmpsnorm(
+    x = samples,
+    theta0 = theta0, 
+    tau = sqrt(tau_sq),
+    sigma = sigma,
+    eta = eta,
+    log = TRUE))
+}
+
+nlm(objective, p = c(1, 1))
+
+# objective2 = function(p) {
+#   theta0 = p[1]
+#   tau_sq = p[2]^2
+#   sum(-log(truncnorm::dtruncnorm(
+#     x = samples/sigma,
+#     a = qnorm(1 - 0.025),
+#     mean = theta0, 
+#     sd = sqrt(tau_sq + sigma^2))))
+# }
+
+#nlm(objective2, p = c(1, 1))
+
+### ============================================================================
+### Contour plot
+### ============================================================================
+
+X = seq(-60, 2, by = 1)
+Y = seq(0.01, 10, by = 1)
+FUN = Vectorize(function(theta0, tau) objective(c(theta0, tau)))
+Z = outer(X = X, Y = Y, FUN = FUN)
+
+
+contour(X, Y, Z)
+x = seq(from = -50, to = 0, by = 0.1)
[…]

### 2020-07-02 R/graph.R
:pig: Work.

@@ -3,7 +3,7 @@
 ### ============================================================================
 
 set.seed(313)
-n = 300
+n = 40
 theta0 = 0
 tau = 0.1
 sigma = 1/sqrt(runif(n, 10, 80))
@@ -65,15 +65,16 @@ nlm(objective, p = c(1, 1))
 ### Contour plot
 ### ============================================================================
 
-X = seq(-60, 2, by = 1)
-Y = seq(0.01, 10, by = 1)
+X = seq(-50, 0, by = 0.1)
+Y = seq(0.01, 10, by = 0.1)
 FUN = Vectorize(function(theta0, tau) objective(c(theta0, tau)))
 Z = outer(X = X, Y = Y, FUN = FUN)
 
 
-contour(X, Y, Z)
-x = seq(from = -50, to = 0, by = 0.1)
-lines(x, sqrt(abs(x)), lty = 2, lwd = 2)
+filled.contour(X, Y, -Z, xlab = expression(theta[0]), ylab = expression(tau),
+               cex.lab = sqrt(2), main = "Likelihood of publication bias model")
+#x = seq(from = -50, to = 0, by = 0.1)
+#lines(x, sqrt(abs(x)), lty = 2, lwd = 2)
 
 library("rgl")
 plot3d(X, Y, Z)

### 2020-07-30 R/graph.R
:pear: Work.

@@ -2,12 +2,12 @@
 ### Sampling
 ### ============================================================================
 
-set.seed(313)
-n = 40
+set.seed(20)
+n = 5
 theta0 = 0
 tau = 0.1
 sigma = 1/sqrt(runif(n, 10, 80))
-eta = c(1, 0, 0)
+eta = c(1, 0.5, 0.1)
 
 samples = publipha::rmpsnorm(
   n = n, 
@@ -15,6 +15,15 @@ samples = publipha::rmpsnorm(
   tau = tau, 
   sigma = sigma, 
   eta = eta)
+
+
+### ============================================================================
+### Estimating
+### ============================================================================
+
+effects = samples
+v = sigma^2
+weightr::weightfunct(effects, v, steps = c(0.025, 0.05, 1))
 
 ### ============================================================================
 ### Plotting

### 2020-07-31 R/cuddy.R
:+1:  Clean-up

@@ -1,0 +1,34 @@
+## This package is used for the cuddy data.
+#install.packages("publipha")
+
+cuddy2018 = publipha::dat.cuddy2018
+cuddy2018 = cuddy2018[cuddy2018$yi < 1.5, ] # removes outlier.
+
+eta = c(1, 0.6, 0.1)
+
+objective = function(p) {
+  theta0 = p[1]
+  tau_sq = p[2]^2
+  sum(-publipha::dmpsnorm(
+    x = sqrt(yi),
+    theta0 = theta0, 
+    tau = sqrt(tau_sq),
+    sigma = sqrt(vi),
+    eta = eta,
+    log = TRUE))
+}
+
+x = seq(-10, 0, by = 0.1)
+y = seq(0.01, 0.8, by = 0.1)
+FUN = Vectorize(function(theta0, tau) objective(c(theta0, tau)))
+z = outer(X = x, Y = y, FUN = FUN)
+
+pdf("chunks/cuddy.pdf")
+contour(
+  x = x, 
+  y = y, 
+  z = -z, 
+  xlab = expression(theta[0]), ylab = expression(tau),
+  cex.lab = sqrt(2), main = "Likelihood of Hedges' publication bias model"
+  )
+dev.off()  

### 2020-07-31 R/graph.R

@@ -1,138 +1,0 @@
-### ============================================================================
-### Sampling
-### ============================================================================
-
-set.seed(20)
-n = 5
-theta0 = 0
-tau = 0.1
-sigma = 1/sqrt(runif(n, 10, 80))
-eta = c(1, 0.5, 0.1)
-
-samples = publipha::rmpsnorm(
-  n = n, 
-  theta0 = theta0, 
-  tau = tau, 
-  sigma = sigma, 
-  eta = eta)
-
-
-### ============================================================================
-### Estimating
-### ============================================================================
-
-effects = samples
-v = sigma^2
-weightr::weightfunct(effects, v, steps = c(0.025, 0.05, 1))
-
-### ============================================================================
-### Plotting
-### ============================================================================
-
-x = seq(10, 80)
-
-plot(
-  x = 1/sigma^2, 
-  y = samples, 
-  log = "x", 
-  xlab = expression(1/sigma),
-  ylab = "Effect size estimate"
-  )
-lines(x, 1.96/sqrt(x))
-
-### ============================================================================
-### Maximum likelihood estimation
-### ============================================================================
-
-objective = function(p) {
-  theta0 = p[1]
-  tau_sq = p[2]^2
-  sum(-publipha::dmpsnorm(
-    x = samples,
-    theta0 = theta0, 
-    tau = sqrt(tau_sq),
-    sigma = sigma,
-    eta = eta,
-    log = TRUE))
-}
-
-nlm(objective, p = c(1, 1))
-
-# objective2 = function(p) {
-#   theta0 = p[1]
-#   tau_sq = p[2]^2
-#   sum(-log(truncnorm::dtruncnorm(
-#     x = samples/sigma,
-#     a = qnorm(1 - 0.025),
-#     mean = theta0, 
-#     sd = sqrt(tau_sq + sigma^2))))
-# }
-
-#nlm(objective2, p = c(1, 1))
-
-### ============================================================================
-### Contour plot
-### ============================================================================
-
-X = seq(-50, 0, by = 0.1)
[…]

### 2020-07-31 README.Rmd
:book: Added readme.

---
output:
  github_document:
    html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# Infinite diameter confidence sets in Hedges' publication bias model

Repository for the arXiv version of the paper [Infinite diameter confidence sets in Hedges' publication bias model](https://arxiv.org/abs/1912.09180).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(out.width='750px', dpi=200)
```

### 2020-08-06 infiniteci.tex
:+1: Small changes to contour plot.

--- 2020-04-24 infiniteci.tex
@@
-\documentclass[twoside]{article}
-\usepackage{arxiv}
+%% LyX 2.3.4.4 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
+\documentclass[english]{article}
+\usepackage[T1]{fontenc}
+\usepackage[latin9]{inputenc}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage{graphicx}
 
-%%% ============================================================================
-%%% Macros.
-%%% ============================================================================
+\makeatletter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+\numberwithin{equation}{section}
+\numberwithin{figure}{section}
+\usepackage[natbibapa]{apacite}
+\theoremstyle{plain}
+\newtheorem{thm}{\protect\theoremname}
+\theoremstyle{definition}
+\newtheorem{defn}[thm]{\protect\definitionname}
+\theoremstyle{definition}
+\newtheorem{example}[thm]{\protect\examplename}
+\theoremstyle{plain}
+\newtheorem{lem}[thm]{\protect\lemmaname}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage{infiniteci}
+
+\titletag{An arXiv preprint, v2}
+\makeatletter
+\titlerunning{\@title}
+\makeatother
+\authorrunning{Jonas Moss}
+
+\renewcommand{\sqrt}[1]{{(#1)^{1/2}}}
 \DeclareMathOperator{\tr}{tr}
@@
 \DeclareMathOperator{\argmax}{argmax}
+\DeclareMathOperator{\supp}{supp}
 
-\title{Infinite diameter confidence sets in the selection function model for publication bias}
+\usepackage{enumitem}
+\setlist[enumerate]{label = (\roman*)}
 
-\author{
-  Jonas Moss \orcid{0000-0002-6876-6964} \\
-  Department of Mathematics, University of Oslo\\
-  PB 1053, Blindern, NO-0316, Oslo, Norway \\
-  \it{jonasmgj@math.uio.no}
-}
+\makeatother
 
-\titletag{An arXiv preprint, v2}
-\makeatletter
-\titlerunning{\@title}
-\makeatother
-\authorrunning{Jonas Moss}
+\usepackage{babel}
+\providecommand{\definitionname}{Definition}
+\providecommand{\examplename}{Example}
+\providecommand{\lemmaname}{Lemma}
+\providecommand{\theoremname}{Theorem}
 
 \begin{document}
+\title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
+\author{Jonas Moss \orcid{0000-0002-6876-6964}\\
+Department of Mathematics, University of Oslo\\
+PB 1053, Blindern, NO-0316, Oslo, Norway\emph{}\\
+\emph{jonasmgj@math.uio.no}}
 \maketitle
 \begin{abstract}
-Meta-analysis is the quantitative combination of results from different studies.
-The assumptions of classical meta-analysis models are not satisfied whenever publication bias is present, which causes inconsistent parameter estimates.
-A popular method to account for publication bias in meta-analysis is the selection function model, but frequentist estimation of this model is problematic.
-This paper shows there is no confidence set of guaranteed finite diameter for the mean and heterogeneity parameters in the selection function model.
-The proof is based on a generalization of the Gleser--Hwang theorem.
+Meta-analysis, the statistical analysis of results from separate studies,
+is a fundamental building block of science. But the assumptions of
+classical meta-analysis models are not satisfied whenever publication
+bias is present, which causes inconsistent parameter estimates. Hedges'
+selection function model takes publication bias into account, but
+estimating and infering with this model is tough. Using a generalized
+Gleser--Hwang theorem, we show there is no confidence set of guaranteed
+finite diameter for the parameters of Hedges' selection model. This
+result provides a partial explanation for why inference with Hedges'
+selection model is fraught with difficulties.
 \end{abstract}
-
-\keywords{meta-analysis \and publication bias \and selection function model \and p-hacking}
+\keywords{meta-analysis \and confidence intervals \and file-drawer  problem \and publication bias \and selection models \and weigth function models}
 
@@
 
-Meta-analysis is the quantitative combination of results from different studies with the goal of reducing sampling error \citep{lipsey2001practical}.
-Publication bias occurs when the published research literature is
-not representative of the all the research that has actually been
-done \citep{rothstein2006publication}. An important case of publication
-bias is when publication decisions are made based on \textit{p}-values
-\citep{sterling1959publication}, which, along its sister phenomenon \textit{p}-hacking \citep{simmons2011false},
-can cause seriously biased conclusions when not accounted
-for \citep{simmons2011false,moss2019modelling}.
+A meta-analysis is a statistical analysis that quantiatively combines
+results from separate scientific studies. When the studies measure
+the same phenomenon, pooling of information allows us to predict the
+common effect size with larger precision than we could have done with
+one study alone. Meta-analyses are ubiquitous in the empirical sciences
+and forms a key component of most systematic reviews such as Cochrane's
+reviews \citep{Higgins2019-vv}.
 
-One of the most important models for meta-analysis is the normal random effects
-model with normal likelihoods where the
-standard deviations are assumed to be known \citep{hedges1998fixed}.
-The likelihood for an observation in this model is $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$,
-where $\phi(x\mid\mu,\sigma)$ is the normal density with
-mean $\mu$ and standard deviation $\sigma$.
-The parameter $\tau$ is the standard deviation of the random effects distribution, known as the heterogeneity parameter.
-The $\sigma_i$s are the study-specific standard errors, and $\theta_0$ is the mean of the effect size distribution.
-A modification of the random effects meta-analysis model due to \citet{hedges1984estimation}
-allows us to account for \textit{p}-value based publication bias.
+Most meta-analytic techniques assume honest and unbiased reporting
+of results. But there is ample evidence that the scientific literature
+is not unbiased, as studies with\emph{ }significant \emph{p}-values
+tend to be published with a greater probability than other studies
+\citep{Easterbrook1991-ph}, a phenomenon called publication bias
+by \citet{sterling1959publication} and the file-drawer problem by
+\citet{Rosenthal1979-pm}. When publication bias is present, there
+is no reason to trust the results of meta-analytic methods that do
+not account for it, as the parameter estimates will be incosistent
+\citep{Carter2019-rw}.
 
-Let $u=\Phi(-x_{i}/\sigma_{i})$ be the standard one-sided
-\textit{p}-value for the null hypothesis $\theta_{i}=0$, and $w(u)$
-a probability for each $u$. The selection function meta-analysis
-model \citep{hedges1984estimation,hedges1992modeling} based on
-the\emph{ p}-value $u$ is
+Hedges' \citeyearpar{hedges1992modeling} publication bias model takes
+publication bias explicitly into account using a selection model,
+and is arguably the most appropriate model for publication bias \citep{Carter2019-rw}.
+Despite there being an $\mathtt{R}$ \citep{Team2013-tt} package
+for maximum likelihood estimation of this model, called $\texttt{weightr}$
+\citep{Coburn2019-ec}, the model has not yet taken off. Its maximum
+likelihood estimation methods are numerically unstable and its estimates
+can be off even when they converge \citep{Coburn2019-ec,Stanley2005-ng}.
+The estimate of the mean effect size may be negative and of unrealistically
+large magnitude, and the estimated heterogeneity parameter might be
+improbably large. It turns out there are ridges in the likelihood
+function that can be linked to this behavior \citep{McShane2016-rb},
+but it has not been stated in clear terms exactly what the consequences
+are for inferential procedures. The purpose of this note is to show
+there is no confidence set for the mean effect size that has infinite
+diameter with probability $0$. In the terminology of \citet{berger1999integrated},
+Hedges' publication bias model belongs to the \emph{Gleser--Hwang}
+class.
+
+\section{Hedges' publication bias model}
+
+The most popular and well-known meta-analysis method is the random
+effects model with normal likelihoods \citep{hedges1998fixed}. Written
+in hierarchical notation, it equals
+\begin{eqnarray*}
+\theta_{i} & \sim & N(\theta_{0},\tau),\\
+x_{i}\mid\theta_{i},\sigma & \sim & N(\theta_{i},\sigma_{i}).
+\end{eqnarray*}
+Here $\sigma_{i}$ is the standard deviation of the $i$th study.
+Following the convention in meta-analysis, we assume all $\sigma_{i}$s
+to be known. The mean parameter $\theta$ is the population effect
+size, $N(\theta_{0},\tau)$ is the effect size distribution, and $\tau$
+is the heterogeneity parameter. The purpose of the effect size distribution
+is to model the fact that most effect size estimates plugged into
+a meta-analysis do not appear to measure the same phenomenon. By integrating
+out $\theta_{i}$, we find the density of $x_{i}$,
+\[
+f(x_{i};\theta_{0},\tau,\sigma_{i})=\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}}),
+\]
+where $\phi$ is the density of a normal random variable.
+
+We will assume that the random effects meta-analysis model is true
+in the absence of publication bias. The mechanisms that cause publication
+bias modify the density in a suitable way. Consider the case when
+only significant studies at some specified level $\alpha$ are published.
+Assuming one-sided tests, the \emph{p}-values are $u_{i}=\Phi(-x_{i}/\sigma_{i})$,
+or normal one-sided \emph{p}-values. We will only deal with with one-sided
+\emph{p}-values in this paper, as there is usually, but not always,
+just one direction that is interesting to researchers, reviewers,
+and editors. A one-sided \emph{p}-value can also be used if the researchers
+reported a two-sided value, since $p=0.05$ for a two-sided hypothesis
+corresponds to $p=0.025$ for a one-sided hypothesis, et cetera.
+
+Define $c_{\alpha}=\Phi^{-1}(1-\alpha)$, the cutoff for significance
+at level $\alpha$. The \emph{basic publication bias model} is a truncated
+normal model with density
 \begin{equation}
-f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})\propto\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u)\label{eq:Publication bias model}
+f(x_{i};\theta_{0},\sigma_{i})=\Phi\left(\frac{\theta_{0}-c_{\alpha}}{\sqrt{\sigma_{i}^{2}+\tau^{2}}}\right)^{-1}\phi(x;\theta_{0},\sqrt{\sigma_{i}^{2}+\tau^{2}})1[x_{i}/\sigma_{i}>c_{\alpha}],\label{eq:selection for significance model}
 \end{equation}
-The model is also known as the weighting function publication bias
-model. Here is an interpretation of it:
+This model for publication bias was introduced by \citet{hedges1984estimation}
+in the context of $F$-distributions.
+
+The basic publication bias model is unrealistic. It requires that
+no non-significant studies are published. But even in the fields most
+severely affected by publication bias, such as psychology, a non-negligble
+number of non-significant studies are published \citep{Motyl2017-dx}.
+Moreover, the basic publication bias model does not allow for different
+cutoffs for significance. For instance, it is likely that some editors
+will accept studies reaching a significance at $\alpha=0.025$, corresponding
+to $x_{i}/\sigma_{i}>1.96$ but not at $\alpha=0.05$, corresponding
+to $x_{i}/\sigma_{i}>1.64$.
+
+These problems can be rectified by adopting the selection model for
+publication bias of \citet{iyengar1988selection}, which models the
+following scenario.
 \begin{quote}
-Alice is an editor who receives a study with \textit{p}-value $u$.
-Her publication decision is a random function of this \textit{p}-value. That is, 
-she will publish the study with some probability $w(u)$.
+\textbf{Publication bias scenario.} Alice the editor receives a study
+with the \emph{p}-value $u$. Her publication decision is a random
+function of this \emph{p}-value. That is, she will publish the study
+with some probability $w(u)$ and reject it with probability $1-w(u)$.
 Every study you will ever read in Alice's journal has survived this
@@
 \end{quote}
-This is a rejection sampling \citep{von1951various,flury1990acceptance}
-procedure. The publication probability function is likely to be well
-approximated by a step function, with cutoffs such as $0.01,0.025$
-and $0.05$ being especially important. To model this, let $\alpha$
-be a vector with $0=\alpha_{0}<\alpha_{1}<\cdots<\alpha_{J}=1$ and
-$\rho$ be a non-negative vector in $[0,1]^{J}$ with $\rho_{1}=1$.
-Now define $w(u\mid\rho,\alpha)=\sum_{j=1}^{J}\rho_{j}1_{(\alpha_{j-1},\alpha_{j}]}(u)$.
-This is a step function where the value of $w$ on each step $(\alpha_{j-1},\alpha_{j}]$
-is the probability of acceptance for a study with a\emph{ p}-value
-$u$ falling inside the interval $(\alpha_{j-1},\alpha_{j}]$. I will
-call the density proportional to $\phi(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})w(u;\rho,\alpha)$
-the step function publication bias model and denote it $f(x_{i}\mid\theta_{0},(\sigma_{i}^{2}+\tau^{2})^{1/2})$.
+Let $w(u_{i})$ be a function of the \emph{p}-value $u_{i}=1-\Phi(-x_{i}/\sigma_{i})$
+taking values in $[0,1]$. Then $w(u_{i})$ is a probability for every
+$u_{i}$, and the selection model
 
-The step function publication bias model was first used by \citet{hedges1984estimation},
-who used an $F$ distribution instead of a the normal distribution
-and a single step in $w(u\mid\rho,\alpha)$. \citet{iyengar1988selection}
-studied other choices of $w$ while \citet{citkowicz2017parsimonious}
-used a beta density publication probability function instead of a
-step function. \citet{hedges1992modeling} is an accessible paper
-about the model.
+\begin{equation}
+f(x_{i};\theta_{0},\sqrt{\sigma_{i}^{2}+\tau^{2}})\propto\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})w(u)\label{eq:iyengar-greenhouse model}
+\end{equation}
+models the publication bias scenario exactly. This model can be viewed
+as a rejection sampling procedure \citep{flury1990acceptance,von1951various},
+where $\phi$ serves as proposal distribution for $f$. Variants of
+this model, with and without covariates, has been studied by e.g.
+\citet{Dear1992-gw,Vevea1995-on,Vevea2005-xp,citkowicz2017parsimonious}.
 
-Frequentist estimation of the step function publication bias model
-is problematic, as noted by \citet[Appendix, 1]{mcshane2016adjusting}.
-The purpose of this paper is to formalize and prove exactly how bad frequentist estimation of this model can be.
-I do this by proving there are no confidence sets of guaranteed finite diameter for the mean parameter $\theta_{0}$
-and the heterogeneity parameter $\tau$ for any coverage $1-\alpha$.
-This is a problematic result for two reasons: (i) It would be hopeless
-to report confidence sets for $\tau^{2}$ like $[0.5,\infty)$,
-as they have no practical value. (ii) It shows that the automatic confidence
-sets procedures that are guaranteed to yield finite confidence sets
-of some positive nominal coverage, such as bootstrapped confidence
-sets, likelihood-ratio based confidence sets, and subsampling confidence
-sets never have true coverage greater than $0$ \citep[see][]{gleser996bootstrap}.
+\citet{hedges1992modeling} studies the selection model when $w$
+is a step function with fixed steps. Let $\alpha$ be a vector with
+elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$
+be a $K$-ary non-negative, non-increasing vector having its first
+element equal to $\rho_{1}=1$. Define the step function $w$ based
+on $\alpha$ and $\rho$ as
+\begin{equation}
+w(u;\rho,\alpha)=\sum_{k=1}^{K}\rho_{k}1_{(\alpha_{k-1},\alpha_{k}]}(u).\label{eq:step function}
+\end{equation}
+We call the selection model with a step function \emph{Hedges' publication
+bias model. }Its density is
+\begin{equation}
+f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho_{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1_{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
+\end{equation}
+Interpretating Hedges' publication bias model is easy. When the editor
+receives a study with \emph{p}-value $u$, she finds the $j$ such
+that $u\in(\alpha_{j-1},\alpha_{j}]$ and accepts with probability
+$\rho_{j}$. Since $\rho_{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
+The vector $\rho$ is non-increasing since a publication decision
+based solely on \emph{p}-values should always act favorably towards
+lower \emph{p}-values. The parameters $(\theta_{0},\tau,\rho)$ of
+the model are identified when $\alpha$ is fixed \citep[Web Appendix A]{moss2019modelling}.
 
-The main result of this paper is the following theorem.
-\begin{thm}
-\label{prop:p-hacking infinite confidence interval}Let $h(x)=\prod_{i=1}^{n}f(x_{i}\mid\theta_{0},\tau,\sigma_{i})$
-be the density of a $n$ independent observations from a step function
-publication bias model. Then $h$ has no almost surely finite diameter
-confidence set for $\left|\theta\right|$ or $\sigma$ of non-zero
-coverage.
+Hedges' publication bias models allows both for non-significant studies
+to be published and allows the editor to act differently towards different
+cutoffs such as $\alpha=0.025$ and $\alpha=0.05$. In addition, the
+model can approximate any non-increasing selection function $w$ by
+increasing the number of steps.
+
+We can write Hedges' model as a mixture model on the form
+\begin{equation}
+f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})=\sum_{k=1}^{K}\pi^{k}f^{k}(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}}).\label{eq:mixture model formulation}
+\end{equation}
+Here $f^{K}$ is a normal density, $f^{k},k<K$ are normal densities
+truncated to $[\Phi^{-1}(1-\alpha_{j-1}),\Phi^{-1}(1-\alpha))$, and
+$\pi^{k}$ are mixture probabilities, i.e., $\pi^{k}>0$ for each
+$k$ and $\sum_{k=1}^{K}\pi^{k}=1$. The mixture probabilities $\pi^{k}$
+are functions of $(\theta_{0},\tau,\sigma_{i},\rho)$, see the appendix
+(p. \pageref{eq:pi_i formula}) for their formula.
+
+The main benefit of Hedges' publication bias model (\ref{eq:hedges model})
+is how it models \emph{p}-values based publication bias directly,
+there is no approximation involved. If you believe in the random effects
+meta-analysis model and the \emph{p}-value based publication bias
+scenario, Hedges' publication bias model is simply the correct model.
+Most statistical methods correcting for publication bias in the literature
+either do not make use of an explicit statistical model or do not
+estimate the parameters $\theta_{0}$ and $\tau$. For instance, the
+funnel funnel plot of \citet{Egger1997-rd} is a graphical method,
+while the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric
+method based on making the funnel plot symmetric. \citet{Stanley2005-ng,stanley2014meta}
+discuss various misspecified regression-based estimators of the corrected
+effect size $\theta$ based on the fixed effect Hedges' publication
+bias model. The estimating \emph{p}-curve method of \citet{Simonsohn2014-cn}
+and \emph{p}-uniform of \citet{Van_Assen2015-qs,Van_Aert2016-cu}
+are two methods for dealing with publication bias hailing from psychology.
+Both are based on a variant of the basic publication bias model, but
+with fixed instead of random effects, and both employ somewhat unusual
+estimation methods \citep{McShane2016-rb}. Since there is ample evidence
+of heterogeneity in meta-analysis, restricting oneself to the fixed
+effects meta-analysis is a mistake.
+
+Hedges' model has some downsides. It models only bias due to selection
+of \emph{p}-values, not every source of bias, such as language bias
+\citep{Egger1998-kj}. Second, it may not be best model for biases
+with other causes than the publication process, such as \emph{p}-hacking
+\citep{simmons2011false}. \citet{moss2019modelling} propose a related
+model that may be more successful at correcting for \emph{p}-hacking.
+
+Estimation of Hedges' model is difficult. \citet[Section 6.3]{Stanley2005-ng}
+discusses three problematic cases in economics when maximum likelihood
+was used to estimate Hedges' publication bias model. \citet[Appendix A]{McShane2016-rb}
+notes that while estimation of the basic publication bias model is
+hard, introducing the heterogeneity parameter exacerbates the problem.
+The likelihood function has contours following approximately $\tau\propto\sqrt{|\theta|}$.
+Figure \ref{fig:contour lines} shows the contour lines for the meta-analysis
+of \citet{Cuddy2018-kp} where the selection probabilities of the
+step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$.
+Only just around the maximum at $\hat{\theta}_{0}=0.55$ and $\hat{\sigma}=5\cdot10^{-7}$
+can the likelihood be approximated with a quadratic function.
+
+\begin{figure}
+\noindent \begin{centering}
+\includegraphics[scale=0.5]{chunks/cuddy}
+\par\end{centering}
+\caption{\label{fig:contour lines}Contour lines for the log-likelihood for
+the simple publication model using power posing data of \citet{Cuddy2018-kp}. }
+
+\end{figure}
+
+\section{Confidence sets of infinite diameter}
+
+Fix some measurable space $(\Omega,\mathcal{F})$, let $\mathcal{P}$
+be a family of dominated probability measures defined on this measurable
+space, and $\mathcal{\Pi}$ a partition of $\mathcal{P}$. Recall
+that a partition of $\mathcal{P}$ is a collection of disjoint non-empty
+subsets $\pi$ of $\mathcal{P}$ such that $\bigcup_{\pi\in\Pi}\pi=\mathcal{P}$.
+When $p$ is a density associated with a $P\in\mathcal{P}$, we will
+use the standard notation $[p]$ to denote the unique $\pi$ containing
+$P$. 
+\begin{defn}
+\label{def:confidence set} A \emph{confidence set} of level $\alpha$
+is a family of rejection sets $\{R(\pi)\},\pi\in\Pi$ such that
+\[
+\sup_{\pi\in\Pi}\sup_{P\in\pi}P(R(\pi))\leq\alpha.
+\]
+If the inequality is an equality, the confidence set has \emph{size}
+$\alpha$. 
+\end{defn}
+
+This definition of confidence sets might look slightly unfamiliar,
+but it is a straight-forward generalization of the definitions in
+\citet[Definition 9.1.5]{Casella2002-lg} and \citet[Section 3.5]{lehmann2006testing}.
+Usually, a confidence is defined as a set $C$ adhering to the relation
+\begin{equation}
+\pi_{0}\in C\iff\omega\notin R(\pi_{0}).\label{eq:c-confidence set}
+\end{equation}
+That is, $\pi_{0}\in C$ if and only if we accept the null-hypothesis
+$H_{0}:\pi=\pi_{0}$, but will only need the formulation using rejection
+sets in this paper. When confidence sets are defined in terms of rejection
+sets, there is sometimes no partition $\Pi$ to take the supremum
+over, and the definition reduces to $\sup_{P\in\mathcal{P}}P(R(P))\leq\alpha$.
+The term\emph{ confidence interval} is far more common than confidence
+set, but this requires that $C$ of equation \ref{eq:c-confidence set}
+is an interval, which we will not require here.
+
+The following example should make Definition \ref{def:confidence set}
+familiar.
+\begin{example}
+\label{exa:t-test} Consider the usual \emph{t}-confidence interval
+with $n$ observations. Here $\mathcal{P}$ contains all measures
+$P_{\mu,\sigma}^{n}$, where $P_{\mu,\sigma}$ is the probability
+measure of a normal with mean $\mu$ and standard deviation $\sigma$.
+Furthermore, when $Q$ is a probability measure, $Q^{n}$ denotes
+the $n$-fold product measure of $Q$, corresponding to $n$ independent
+samples from $Q$. Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
+contain all normal probability measures with mean $\mu$ and some
+positive standard deviation. Then $\{\pi(\mu)\},\mu\in\mathbb{R}$
+defines a partition of $\mathcal{P}$. A two-sided \emph{t}-confidence
+interval is a confidence set of size $\alpha$ with partition $\{\pi(\mu)\},\mu\in\mathbb{R}$
+according to definition \ref{def:confidence set}.
+\end{example}
+
+Now we must find out how to measure the size of confidence sets. Let
+a \emph{size function} be any positive function $\left\Vert \cdot\right\Vert :\Pi\to[0,\infty)$.
+In the \emph{t}-confidence interval example above, $\left\Vert \cdot\right\Vert $
+can be taken to be $\left\Vert \pi\right\Vert =|\mu|$ for the unique
+$\mu$ associated with each $\pi$.
+
+The diameter of a confidence set is the random variable
+\begin{equation}
+D(\omega)=\sup_{\pi\in\Pi}\{\left\Vert \pi\right\Vert \mid\omega\notin R(\pi)\}.\label{eq:diameter}
+\end{equation}
+That is, the diameter tells you the size of the largest accepted $\pi$.
+We will assume that $D$ is Borel measurable.
+\begin{defn}
+\label{def:infinite diameter}A confidence set has infinite diameter
+with $P$-positive probability if $P(D=\infty)>0$. It has infinite
+diameter with positive probability if $P(D=\infty)>0$ for all $P\in\mathcal{P}$.
+\end{defn}
+
+This is a modified Gleser--Hwang theorem \citep[Theorem 1]{gleser1987nonexistence}
+formulated in terms of partitions. Its proof is in the appendix (p.
+\pageref{proof:Gleser--Hwang}).
+\begin{thm}[Gleser--Hwang theorem]
+\label{thm:Gleser--Hwang} Suppose there is a sequence $\{p_{i}\}$
+of densities from $\mathcal{P}$ satisfying the following: 
+\begin{enumerate}
+\item There is a density $p^{\star}$ such that $p_{i}$ converges to $p^{\star}$
+pointwise,
+\item $\supp p\supseteq\supp p^{\star}$ for all $p$,
+\item the size of $[p_{i}]$ goes to infinity, $\left\Vert [p_{i}]\right\Vert \to\infty$.
+\end{enumerate}
+Then every confidence set with level $\alpha>0$ has infinite diameter
+with positive probability.
 \end{thm}
 
-\section{Definitions and Proofs}
-Let $P_{\theta},\theta\in\Theta$ be a family of dominated probability
-measures with densities $p_{\theta}$. Let $g:\Theta\to E$ for some
-set $E$ equipped with a positive function $\left\Vert \cdot\right\Vert :E\to[0,\infty)$.
-Here $g$ maps $\theta$ to the parameter we wish to form a confidence
-set for, sometimes called a \textit{focus parameter} ((cite Nils)).
-For instance, $g(\theta) = \theta$ or $g(\theta) = E_\theta(X)$, the expectation of some random variable $X$ calculated under $P_\theta$.
+Following the terminology of \citet{berger1999integrated}, we will
+say that families $\mathcal{P}$ of probabilities satisfying the conclusion
+of Theorem \ref{thm:Gleser--Hwang} for some suitable partition $\Pi$
+belong to the Gleser--Hwang class. To make the Gleser--Hwang class
+more familiar, we will present two examples. More examples can be
+found in the papers of \citet{gleser1987nonexistence} and \citet{berger1999integrated}.
+\begin{example}[Fieller's problem]
+\label{exa:Fieller's problem} Let $X,Y$ be an observation from
+a bivariate normal $N([\mu_{1},\mu_{2}],I\sigma^{2})$, where $\sigma^{2}$
+is known. We want to form a confidence set for ratio $\mu_{2}/\mu_{1}$.
+The most famous confidence set is due to \citet{Fieller1940-lg}.
+His confidence set can be finite, the whole real line, or the union
+of two disjoint semi-infinite intervals \citep{Koschat1987-dk}, all
+with positive probability.
 
-The function $\left\Vert \cdot\right\Vert$ measures the \textit{size} of each $e \in E$. It could be a norm if $E$ is a vector space, and below it is the
-absolute value $\left|\cdot\right|$.
+But it is not only Fieller's confidence set that might be infinitely
+long. The Gleser--Hwang theorem can be used to show that every confidence
+set for $\mu_{2}/\mu_{1}$ must be infinitily long with positive probability.
+This result is almost independent of the distribution of $X$ and
+$Y$. To state this result in our notation, let $\mathcal{P}$ be
+a family of bivariate distributions over $(X,Y)$. All of these distributions
+have the same support, and all of them have finite means $E_{p}(X)$
+and $E_{p}(Y)$. Moreover, assume $E_{p}(X)=0$ is attainable for
+some $p\in\mathcal{P}$. Define the partition $\Pi$ by $p,q\in\pi$
+if and only if $E_{p}(X)/E_{p}(Y)=E_{q}(X)/E_{q}(Y)$, and let $\left\Vert [p]\right\Vert =|E_{q}(X)/E_{q}(Y)|$,
+i.e., the ratio of means. Choose a sequence $p_{n}(x,y)=p(x,y)$,
+where $p(x,y)$ is density with means $E_{p}X>0$ and $E_{p}Y=0$.
+Then $\left\Vert [p]\right\Vert =\infty$, the conditions of Theorem
+\ref{thm:Gleser--Hwang} are satisfied, and every confidence set with
+level $\alpha>0$ has infinite diameter with positive probability.
+\begin{example}[Bahadur--Savage]
+\label{exa:Bahadur--Savage} \citet{bahadur1956nonexistence} studies
+non-parametric testing of the mean, and concludes the mean cannot
+be meaningfully tested. They are working with a family $\mathcal{P}$
+of densities over $\mathbb{R}$ that covers all finite means, has
+finite variances, and is closed under convex combinations. Similar
+problems were considered by \citet{romano2004non} and \citet{Donoho1988-hg}.
 
-A random set $C$ is a confidence set for $g(\theta)$ with coverage probability $1-\alpha$
-if $P_{\theta}(g(\theta)\in C)\geq1-\alpha$
-for all $\theta$. An\emph{ }acceptance set with level $\alpha$ has
-the property than $P_{\theta}(A_{g(\theta)})\geq1-\alpha$.
-There is a well known duality between confidence sets and acceptance
-sets: For each confidence set $C$ there is a collection of acceptance
-sets $A_{g(\theta)}$ satisfying $\omega\in A_{g(\theta)}$ if and only if $g(\theta)\in C(\omega)$. The classical reference for these concepts is of \citet[chapter 3.5]{lehmann2006testing}
+Using the Gleswer--Hwang theorem, it is easy to verify every confidence
+set has infinite diameter with positive probability. Define the partition
+$\Pi$ by $p,q\in\Pi$ if and only if $E_{p}(X)=E_{q}(X)$, and let
+$\left\Vert [p]\right\Vert =|E_{p}(X)|$. Let
+\[
+p_{n}(x)=\left(1-\frac{1}{n}\right)q_{0}(x)+\frac{1}{n}q_{n^{2}}(x),
+\]
+where $p_{0}$ has mean $0$ and $q_{n^{2}}$ has mean $n^{2}$. Then
+$\left\Vert [p_{n}]\right\Vert =n$, the conditions of Theorem \ref{thm:Gleser--Hwang}
+are satisfied, and every confidence set with level $\alpha>0$ has
+infinite diameter with positive probability.
+\end{example}
 
-We will need terminology for the diameter of the confidence set according
-to the function $\left\Vert \cdot\right\Vert $. The diameter is
-a random variable, $D=\textrm{sup}_{\eta\in C}\left\Vert \eta\right\Vert $.
-A confidence set has infinite diameter at $\theta$ with positive
-probability if $P_{\theta}(D=\infty)>0$. If $P_{\theta}(D=\infty)>0$
-for all $\theta$, we will say that $D$ has infinite diameter with
-positive probability.
+\end{example}
 
-The main ingredient in the proof of Theorem \ref{prop:p-hacking infinite confidence interval}
-is Theorem \ref{thm:Infinite diameter main theorem}, an extension
-and reformulation of the Gleser--Hwang theorem \citep{gleser1987nonexistence}. 
-They used their theorem o prove the non-existence of confidence sets with
-guaranteed finite diameter for models such as the errors-in-variables
-regression model ((cite)) and Fieller's ratio of means problem ((cite)). \citet[theorem 1]{berger1999integrated}
-is a similar extension of the Gleser--Hwang theorem.
+There are several natural candidates for $\Pi$ when working with
+Hedges' selection function model (\ref{eq:hedges model}). We will
+work with three of them. First, consider the partition where $p,q\in\pi$
+if and only if $p,q$ have the same mean effect size parameter $\theta_{0}$.
+We will equip this partition with the size function $\left\Vert \pi\right\Vert =|\theta_{0}|$,
+and it corresponds to a confidence set for $\theta_{0}$. Second,
+consider the partition where all $p,q\in\pi$ have the same heterogeneity
+parameter $\tau$, equipped with $\left\Vert \pi\right\Vert =\tau$.
+Finally, we will work with the partition where all $p,q\in\pi$ have
+the same heterogeneity parameter $\tau$ and population effect size
+$\theta_{0}$, and equip it with $\left\Vert \pi\right\Vert =\sqrt{\theta_{0}^{2}+\tau^{2}}$.
+This information is summarised in Table \ref{tab:Possible partitions}
+for convenience.
 
-The problem with non-existence
-of confidence sets with guaranteed finite diameter for finite-dimensional
-parameters has not received much attention in the statistical literature,
-as lamented by \citet{gleser996bootstrap}. Some references in this
-area are \citet{bahadur1956nonexistence}, who studied infinitely
-large confidence sets in non-parametric estimation of the mean, \citeauthor{romano2004non}'s
-(2004) extension of their results, \citet{Donoho1988-hg} and \citet{Pfanzagl1998-fe}.
+\begin{table}
+\noindent \centering{}\caption{\label{tab:Possible partitions}The three partitions $\Pi$ for the
+selection function model}
+{\small{}}%
+\begin{tabular}{llll}
+ & {\small{}Symbol} & {\small{}Size $\left\Vert \cdot\right\Vert $} & {\small{}Confidence set}\tabularnewline
+\hline 
+{\small{}Mean effect size} & {\small{}$\theta_{0}$} & {\small{}$\left\Vert \pi\right\Vert =|\theta_{0}|$} & {\small{}Confidence set for $\theta_{0}$}\tabularnewline
+{\small{}Heterogeneity parameter} & {\small{}$\tau$} & {\small{}$\left\Vert \pi\right\Vert =\tau$} & {\small{}Confidence set for $\tau$}\tabularnewline
+Both parameters & {\small{}$(\theta_{0},\tau)$} & {\small{}$\left\Vert \pi\right\Vert =\sqrt{\theta_{0}^{2}+\tau^{2}}$} & {\small{}Joint confidence set for $(\theta,\tau)$}\tabularnewline
+\end{tabular}
+\end{table}
+
+Let us take a look at the basic publication bias model (\ref{eq:selection for significance model})
+again. To use Theorem \ref{thm:Gleser--Hwang} we need a witnessing
+sequence of functions $p_{n}\to p$ satisfying the conditions $\text{(ii)}$
+and $\text{(iii)}$. The next lemma shows how to make such a witness
+for the truncated normal. Its proof is in the appendix (p. \pageref{proof:generalized shifted exponential}).
 \begin{lem}
-Let $C$ be a confidence set and $A_{g(\theta)}$ its associated
-acceptance sets. If there exists a sequence $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$
-with $\left\Vert g(\theta_{n})\right\Vert \to\infty$ such
-that $\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0,$then
-the diameter of $C$ at $\theta$ is infinite with positive probability.
+\label{lem:generalized shifted exponential} Let $f_{n}$ be a normal
+density truncated to $[a,b)$, where $b=\infty$ is allowed, with
+underlying mean $\theta_{n}=-n$ and standard deviation $\sigma_{n}^{2}=n^{2}+c$
+for some $c\in\mathbb{R}$. Then $f_{n}$ converges pointwise to $\exp(-x)/[\exp(-a)-\exp(-b)]$,
+the distribution of an exponential variable truncated to $[a,b)$.
 \end{lem}
-\begin{proof}
-Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$
-for each $n$; such a sequence can always be found by appropriately
-filtering the original $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$.
-Since $\left\{ D\geq n\right\} $ is a decreasing sequence of sets,
-$P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)$
-for each $\theta$. From $A_{g(\theta_{n})}\subseteq\left\{ D\geq n\right\} $
-it follows that $P_{\theta}(A_{g(\theta_{n})})\leq P_{\theta}(D\geq n)$,
-thus $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)\geq\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0$.
-\end{proof}
-This is the extension of the Gleser--Hwang theorem.
+
+Using Lemma \pageref{lem:generalized shifted exponential} it is not
+hard to show that the basic publication bias model (\ref{eq:selection for significance model})
+is a member of the Gleser--Hwang class.
 \begin{thm}
-\label{thm:Infinite diameter main theorem}If there exists a sequence
-$\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$ with $\left\Vert g(\theta_{i})\right\Vert \to\infty$
-such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\textrm{supp}p_{\theta}=\textrm{supp}f^{\star}$
-for each $\theta$, then every confidence set with coverage $1-\alpha>0$
-has infinite diameter with positive probability.
+\label{thm:simple publication bias} Assume $n$ independent samples
+from the basic publication bias model (\ref{eq:selection for significance model}).
+Then, for any $n$, any confidence set for $\theta_{0},\tau$, or
+$(\theta_{0},\tau)$ with level $\alpha>0$ will have infinite diameter
+with positive probability. 
 \end{thm}
-\begin{proof}
-Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$.
-By a variant of the dominated convergence theorem \citep[Exercise 16.4a]{billingsley1995probability}, $\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
-Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\}$, we have 
-$1-\alpha\leq\int_{A_{g(\theta_{n})}}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
-for all $n$, thus $\int_{D=\infty}f^{\star}d\mu>1-\alpha>0$. The
-result follows from $P_{\theta}(D\geq n)=\int_{D\geq n}(p_{\theta}/p_{\theta_{n}})p_{\theta_{n}}d\mu>\int_{D=\infty}(p_{\theta}/f^{\star})f^{\star}d\mu>0$.
-\end{proof}
-This is an extension of Theorem \ref{thm:Infinite diameter main theorem}
-to mixture distributions.
-\begin{prop}
-\label{cor:Mixture model corollary}Let $f_{\theta}^{1},f_{\theta}^{2},\ldots$
-be a finite or infinite sequence of densities, $\pi(\theta)$
-a countable probability vector and $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
-a mixture distribution. Assume there is a sequence $\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$
-with $\left\Vert g(\theta_{i})\right\Vert \to\infty$ such
-that $f_{\theta_{i}}^{1}\to f^{\star}$ pointwise and $\textrm{supp}f_{\theta}^{1} = \textrm{supp}f^{\star}$
-for each $\theta$ . If there is a parameter $\theta'\in\Theta$ satisfying
-$\pi_{1}(\theta')>\alpha$, the mixture $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
-admits no almost surely finite diameter confidence set of coverage
-$1-\alpha$ for $g(\theta)$.
-\end{prop}
 
 \begin{proof}
-Let $C$ be confidence set for $g(\theta)$ with coverage
-$1-\alpha$. Since $\pi_{1}(\theta')>\alpha$ by assumption,
-$C$ must include a confidence $C_{1}$ for $f_{\theta}^{1}$ of some
-positive coverage. But by Theorem \ref{thm:Infinite diameter main theorem},
-$C_{1}$ has infinite diameter with positive probability for all $\theta$.
-Since $C\supseteq C_{1}$, $C$ has infinite diameter with positive
-probability too.
+\label{proof:simple publication bias}Let $\Pi$ be the partition
+of $\mathcal{P}$ where $p,q\in\pi$ if and only if they share the
+same $\theta_{0}$, and let $||[p]||=|\theta_{0}|$. We are dealing
+with products of densities of the form (\ref{eq:selection for significance model}),
+that is,
+\[
+p(x)=\prod_{i=1}^{N}\Phi\left(\frac{\theta_{0}-c_{\alpha}}{\sqrt{\sigma_{i}+\tau}}\right)^{-1}\phi(x_{i};\theta_{0},\sqrt{\sigma_{i}^{2}+\tau^{2}}),
+\]
+where $\sigma_{i}$ are known parameters. From Lemma \ref{lem:generalized shifted exponential},
+$p_{n}$ converges to a product of truncated exponentials when $\theta_{n}=-n$
+and $\tau_{n}^{2}=n$. Since $||[p_{n}]||=n$, the three conditions
+of Theorem \ref{thm:Gleser--Hwang} are satisfied. The proofs for
+$||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$ are
+similar and omitted.
 \end{proof}
-The following lemma is a proof of proposition \ref{prop:p-hacking infinite confidence interval}
-for the special case when no non-significant studies are published.
-Let $\phi_{[a,b)}(x\mid\theta,\sigma)$ denote
-the density of a normal variable with mean $\theta$ and standard
-deviation $\sigma$ truncated to $[a,b)$.
+Proving the analogue of Theorem \ref{thm:simple publication bias}
+for Hedges' publication is only somewhat more involved. We will use
+the mixture representation of (\ref{eq:mixture model formulation})
+and a lemma generalizing Theorem \ref{thm:Gleser--Hwang} to a certain
+kind of mixtures.
+
+Let $f^{1},f^{2},\ldots,f^{K}$ be a sequence of densities, $\pi=(\pi_{1},\pi_{2},\ldots,\pi_{K})$
+a probability vector, and $p=\sum_{k\leq K}\pi^{k}f^{k}$ a mixture
+distribution. We will assume that the size of $[p]$ equals the size
+of any of its mixture components $[f^{k}]$ for some size $\left\Vert \cdot\right\Vert $,
+i.e., $\left\Vert [p]\right\Vert =\left\Vert [f^{k}]\right\Vert $
+for all $k$. Why we do this will be clear in the proof of Theorem
+\ref{thm:general publication bias}, but think of it this way: If
+all of $p$s mixture components have the same mean, the mean of $p$
+equals the mean of any $f^{k}$. 
 \begin{lem}
-\label{lem:One-sided normal limit}Let $f$ be a normal density truncated
-to $[c,\infty)$ with underlying mean $\theta_{n}=-n-c$
-and standard deviation $\sigma_{n}=n^{1/2}$. Then $\phi_{[c,\infty)}(x\mid\theta_{n},\sigma_{n})$
-converges pointwise to $\exp(-x-c)$, the density of a
-shifted exponential.
+\label{prop:Mixture model corollary} Let $\mathcal{P}$ be a class
+of $K$-ary mixture distributions and $||[p]||$ be the assumption
+above. Assume there is a sequence $p_{i}=\sum_{k\leq K}\pi_{i}^{k}f_{i}^{k}$
+and a subset $K'$ such that 
+\begin{enumerate}
+\item For all $k\in K'$, there is a density $f^{k\star}$ such that $f_{i}^{k}$
+converges to $f^{k\star}$ pointwise.
+\item For all mixtures $p$, $\supp p\supseteq\supp f^{k\star}$ for some
+$k\in K'$.
+\item For all $k\in K'$, the size of $[f_{i}^{k}]$ goes to infinity, $\left\Vert [f_{i}^{k}]\right\Vert \to\infty$.
+\item The density concentrates on the components indexed by $K'$, $\lim_{i\to\infty}\sum_{k\in K'}\pi_{i}^{k}=1$.
+\end{enumerate}
+Then every confidence set with level $\alpha>0$ has infinite diameter
+with positive probability.
 \end{lem}
@@
 \begin{proof}
-The formula for $\phi_{[c,\infty)}(x;\theta_{n},\sigma_{n})$
-is $\Phi(-\frac{n+c}{n^{1/2}})^{-1}\phi(x;-n-c,n^{1/2})1_{x>c}$.
+We employ Theorem \ref{thm:Gleser--Hwang}. By (i) and (iv), $p_{i}$
+converges pointwise to the density $\sum_{k\in K'}\pi_{i}^{k\star}f_{i}^{k\star}=p^{\star}$
+. That $\supp p\supseteq p^{\star}$ follows from (ii) and (iv). Finally,
+from the assumption that$\left\Vert [p]\right\Vert =\left\Vert [f_{k}]\right\Vert $,
+we get that $\left\Vert [p]\right\Vert \to\infty$ too. 
+\end{proof}
+\begin{thm}
+\label{thm:general publication bias} Assume $n$ independent samples
+from the publication bias model (\ref{eq:selection for significance model}),
+where the selection probability $\rho$ is unknown and $\alpha$ is
+known. Then any confidence set for $\theta_{0},\tau$, or $(\theta_{0},\tau)$
+will have infinite diameter with positive probability.
+\end{thm}
+
+\begin{proof}
+\label{proof:general publication bias} Let $n=1$ and consider confidence
+sets for $\theta_{0}$. Let $\Pi$ be the partition of $\mathcal{P}$
+where $p,q\in\pi$ if and only if they share the same $\theta_{0}$,
+and let $||[p]||=|\theta_{0}|$. Then $||f^{k}||=|\theta_{0}|$ from
+the mixture representation (\ref{eq:mixture model formulation}).
+Using Lemma \ref{lem:generalized shifted exponential}, we see that
+$f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$
+and $\sqrt{\tau^{2}+\sigma^{2}}=n^{1/2}$, so that (i), (ii), (iii)
+of Proposition \ref{prop:Mixture model corollary} are satisfied with
+$K'=K\backslash\{1\}$. The mixture probabilities for $k\neq K$ can
+be fixed at e.g. $\pi=1/(K-1)$, and (iv) is satisfied as well. The
+proofs for $||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$
+are similar and omitted. When $n>1$, expand the expression $\prod_{j=1}^{n}\sum_{k\leq K}\pi_{i}^{k}(\sigma_{j})f_{i}^{k}(\sigma_{j}),$and
+use the same reasoning as in the first part of this proof.
+\end{proof}
+
+\section{Remarks}
+
+Well-behaved confidence sets for Hedges publication bias model do
+not exist, but well-behaved credibility sets do. Bayesian estimation
+of Hedges' model can be made routine, as it is easy to find uncontroverisal
+priors for $\theta_{0}$ and $\tau$. In practical meta-analyses we
+know that $\theta_{0}$ cannot be large, and is likely to be close
+to $0$. Moreover, since it is common effects in meta-analyses to
+be intepreted as the aggregation of many small effects, the central
+limit theorem justifies using a normal prior. As we want to remove
+prior mass from negative $\theta_{0}$s of large magnitude, $N(0,1)$
+is a decent standard prior. Similarily, a half-normal is a reasonable
+prior for the heterogeneity parameter $\tau$. \citet{moss2019modelling}
+employed these priors on several examples.
+
+\section*{Appendix}
+
+The following sandwich convergence theorem is used in the proof of
+the Gleser--Hwang theorem. 
+\begin{lem}[{\citet[Exercise 16.4(a)]{billingsley1995probability}}]
+\label{lem:Dominated covergence theorem} Suppose $a_{n},b_{n},f_{n}$
+converge to $a,b,f$ and $a_{n}\leq f_{n}\leq b_{n}$ for all $n$.
+If $\int a_{n}d\mu\to\int ad\mu$ and $\int b_{n}d\mu\to\int bd\mu$,
+then $\int f_{n}d\mu\to\int fd\mu$.
+\end{lem}
+
+The proof of Theorem \ref{thm:Gleser--Hwang} follows the proof of
+\citet[Theorem 1]{gleser1987nonexistence} closely. 
+\begin{proof}[Proof of Theorem \ref{thm:Gleser--Hwang}]
+\label{proof:Gleser--Hwang}We can assume without loss of generality
+that $\left\Vert [p_{n}]\right\Vert \geq n$, as we can choose a subsequence
+if we have to. By definition of the diameter $D$ (\ref{eq:diameter})
+we see that
+\[
+\{D\geq n\}=\{\omega\in\Omega\mid\textrm{there is a }\pi\textrm{ such that}\left\Vert \pi\right\Vert \geq n\textrm{ and }\omega\in R^{c}(\pi)\},
+\]
+and if $||[p_{n}]||\geq n$, then $R^{c}([p_{n}])\subseteq\{D\geq n\}$.
+Since we assume that $\left\Vert [p_{n}]\right\Vert \geq n$ and 
+\[
+1-\alpha\leq P_{n}(R^{c}([p_{n}]))=\int_{R^{c}([p_{n}])}p_{n}d\mu
+\]
+by definition of a confidence set, we have that
+\begin{equation}
+0<1-\alpha\leq\int_{R^{c}([p_{n}])}p_{n}d\mu\leq\int_{D\geq n}p_{n}d\mu\label{eq:inequality with R^c}
+\end{equation}
+for all $n$. Since $p_{n}$ and $p^{\star}$ are densities,
+\[
+\lim_{n\to\infty}\int p_{n}d\mu=1=\int p^{\star}d\mu=\int\lim_{n\to\infty}p_{n}d\mu.
+\]
+This allows us to use Lemma \ref{lem:Dominated covergence theorem}
+with $a_{n}=0$, $b_{n}=p_{n}$, and $f_{n}=1_{D\geq n}p_{n}$ and
+conclude that
+
+\begin{equation}
+\int_{D\geq n}p_{n}d\mu\to\int_{D=\infty}p^{\star}d\mu.\label{eq:limit of pn}
+\end{equation}
+Combining equations (\ref{eq:inequality with R^c}) and (\ref{eq:limit of pn}),
+we get
+\[
+0<1-\alpha\leq\int_{D=\infty}p^{\star}d\mu.
+\]
+Let $P\in\mathcal{P}$ be arbitrary, $p$ be its density, and consider
+\[
+P(D=\infty)=\int_{D=\infty}pd\mu\geq\int_{D=\infty\cap\supp p^{\star}}\left(\frac{p}{p^{\star}}\right)p^{\star}d\mu.
+\]
+Since $\int_{D=\infty}p^{\star}d\mu>0$ and $p/p^{\star}>0$ on $\supp p^{\star}$
+(since $\supp p\supseteq\supp p^{\star}$ by assumption), we see that
+$\int_{D=\infty\cap\supp p^{\star}}(p/p^{\star})p^{\star}d\mu>0$
+too. It follows that $P(D=\infty)>0$, and, since $P$ is aribtrary,
+$D$ has infinite diameter with positive probability.
+\end{proof}
+Now we prove Lemma (\ref{lem:generalized shifted exponential}).
+\begin{proof}[Proof of Lemma (\ref{lem:generalized shifted exponential})]
+\label{proof:generalized shifted exponential}Let $n^{2}>-c$, so
+that $\sigma_{n}^{2}>0$. Recll the well-known formula for the normal
+truncated to $[a,b]$,
+\begin{eqnarray}
+f_{n}(x) & = & \frac{1}{\Phi\left(\frac{b-\theta_{n}}{\sigma_{n}}\right)-\Phi\left(\frac{a-\theta_{n}}{\sigma_{n}}\right)}\phi(x;\theta_{n},\sigma_{n})1[a,b](x),\label{eq:truncated}\\
+ & = & \frac{\phi(x;-n,(n+c)^{1/2})1[a,b](x)}{\Phi[-(a+n)(n+c)^{-1/2}]-\Phi[-(b+n)(n+c)^{-1/2}]}.\nonumber 
+\end{eqnarray}
 The normal density part equals
 \[
-(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp\left(\frac{-n^{2}-2n(c+x)+[2cx-c^{2}-x^{2}]}{2n}\right)
+\phi(x;-n,(n+c)^{1/2})=(2\pi)^{-1/2}(n+c)^{-1/2}\exp\left(-\frac{x^{2}+2nx+n^{2}}{2(n+c)}\right).
 \]
-When $n$ is large compared to $x$ and $c$, $[2cx-c^{2}-x^{2}]/2n$
-is negligible, hence 
+When $n$ is large compared to $x$, the term $x^{2}/2(n+c)$ is negligible,
+hence
+\begin{eqnarray*}
+\phi(x;-n,(n+c)^{1/2}) & \approx & (2\pi)^{-1/2}(n+c)^{-1/2}\exp(-n^{2}/2(n+c))\exp(-x),\\
+ & = & (n+c)^{-1/2}\phi(n/(n+c)^{1/2})\exp(-x).
+\end{eqnarray*}
+From Equation 5 of \citet{borjesson1979simple}, we know that $\Phi(-x)\approx\phi(x)/x$
+as $x$ grows. The part of (\ref{eq:truncated}) involving cumulative
+normal distributions become
+\begin{eqnarray*}
+\Phi[-(a+n)(n+c)^{-1/2}] & \approx & \frac{(n+c)^{1/2}}{n+a}\phi[-(a+n)(n+c)^{-1/2}],
+\end{eqnarray*}
+and using the same reasoning as above, we find that $\phi[-(a+n)(n+c)^{-1/2}]\approx\phi((n+c)^{1/2})\exp(-a)$
+as $n$ increase. Therefore,
 \[
-\phi(x;\theta_{n},\sigma_{n})\approx(2\pi)^{-1/2}n^{-\frac{1}{2}}\exp(-n/2)\exp(-x-c)
+\Phi[-(a+n)(n+c)^{-1/2}]\to\frac{(n+c)^{1/2}\phi((n+c)^{1/2})\exp(-a)}{a+n}.
 \]
-which equals $\exp(-x-c)\phi(n^{1/2})/n^{1/2}$.
-Since $\Phi(-(\theta_{n}+c)/\sigma_{n})=\Phi(n^{1/2})\approx n^{1/2}/\phi(n^{1/2})$
-as $n$ grows \citep[equation 5]{borjesson1979simple},
-we end up with $$\Phi(-(\theta_{n}+c)/\sigma_{n})^{-1}\phi(x;\theta_{n},\sigma_{n})1_{x>c}\to\exp(-x-c)$$
+Since this reasoning applies to $b$ as well, we get that $f$ approaches
+\begin{eqnarray*}
+ &  & \frac{(n+c)^{-1/2}\phi(n/(n+c)^{1/2})\exp(-x)}{\Phi[-(a+n)n^{-1/2}]-\Phi[-(b+n)n^{-1/2}]},\\
+ & \approx & \frac{(n+c)^{-1/2}\phi(n/(n+c)^{1/2})\exp(-x)}{(n+c)^{1/2}\phi((n+c)^{1/2})\left[\frac{\exp(-a)}{a+n}-\frac{\exp(-b)}{b+n}\right]},\\
+ & = & \frac{\phi(-n^{2}/2(n+c))\exp(-x)}{\phi((n+c)^{1/2})\left[\frac{\exp(-a)}{a+n}-\frac{\exp(-b)}{b+n}\right]},\\
+ & \approx & \exp(-x)n^{-1}\left[\frac{\exp(-a)}{a+n}-\frac{\exp(-b)}{b+n}\right]^{-1},\\
+ & \to & \exp(-x)\left[\exp(-a)-\exp(-b)\right]^{-1}.
+\end{eqnarray*}
+Here the third line follows from $\phi(n/(n+c)^{1/2})/\phi((n+c)^{1/2})\to1$.
 \end{proof}
-%
-This lemma gives a mixture representation of the publication bias
-model. The proof is omitted.
-\begin{lem}
-\label{prop:Mixture representation} The density of an observation
-from the step function publication bias model with parameters $\theta_{0},\tau,\sigma_{i}$
-is
-\begin{equation}
-f(x\mid\theta_{0},\tau,\sigma_{i})=\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\Phi^{-1}(1-\alpha_{j-1}))}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})\label{eq:Random effects publication bias}
-\end{equation}
-where 
+For convenience, we show the formula for the mixture probabilities
+$\pi_{i}$ here. Let $c_{j}=\Phi^{-1}(1-\alpha_{j})$ and define 
 \[
-\pi_{j}(\theta,\tau,\sigma_{i})=\rho_{j}\frac{\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})}{\sum_{j=1}^{J}\rho_{j}[\Phi(c_{j-1}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]}.
+c=\sum_{k=1}^{K}\rho_{k}[\Phi(c_{j-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
 \]
-\end{lem}
+Then $\pi_{K}=\rho_{K}c^{-1}$ and \label{eq:pi_i formula}
+\[
+\pi_{k}=c^{-1}(\rho_{k}-\rho_{K})[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]
+\]
 
-\begin{proof}[Proof of Theorem \ref{prop:p-hacking infinite confidence interval}]
-Using the representation of \cref{eq:Random effects publication bias}
-of Lemma \ref{prop:Mixture representation} and Corollary \ref{cor:Mixture model corollary}, 
-it is enough to show the result for $\phi_{[\Phi^{-1}(1-\alpha_{j}),\infty)}(x\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})$
-where $\alpha_{j+1}=1$. To this end, let $c=\Phi(1-\alpha_{j})$.
-Then $\theta_{n}=-n-c$ and $\tau_{n}^{2}=n$ does the trick by lemma
-\ref{lem:One-sided normal limit}. For the case with more than one
-observation, observe that 
-\[
-\prod_{i=1}^{n}\sum_{j=1}^{N}\pi_{j}\phi_{[\Phi^{-1}(1-\alpha_{j}),\infty)}(x_{i}\mid\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})
-\]
-is mixture model. (Just expand it.) The component belonging to the
-mixture probability $\pi_{j}^{n}$ fulfills the demands of proposition
-\ref{cor:Mixture model corollary} for $\alpha_{j}$ when $\alpha_{j+1}=1$,
-as its density is a product of densities converging to shifted exponentials.
-\end{proof}
+\bibliographystyle{apacite}
+\bibliography{infiniteci}
 
-\section*{Acknowledgements}
-I am grateful to Riccardo De Bin and Emil Aas Stoltenberg for reading through the manuscript and giving helpful comments.
-
-%\printbibliography
-
-\bibliography{infiniteci}
 \end{document}

### 2020-08-06 R/cuddy.R

@@ -1,10 +1,15 @@
-## This package is used for the cuddy data.
-#install.packages("publipha")
+## This package is used for the cuddy data
+## The data is from the publipha package, which is required for.
+## calculating the density as well.
 
 cuddy2018 = publipha::dat.cuddy2018
 cuddy2018 = cuddy2018[cuddy2018$yi < 1.5, ] # removes outlier.
 
+yi = cuddy2018$yi
+vi = cuddy2018$vi
+
 eta = c(1, 0.6, 0.1)
+alpha = c(0, 0.025, 0.05, 1)
 
 objective = function(p) {
   theta0 = p[1]
@@ -15,13 +20,16 @@ objective = function(p) {
     tau = sqrt(tau_sq),
     sigma = sqrt(vi),
     eta = eta,
+    alpha = alpha,
     log = TRUE))
 }
 
-x = seq(-10, 0, by = 0.1)
-y = seq(0.01, 0.8, by = 0.1)
+x = seq(0.4, 0.7, length.out = 100)
+y = seq(0.01, 1, length.out = 100)
 FUN = Vectorize(function(theta0, tau) objective(c(theta0, tau)))
 z = outer(X = x, Y = y, FUN = FUN)
+
+solution = abs(nlm(objective, p = c(0.2, 0.01))$estimate) # 5.53-01 -4.99-07
 
 pdf("chunks/cuddy.pdf")
 contour(
@@ -31,4 +39,8 @@ contour(
   xlab = expression(theta[0]), ylab = expression(tau),
   cex.lab = sqrt(2), main = "Likelihood of Hedges' publication bias model"
   )
+points(x = solution[1], y = solution[2], pch = 20)
 dev.off()  
+
+
+nlm(objective, p = c(0.2, 0.01))

### 2020-08-06 R/cuddy.R
:+1: Better plot.

@@ -4,6 +4,7 @@
 
 cuddy2018 = publipha::dat.cuddy2018
 cuddy2018 = cuddy2018[cuddy2018$yi < 1.5, ] # removes outlier.
+cuddy2018 = cuddy2018
 
 yi = cuddy2018$yi
 vi = cuddy2018$vi
@@ -24,7 +25,7 @@ objective = function(p) {
     log = TRUE))
 }
 
-x = seq(0.4, 0.7, length.out = 100)
+x = seq(-3, 1, length.out = 100)
 y = seq(0.01, 1, length.out = 100)
 FUN = Vectorize(function(theta0, tau) objective(c(theta0, tau)))
 z = outer(X = x, Y = y, FUN = FUN)
@@ -36,6 +37,7 @@ contour(
   x = x, 
   y = y, 
   z = -z, 
+  levels = c(12, 10, 5, 0, -10, -100, -200, -500),
   xlab = expression(theta[0]), ylab = expression(tau),
   cex.lab = sqrt(2), main = "Likelihood of Hedges' publication bias model"
   )

### 2020-08-06 R/cuddy.R
Update cuddy.R

@@ -26,7 +26,7 @@ objective = function(p) {
 }
 
 x = seq(-3, 1, length.out = 100)
-y = seq(0.01, 1, length.out = 100)
+y = seq(10^(-7), 1, length.out = 100)
 FUN = Vectorize(function(theta0, tau) objective(c(theta0, tau)))
 z = outer(X = x, Y = y, FUN = FUN)
 

### 2020-08-12 infiniteci.tex
:pear: Update.

@@
 \end{eqnarray*}
-Here $\sigma_{i}$ is the standard deviation of the $i$th study.
-Following the convention in meta-analysis, we assume all $\sigma_{i}$s
-to be known. The mean parameter $\theta$ is the population effect
-size, $N(\theta_{0},\tau)$ is the effect size distribution, and $\tau$
-is the heterogeneity parameter. The purpose of the effect size distribution
-is to model the fact that most effect size estimates plugged into
-a meta-analysis do not appear to measure the same phenomenon. By integrating
-out $\theta_{i}$, we find the density of $x_{i}$,
+Here $x_{i}$ is the effect size and $\sigma_{i}$ is the standard
+deviation of the $i$th study, and $i=1,\ldots,N$. Following the
+convention in meta-analysis, we assume all $\sigma_{i}$s to be known.
+The mean parameter $\theta$ is the population effect size, $N(\theta_{0},\tau)$
+is the effect size distribution, and $\tau$ is the heterogeneity
+parameter. The purpose of the effect size distribution is to model
+the fact that most effect size estimates plugged into a meta-analysis
+do not appear to measure the same phenomenon. By integrating out $\theta_{i}$,
+we find the density of $x_{i}$,
 \[
@@
 \begin{equation}
-w(u;\rho,\alpha)=\sum_{k=1}^{K}\rho_{k}1_{(\alpha_{k-1},\alpha_{k}]}(u).\label{eq:step function}
+w(u;\rho,\alpha)=\sum_{k=1}^{K}\rho^{k}1_{(\alpha_{k-1},\alpha_{k}]}(u).\label{eq:step function}
 \end{equation}
@@
 \begin{equation}
-f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho_{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1_{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
+f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho^{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1_{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
 \end{equation}
 Interpretating Hedges' publication bias model is easy. When the editor
-receives a study with \emph{p}-value $u$, she finds the $j$ such
-that $u\in(\alpha_{j-1},\alpha_{j}]$ and accepts with probability
-$\rho_{j}$. Since $\rho_{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
+receives a study with \emph{p}-value $u$, she finds the $k$ such
+that $u\in(\alpha_{k-1},\alpha_{k}]$ and accepts with probability
+$\rho^{k}$. Since $\rho^{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
 The vector $\rho$ is non-increasing since a publication decision
@@
 
-Hedges' publication bias models allows both for non-significant studies
+Hedges' publication bias model allows both for non-significant studies
 to be published and allows the editor to act differently towards different
@@
 estimate the parameters $\theta_{0}$ and $\tau$. For instance, the
-funnel funnel plot of \citet{Egger1997-rd} is a graphical method,
-while the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric
+funnel plot of \citet{Egger1997-rd} is a graphical method, while
+the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric
 method based on making the funnel plot symmetric. \citet{Stanley2005-ng,stanley2014meta}
@@
 be a family of dominated probability measures defined on this measurable
-space, and $\mathcal{\Pi}$ a partition of $\mathcal{P}$. Recall
-that a partition of $\mathcal{P}$ is a collection of disjoint non-empty
-subsets $\pi$ of $\mathcal{P}$ such that $\bigcup_{\pi\in\Pi}\pi=\mathcal{P}$.
+space, and $\Pi$ a partition of $\mathcal{P}$. Recall that a partition
+of $\mathcal{P}$ is a collection of disjoint non-empty subsets $\pi$
+of $\mathcal{P}$ such that $\bigcup_{\pi\in\Pi}\pi=\mathcal{P}$.
 When $p$ is a density associated with a $P\in\mathcal{P}$, we will
@@
 \begin{thm}[Gleser--Hwang theorem]
-\label{thm:Gleser--Hwang} Suppose there is a sequence $\{p_{i}\}$
+\label{thm:Gleser--Hwang} Suppose there is a sequence $\{p_{n}\}$
 of densities from $\mathcal{P}$ satisfying the following: 
 \begin{enumerate}
-\item There is a density $p^{\star}$ such that $p_{i}$ converges to $p^{\star}$
+\item There is a density $p^{\star}$ such that $p_{n}$ converges to $p^{\star}$
 pointwise,
-\item $\supp p\supseteq\supp p^{\star}$ for all $p$,
-\item the size of $[p_{i}]$ goes to infinity, $\left\Vert [p_{i}]\right\Vert \to\infty$.
+\item $\supp p\supseteq\supp p^{\star}$ for all densities $p$ derived
+from $\mathcal{P}$,
+\item the size of the equivalence class $[p_{n}]$ goes to infinity as $n$
+increases, $\left\Vert [p_{n}]\right\Vert \to\infty$.
 \end{enumerate}
@@
 say that families $\mathcal{P}$ of probabilities satisfying the conclusion
-of Theorem \ref{thm:Gleser--Hwang} for some suitable partition $\Pi$
+of Theorem \ref{thm:Gleser--Hwang} for a suitable partition $\Pi$
 belong to the Gleser--Hwang class. To make the Gleser--Hwang class
@@
 found in the papers of \citet{gleser1987nonexistence} and \citet{berger1999integrated}.
-\begin{example}[Fieller's problem]
-\label{exa:Fieller's problem} Let $X,Y$ be an observation from
-a bivariate normal $N([\mu_{1},\mu_{2}],I\sigma^{2})$, where $\sigma^{2}$
-is known. We want to form a confidence set for ratio $\mu_{2}/\mu_{1}$.
-The most famous confidence set is due to \citet{Fieller1940-lg}.
-His confidence set can be finite, the whole real line, or the union
-of two disjoint semi-infinite intervals \citep{Koschat1987-dk}, all
-with positive probability.
+
+Fieller's problem is the best known case of a badly behaved confidence
+set. Let $X,Y$ be an observation from a bivariate normal $N([\mu_{1},\mu_{2}],I\sigma^{2})$,
+where $\sigma^{2}$ is known. We want to form a confidence set for
+the ratio $\mu_{2}/\mu_{1}$. The most famous confidence set is due
+to \citet{Fieller1940-lg}. His confidence set can be finite, the
+whole real line, or the union of two disjoint semi-infinite intervals
+\citep{Koschat1987-dk}, all with positive probability.
 
@@
 level $\alpha>0$ has infinite diameter with positive probability.
-\begin{example}[Bahadur--Savage]
-\label{exa:Bahadur--Savage} \citet{bahadur1956nonexistence} studies
-non-parametric testing of the mean, and concludes the mean cannot
-be meaningfully tested. They are working with a family $\mathcal{P}$
-of densities over $\mathbb{R}$ that covers all finite means, has
-finite variances, and is closed under convex combinations. Similar
-problems were considered by \citet{romano2004non} and \citet{Donoho1988-hg}.
+
+\citet{bahadur1956nonexistence} studies non-parametric testing of
+the mean, and concludes the mean cannot be meaningfully tested. They
+are working with a family $\mathcal{P}$ of densities over $\mathbb{R}$
+that covers all finite means, has finite variances, and is closed
+under convex combinations. Similar problems were considered by \citet{romano2004non}
+and \citet{Donoho1988-hg}.
 
@@
 set has infinite diameter with positive probability. Define the partition
-$\Pi$ by $p,q\in\Pi$ if and only if $E_{p}(X)=E_{q}(X)$, and let
+$\Pi$ by $p,q\in\pi$ if and only if $E_{p}(X)=E_{q}(X)$, and let
 $\left\Vert [p]\right\Vert =|E_{p}(X)|$. Let
@@
 infinite diameter with positive probability.
-\end{example}
-
-\end{example}
 
@@
 
-Using Lemma \pageref{lem:generalized shifted exponential} it is not
-hard to show that the basic publication bias model (\ref{eq:selection for significance model})
+Using Lemma \ref{lem:generalized shifted exponential} it is not hard
+to show that the basic publication bias model (\ref{eq:selection for significance model})
 is a member of the Gleser--Hwang class.
@@
 
-Let $f^{1},f^{2},\ldots,f^{K}$ be a sequence of densities, $\pi=(\pi_{1},\pi_{2},\ldots,\pi_{K})$
+Let $f^{1},f^{2},\ldots,f^{K}$ be a sequence of densities, $\pi=(\pi^{1},\pi^{2},\ldots,\pi^{K})$
 a probability vector, and $p=\sum_{k\leq K}\pi^{k}f^{k}$ a mixture
@@
 of $K$-ary mixture distributions and $||[p]||$ be the assumption
-above. Assume there is a sequence $p_{i}=\sum_{k\leq K}\pi_{i}^{k}f_{i}^{k}$
+above. Assume there is a sequence $p_{n}=\sum_{k\leq K}\pi_{n}^{k}f_{n}^{k}$
 and a subset $K'$ such that 
 \begin{enumerate}
-\item For all $k\in K'$, there is a density $f^{k\star}$ such that $f_{i}^{k}$
+\item For all $k\in K'$, there is a density $f^{k\star}$ such that $f_{n}^{k}$
 converges to $f^{k\star}$ pointwise.
@@
 $k\in K'$.
-\item For all $k\in K'$, the size of $[f_{i}^{k}]$ goes to infinity, $\left\Vert [f_{i}^{k}]\right\Vert \to\infty$.
-\item The density concentrates on the components indexed by $K'$, $\lim_{i\to\infty}\sum_{k\in K'}\pi_{i}^{k}=1$.
+\item For all $k\in K'$, the size of $[f_{n}^{k}]$ goes to infinity, $\left\Vert [f_{n}^{k}]\right\Vert \to\infty$.
+\item The density concentrates on the components indexed by $K'$, $\lim_{n\to\infty}\sum_{k\in K'}\pi_{n}^{k}=1$.
 \end{enumerate}
@@
 \begin{proof}
-We employ Theorem \ref{thm:Gleser--Hwang}. By (i) and (iv), $p_{i}$
-converges pointwise to the density $\sum_{k\in K'}\pi_{i}^{k\star}f_{i}^{k\star}=p^{\star}$
+We employ Theorem \ref{thm:Gleser--Hwang}. By (i) and (iv), $p_{n}$
+converges pointwise to the density $\sum_{k\in K'}\pi_{n}^{k\star}f_{n}^{k\star}=p^{\star}$
 . That $\supp p\supseteq p^{\star}$ follows from (ii) and (iv). Finally,
-from the assumption that$\left\Vert [p]\right\Vert =\left\Vert [f_{k}]\right\Vert $,
-we get that $\left\Vert [p]\right\Vert \to\infty$ too. 
+from the assumption that$\left\Vert [p_{n}]\right\Vert =\left\Vert [f_{n}^{k}]\right\Vert $,
+we get that $\left\Vert [p_{n}]\right\Vert \to\infty$ too. 
 \end{proof}
@@
 proofs for $||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$
-are similar and omitted. When $n>1$, expand the expression $\prod_{j=1}^{n}\sum_{k\leq K}\pi_{i}^{k}(\sigma_{j})f_{i}^{k}(\sigma_{j}),$and
+are similar and omitted. When $N>1$, expand the expression $\prod_{j=1}^{n}\sum_{k\leq K}\pi_{i}^{k}(\sigma_{j})f_{i}^{k}(\sigma_{j}),$and
 use the same reasoning as in the first part of this proof.
@@
 If $\int a_{n}d\mu\to\int ad\mu$ and $\int b_{n}d\mu\to\int bd\mu$,
-then $\int f_{n}d\mu\to\int fd\mu$.
+then $\int f_{n}d\mu\to\int fd\mu$ for any measure $\mu$.
 \end{lem}
 
-The proof of Theorem \ref{thm:Gleser--Hwang} follows the proof of
-\citet[Theorem 1]{gleser1987nonexistence} closely. 
+The proof of Theorem \ref{thm:Gleser--Hwang} closely follows the
+proof of \citet[Theorem 1]{gleser1987nonexistence}.
 \begin{proof}[Proof of Theorem \ref{thm:Gleser--Hwang}]
@@
 \end{proof}
-Now we prove Lemma (\ref{lem:generalized shifted exponential}).
+Now we prove Lemma \ref{lem:generalized shifted exponential}.
 \begin{proof}[Proof of Lemma (\ref{lem:generalized shifted exponential})]
 \label{proof:generalized shifted exponential}Let $n^{2}>-c$, so
-that $\sigma_{n}^{2}>0$. Recll the well-known formula for the normal
+that $\sigma_{n}^{2}>0$. Recall the well-known formula for the normal
 truncated to $[a,b]$,
@@
 \[
-c=\sum_{k=1}^{K}\rho_{k}[\Phi(c_{j-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
+c=\sum_{k=1}^{K}\rho^{k}[\Phi(c_{j-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
 \]
-Then $\pi_{K}=\rho_{K}c^{-1}$ and \label{eq:pi_i formula}
+Then $\pi^{K}=\rho^{k}c^{-1}$ and \label{eq:pi_i formula}
 \[
-\pi_{k}=c^{-1}(\rho_{k}-\rho_{K})[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]
+\pi^{k}=c^{-1}(\rho^{k}-\rho^{k})[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]
 \]

### 2020-08-12 infiniteci.tex
Updates from Overleaf
:book: Spellcheck.

@@
 selection function model takes publication bias into account, but
-estimating and infering with this model is tough. Using a generalized
+estimating and inferring with this model is tough. Using a generalized
 Gleser--Hwang theorem, we show there is no confidence set of guaranteed
@@
 
-A meta-analysis is a statistical analysis that quantiatively combines
+A meta-analysis is a statistical analysis that quantitatively combines
 results from separate scientific studies. When the studies measure
@@
 is no reason to trust the results of meta-analytic methods that do
-not account for it, as the parameter estimates will be incosistent
+not account for it, as the parameter estimates will be inconsistent
 \citep{Carter2019-rw}.
@@
 no non-significant studies are published. But even in the fields most
-severely affected by publication bias, such as psychology, a non-negligble
+severely affected by publication bias, such as psychology, a non-negligible
 number of non-significant studies are published \citep{Motyl2017-dx}.
@@
 \end{equation}
-Interpretating Hedges' publication bias model is easy. When the editor
+Interpreting Hedges' publication bias model is easy. When the editor
 receives a study with \emph{p}-value $u$, she finds the $k$ such
@@
 long. The Gleser--Hwang theorem can be used to show that every confidence
-set for $\mu_{2}/\mu_{1}$ must be infinitily long with positive probability.
+set for $\mu_{2}/\mu_{1}$ must be infinitely long with positive probability.
 This result is almost independent of the distribution of $X$ and
@@
 $\theta_{0}$, and equip it with $\left\Vert \pi\right\Vert =\sqrt{\theta_{0}^{2}+\tau^{2}}$.
-This information is summarised in Table \ref{tab:Possible partitions}
+This information is summarized in Table \ref{tab:Possible partitions}
 for convenience.
@@
 not exist, but well-behaved credibility sets do. Bayesian estimation
-of Hedges' model can be made routine, as it is easy to find uncontroverisal
+of Hedges' model can be made routine, as it is easy to find uncontroversial
 priors for $\theta_{0}$ and $\tau$. In practical meta-analyses we
@@
 to $0$. Moreover, since it is common effects in meta-analyses to
-be intepreted as the aggregation of many small effects, the central
+be interpreted as the aggregation of many small effects, the central
 limit theorem justifies using a normal prior. As we want to remove
 prior mass from negative $\theta_{0}$s of large magnitude, $N(0,1)$
-is a decent standard prior. Similarily, a half-normal is a reasonable
+is a decent standard prior. Similarly, a half-normal is a reasonable
 prior for the heterogeneity parameter $\tau$. \citet{moss2019modelling}
@@
 \label{proof:Gleser--Hwang}We can assume without loss of generality
-that $\left\Vert [p_{n}]\right\Vert \geq n$, as we can choose a subsequence
+that $\left\Vert [p_{n}]\right\Vert \geq n$, as we can choose a sub-sequence
 if we have to. By definition of the diameter $D$ (\ref{eq:diameter})
@@
 $\int_{D=\infty\cap\supp p^{\star}}(p/p^{\star})p^{\star}d\mu>0$
-too. It follows that $P(D=\infty)>0$, and, since $P$ is aribtrary,
+too. It follows that $P(D=\infty)>0$, and, since $P$ is arbitrary,
 $D$ has infinite diameter with positive probability.

### 2020-08-12 infiniteci.tex
Updates from Overleaf

--- 2020-08-12 infiniteci.tex
@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[english]{article}
+\documentclass[twoside]{article}
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
 \usepackage{amsmath}
@@
 
+%% almost as usual
+\author{Matthias Templ\\ Vienna University of Technology \And 
+        Second Author\\ Affiliation}
+%% \AND can be used instead of \And and starts a new line
+\title{Guidelines for Submitting a Manuscript to the Austrian Journal of Statistics}
+
+%% for pretty printing and a nice hypersummary also set:
+\Plainauthor{Matthias Templ, Second Author} %% comma-separated
+\Plaintitle{A Capitalized Title: Something about a Topic} %% without formatting
+\Shorttitle{A Capitalized Title} %% a short title (if necessary)
+
+%% an abstract and keywords
+\Abstract{
+  This guideline of the Austrian Journal of Statistics (AJS) shows the required style of manuscripts submitted to the Austrian Journal of Statistics. We highly recommend
+to follow exactly the provided instructions already at the very
+beginning when writing the paper. The present document can be used
+directly as template. The file named {\tt guidelinesAJS.tex} may be
+obtained from the site \href{https://github.com/matthias-da/ajs-public}{https://github.com/matthias-da/ajs-public}.
+
+Manuscripts submitted without considering the AJS style file will be very likely not sent into review, but declined with possibility for re-submission.
+}
+\Keywords{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}
+\Plainkeyword{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}
+
+%% publication information
+%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
+%% \Volume{50}
+%% \Issue{9}
+%% \Month{June}
+%% \Year{2012}
+%% \Submitdate{2012-06-04}
+%% \Acceptdate{2012-06-04}
+%% \setcounter{page}{1}
+\Pages{1--xx}
+
+%% The address of (at least) one author should be given
+%% in the following format:
+\Address{
+  Matthias Templ\\
+  Institue of Data Analysis and Process Design\\
+  Zurich University of Applied Sciences\\
+  CH-8400 Winterthur, Switzerland\\
+  E-mail: \email{matthias.templ@gmail.com}\\
+  URL: \url{https://www.zhaw.ch/de/ueber-uns/person/teml/}
+}
+%% It is also possible to add a telephone and fax number
+%% before the e-mail in the following format:
+%% Telephone: +43/512/507-7103
+%% Fax: +43/512/507-2851
+
+%% for those who use Sweave please include the following line (with % symbols):
+%% need no \usepackage{Sweave.sty}
+
+%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}

### 2020-08-12 infiniteci.tex

--- 2020-08-12 infiniteci.tex
@@
 \providecommand{\theoremname}{Theorem}
+
+%% almost as usual
+\author{Matthias Templ\\ Vienna University of Technology \And 
+        Second Author\\ Affiliation}
+%% \AND can be used instead of \And and starts a new line
+\title{Guidelines for Submitting a Manuscript to the Austrian Journal of Statistics}
+
+%% for pretty printing and a nice hypersummary also set:
+\Plainauthor{Matthias Templ, Second Author} %% comma-separated
+\Plaintitle{A Capitalized Title: Something about a Topic} %% without formatting
+\Shorttitle{A Capitalized Title} %% a short title (if necessary)
+
+%% an abstract and keywords
+\Abstract{
+  This guideline of the Austrian Journal of Statistics (AJS) shows the required style of manuscripts submitted to the Austrian Journal of Statistics. We highly recommend
+to follow exactly the provided instructions already at the very
+beginning when writing the paper. The present document can be used
+directly as template. The file named {\tt guidelinesAJS.tex} may be
+obtained from the site \href{https://github.com/matthias-da/ajs-public}{https://github.com/matthias-da/ajs-public}.
+
+Manuscripts submitted without considering the AJS style file will be very likely not sent into review, but declined with possibility for re-submission.
+}
+\Keywords{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}
+\Plainkeyword{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}
+
+%% publication information
+%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
+%% \Volume{50}
+%% \Issue{9}
+%% \Month{June}
+%% \Year{2012}
+%% \Submitdate{2012-06-04}
+%% \Acceptdate{2012-06-04}
+%% \setcounter{page}{1}
+\Pages{1--xx}
+
+%% The address of (at least) one author should be given
+%% in the following format:
+\Address{
+  Matthias Templ\\
+  Institue of Data Analysis and Process Design\\
+  Zurich University of Applied Sciences\\
+  CH-8400 Winterthur, Switzerland\\
+  E-mail: \email{matthias.templ@gmail.com}\\
+  URL: \url{https://www.zhaw.ch/de/ueber-uns/person/teml/}
+}
+%% It is also possible to add a telephone and fax number
+%% before the e-mail in the following format:
+%% Telephone: +43/512/507-7103
+%% Fax: +43/512/507-2851
+
+%% for those who use Sweave please include the following line (with % symbols):
+%% need no \usepackage{Sweave.sty}
+
+%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-08-12 infiniteci.tex

--- 2020-08-12 infiniteci.tex
@@
-%% LyX 2.3.4.4 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[english]{article}
+\documentclass[article]{ajs}
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
+\usepackage{natbib}
+\usepackage{enumitem}
+\setlist[enumerate]{label = (\roman*)}
 
-\makeatletter
+%%%%%%%%%%%%
+%% Macros %%
+%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
 \providecommand{\tabularnewline}{\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
 \numberwithin{equation}{section}
 \numberwithin{figure}{section}
-\usepackage[natbibapa]{apacite}
 \theoremstyle{plain}
@@
 \newtheorem{lem}[thm]{\protect\lemmaname}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{infiniteci}
-
-\titletag{An arXiv preprint, v2}
-\makeatletter
-\titlerunning{\@title}
-\makeatother
-\authorrunning{Jonas Moss}
+\providecommand{\definitionname}{Definition}
+\providecommand{\examplename}{Example}
+\providecommand{\lemmaname}{Lemma}
+\providecommand{\theoremname}{Theorem}
 
@@
 
-\usepackage{enumitem}
-\setlist[enumerate]{label = (\roman*)}
+%%%%%%%%%%%%%%%%%%
+%% Declarations %%
+%%%%%%%%%%%%%%%%%%
 
-\makeatother
+\author{Jonas Moss \\ University of Oslo}
+\title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
 
-\usepackage{babel}
-\providecommand{\definitionname}{Definition}
-\providecommand{\examplename}{Example}
-\providecommand{\lemmaname}{Lemma}
-\providecommand{\theoremname}{Theorem}
+\Plainauthor{Jonas Moss} 
+\Plaintitle{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model} 
+\Shorttitle{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
 
-\begin{document}
-\title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
-\author{Jonas Moss \orcid{0000-0002-6876-6964}\\
-Department of Mathematics, University of Oslo\\
-PB 1053, Blindern, NO-0316, Oslo, Norway\emph{}\\
-\emph{jonasmgj@math.uio.no}}
-\maketitle
-\begin{abstract}
+\Abstract{
 Meta-analysis, the statistical analysis of results from separate studies,
@@
 selection model is fraught with difficulties.
-\end{abstract}
-\keywords{meta-analysis \and confidence intervals \and file-drawer  problem \and publication bias \and selection models \and weigth function models}
+}
+
+\Keywords{meta-analysis, confidence intervals, file-drawer problem, publication bias, selection models, weight function models}
+\Plainkeywords{meta-analysis, confidence intervals, file-drawer problem, publication bias, selection models, weight function models}
+
+%% publication information
+%% \Volume{50}
+%% \Issue{9}
+%% \Month{June}
+%% \Year{2012}
+%% \Submitdate{2012-06-04}
+%% \Acceptdate{2012-06-04}
+%% \setcounter{page}{1}
+\Pages{1--xx}
+
+\Address{
+  Jonas Moss\\
+  Department of Mathematics\\
+  University of Oslo\\
+  PB 1053, Blindern, NO-0316, Oslo, Norway\\
+  E-mail: \email{jonasmgj@math.uio.no}
+}
+
+\begin{document}
 
@@
 
-\bibliographystyle{apacite}
 \bibliography{infiniteci}

### 2020-08-15 infiniteci.tex
Updates from Overleaf

@@
 one study alone. Meta-analyses are ubiquitous in the empirical sciences
-and forms a key component of most systematic reviews such as Cochrane's
+and forms a key component of most systematic reviews such as Cochrane
 reviews \citep{Higgins2019-vv}.
@@
 of results. But there is ample evidence that the scientific literature
-is not unbiased, as studies with\emph{ }significant \emph{p}-values
+is not unbiased, as studies with\emph{ }significant \textit{p}-values
 tend to be published with a greater probability than other studies
@@
 
-Hedges' \citeyearpar{hedges1992modeling} publication bias model takes
-publication bias explicitly into account using a selection model,
-and is arguably the most appropriate model for publication bias \citep{Carter2019-rw}.
-Despite there being an $\mathtt{R}$ \citep{Team2013-tt} package
-for maximum likelihood estimation of this model, called $\texttt{weightr}$
-\citep{Coburn2019-ec}, the model has not yet taken off. Its maximum
-likelihood estimation methods are numerically unstable and its estimates
-can be off even when they converge \citep{Coburn2019-ec,Stanley2005-ng}.
-The estimate of the mean effect size may be negative and of unrealistically
-large magnitude, and the estimated heterogeneity parameter might be
-improbably large. It turns out there are ridges in the likelihood
-function that can be linked to this behavior \citep{McShane2016-rb},
-but it has not been stated in clear terms exactly what the consequences
-are for inferential procedures. The purpose of this note is to show
-there is no confidence set for the mean effect size that has infinite
-diameter with probability $0$. In the terminology of \citet{berger1999integrated},
-Hedges' publication bias model belongs to the \emph{Gleser--Hwang}
-class.
+Hedges' \citeyearpar{hedges1992modeling} publication bias model takes publication bias explicitly into account using a selection model, and is arguably the most appropriate model for publication bias \citep{Carter2019-rw}.
+Despite there being an $\mathtt{R}$ \citep{Team2013-tt} package for maximum likelihood estimation of this model, called $\texttt{weightr}$ \citep{Coburn2019-ec}, the model has not yet taken off.
+Its maximum likelihood estimation methods are numerically unstable and its estimates can be off even when they converge \citep{Coburn2019-ec,Stanley2005-ng}.
+The estimate of the mean effect size may be negative and of unrealistically large magnitude, and the estimated heterogeneity parameter might be improbably large.
+It turns out there are ridges in the likelihood function that can be linked to this behavior \citep{McShane2016-rb}, but it has not been stated in clear terms exactly what the consequences are for inferential procedures.
+The purpose of this note is to explain why Hedges' publication bias performs poorly, by showing there is no confidence set for the mean effect size that has infinite diameter with probability $0$.
+%In the terminology of \citet{berger1999integrated}, Hedges' publication bias model belongs to the \emph{Gleser--Hwang} class.
 
@@
 
-The most popular and well-known meta-analysis method is the random
-effects model with normal likelihoods \citep{hedges1998fixed}. Written
-in hierarchical notation, it equals
+The most popular and well-known meta-analysis method is the random effects model with normal likelihoods \citep{hedges1998fixed}. Written in hierarchical notation, it equals
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Here $x_{i}$ is the effect size and $\sigma_{i}$ is the standard
-deviation of the $i$th study, and $i=1,\ldots,N$. Following the
-convention in meta-analysis, we assume all $\sigma_{i}$s to be known.
-The mean parameter $\theta$ is the population effect size, $N(\theta_{0},\tau)$
-is the effect size distribution, and $\tau$ is the heterogeneity
-parameter. The purpose of the effect size distribution is to model
-the fact that most effect size estimates plugged into a meta-analysis
-do not appear to measure the same phenomenon. By integrating out $\theta_{i}$,
-we find the density of $x_{i}$,
+Here $x_{i}$ is the effect size and $\sigma_{i}$ is the standard deviation of the $i$th study, and $i=1,\ldots,N$.
+Following the convention in meta-analysis, we assume all $\sigma_{i}$s to be known.
+The mean parameter $\theta$ is the population effect size, $N(\theta_{0},\tau)$ is the effect size distribution, and $\tau$ is the heterogeneity parameter.
+The purpose of the effect size distribution is to model the fact that most effect size estimates plugged into a meta-analysis do not appear to measure the same phenomenon.
+By integrating out $\theta_{i}$, we find the density of $x_{i}$,
 \[
@@
 
-We will assume that the random effects meta-analysis model is true
-in the absence of publication bias. The mechanisms that cause publication
-bias modify the density in a suitable way. Consider the case when
-only significant studies at some specified level $\alpha$ are published.
-Assuming one-sided tests, the \emph{p}-values are $u_{i}=\Phi(-x_{i}/\sigma_{i})$,
-or normal one-sided \emph{p}-values. We will only deal with with one-sided
-\emph{p}-values in this paper, as there is usually, but not always,
-just one direction that is interesting to researchers, reviewers,
-and editors. A one-sided \emph{p}-value can also be used if the researchers
-reported a two-sided value, since $p=0.05$ for a two-sided hypothesis
-corresponds to $p=0.025$ for a one-sided hypothesis, et cetera.
+We will assume that the random effects meta-analysis model is true in the absence of publication bias.
+The mechanisms that cause publication bias modify the density in a suitable way.
+Consider the case when only significant studies at some specified level $\alpha$ are published.
+Assuming one-sided tests, the \textit{p}-values are $u_{i}=\Phi(-x_{i}/\sigma_{i})$, or normal one-sided \textit{p}-values.
+We will only deal with with one-sided \textit{p}-values in this paper, as there is usually, but not always, just one direction that is interesting to researchers, reviewers, and editors.
+A one-sided \textit{p}-value can also be used if the researchers reported a two-sided value, since $p=0.05$ for a two-sided hypothesis corresponds to $p=0.025$ for a one-sided hypothesis, et cetera.
 
-Define $c_{\alpha}=\Phi^{-1}(1-\alpha)$, the cutoff for significance
-at level $\alpha$. The \emph{basic publication bias model} is a truncated
-normal model with density
+Define $c_{\alpha}=\Phi^{-1}(1-\alpha)$, the cutoff for significance at level $\alpha$. The \emph{basic publication bias model} is a truncated normal model with density
 \begin{equation}
@@
 \end{equation}
-This model for publication bias was introduced by \citet{hedges1984estimation}
-in the context of $F$-distributions.
+where $1[A]$ is the characteristic function of $A$. This model for publication bias was introduced by \citet{hedges1984estimation} in the context of $F$-distributions.
 
-The basic publication bias model is unrealistic. It requires that
-no non-significant studies are published. But even in the fields most
-severely affected by publication bias, such as psychology, a non-negligible
-number of non-significant studies are published \citep{Motyl2017-dx}.
-Moreover, the basic publication bias model does not allow for different
-cutoffs for significance. For instance, it is likely that some editors
-will accept studies reaching a significance at $\alpha=0.025$, corresponding
-to $x_{i}/\sigma_{i}>1.96$ but not at $\alpha=0.05$, corresponding
-to $x_{i}/\sigma_{i}>1.64$.
+The basic publication bias model is unrealistic.
+It requires that no non-significant studies are published.
+But even in the fields most severely affected by publication bias, such as psychology, a non-negligible number of non-significant studies are published \citep{Motyl2017-dx}.
+Moreover, the basic publication bias model does not allow for different cutoffs for significance.
+It is likely that some editors will accept studies reaching a significance at $\alpha=0.025$, corresponding to $x_{i}/\sigma_{i}>1.96$ but not at $\alpha=0.05$, corresponding to $x_{i}/\sigma_{i}>1.64$.
 
-These problems can be rectified by adopting the selection model for
-publication bias of \citet{iyengar1988selection}, which models the
-following scenario.
+These problems can be rectified by adopting the selection model for publication bias of \citet{iyengar1988selection}, which models the following scenario.
 \begin{quote}
-\textbf{Publication bias scenario.} Alice the editor receives a study
-with the \emph{p}-value $u$. Her publication decision is a random
-function of this \emph{p}-value. That is, she will publish the study
-with some probability $w(u)$ and reject it with probability $1-w(u)$.
-Every study you will ever read in Alice's journal has survived this
-selection mechanism, the rest are lost forever.
+\textbf{Publication bias scenario.} Alice the editor receives a study with the \textit{p}-value $u$.
+Her publication decision is a random function of this \textit{p}-value.
+That is, she will publish the study with some probability $w(u)$ and reject it with probability $1-w(u)$.
+Every study you will ever read in Alice's journal has survived this selection mechanism, the rest are lost forever.
 \end{quote}
-Let $w(u_{i})$ be a function of the \emph{p}-value $u_{i}=1-\Phi(-x_{i}/\sigma_{i})$
-taking values in $[0,1]$. Then $w(u_{i})$ is a probability for every
-$u_{i}$, and the selection model
+Let $w(u_{i})$ be a function of the \textit{p}-value $u_{i}=\Phi(-x_{i}/\sigma_{i})$ taking values in $[0,1]$. Then $w(u_{i})$ is a probability for every $u_{i}$, and the selection model
 
@@
 \end{equation}
-models the publication bias scenario exactly. This model can be viewed
-as a rejection sampling procedure \citep{flury1990acceptance,von1951various},
-where $\phi$ serves as proposal distribution for $f$. Variants of
-this model, with and without covariates, has been studied by e.g.
+models the publication bias scenario exactly.
+This model can be viewed as a rejection sampling procedure \citep{flury1990acceptance,von1951various}, where $\phi$ serves as proposal distribution for $f$.
+Variants of this model, with and without covariates, has been studied by e.g.
 \citet{Dear1992-gw,Vevea1995-on,Vevea2005-xp,citkowicz2017parsimonious}.
 
-\citet{hedges1992modeling} studies the selection model when $w$
-is a step function with fixed steps. Let $\alpha$ be a vector with
-elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$
-be a $K$-ary non-negative, non-increasing vector having its first
-element equal to $\rho_{1}=1$. Define the step function $w$ based
-on $\alpha$ and $\rho$ as
+\citet{hedges1992modeling} studies the selection model when $w$ is a step function with fixed steps.
+Let $\alpha$ be a vector with elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$ be a $K$-ary non-negative, non-increasing vector having its first element equal to $\rho_{1}=1$ for identifiability.
+Define the step function $w$ based on $\alpha$ and $\rho$ as
 \begin{equation}
@@
 \end{equation}
-We call the selection model with a step function \emph{Hedges' publication
-bias model. }Its density is
+We call the selection model with a step function \emph{Hedges' publication bias model}. Its density is
 \begin{equation}
-f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho^{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1_{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
+f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho^{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
 \end{equation}
-Interpreting Hedges' publication bias model is easy. When the editor
-receives a study with \emph{p}-value $u$, she finds the $k$ such
-that $u\in(\alpha_{k-1},\alpha_{k}]$ and accepts with probability
-$\rho^{k}$. Since $\rho^{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
-The vector $\rho$ is non-increasing since a publication decision
-based solely on \emph{p}-values should always act favorably towards
-lower \emph{p}-values. The parameters $(\theta_{0},\tau,\rho)$ of
-the model are identified when $\alpha$ is fixed \citep[Web Appendix A]{moss2019modelling}.
+Interpreting Hedges' publication bias model is easy.
+When the editor receives a study with \textit{p}-value $u$, she finds the $k$ such that $u\in(\alpha_{k-1},\alpha_{k}]$ and accepts with probability $\rho^{k}$.
+Since $\rho^{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
+The vector $\rho$ is non-increasing since a publication decision based solely on \textit{p}-values should always act favorably towards lower \textit{p}-values.
+The parameters $(\theta_{0},\tau,\rho)$ of the model are identified when $\alpha$ is fixed \citep[Web Appendix A]{moss2019modelling}.
 
-Hedges' publication bias model allows both for non-significant studies
-to be published and allows the editor to act differently towards different
-cutoffs such as $\alpha=0.025$ and $\alpha=0.05$. In addition, the
-model can approximate any non-increasing selection function $w$ by
-increasing the number of steps.
+Hedges' publication bias model allows both for non-significant studies to be published and allows the editor to act differently towards different cutoffs such as $\alpha=0.025$ and $\alpha=0.05$.
+In addition, the model can approximate any non-increasing selection function $w$ by increasing the number of steps.
 
@@
 Here $f^{K}$ is a normal density, $f^{k},k<K$ are normal densities
-truncated to $[\Phi^{-1}(1-\alpha_{j-1}),\Phi^{-1}(1-\alpha))$, and
-$\pi^{k}$ are mixture probabilities, i.e., $\pi^{k}>0$ for each
-$k$ and $\sum_{k=1}^{K}\pi^{k}=1$. The mixture probabilities $\pi^{k}$
-are functions of $(\theta_{0},\tau,\sigma_{i},\rho)$, see the appendix
-(p. \pageref{eq:pi_i formula}) for their formula.
+truncated to $[\Phi^{-1}(1-\alpha_{k-1}),\Phi^{-1}(1-\alpha_k))$, and $\pi^{k}$ are mixture probabilities, i.e., $\pi^{k}>0$ for each $k$ and $\sum_{k=1}^{K}\pi^{k}=1$.
+The mixture probabilities $\pi^{k}$ are functions of $(\theta_{0},\tau,\sigma_{i},\rho)$, see the appendix (p.
+\pageref{eq:pi_i formula}) for their formula.
 
-The main benefit of Hedges' publication bias model (\ref{eq:hedges model})
-is how it models \emph{p}-values based publication bias directly,
-there is no approximation involved. If you believe in the random effects
-meta-analysis model and the \emph{p}-value based publication bias
-scenario, Hedges' publication bias model is simply the correct model.
-Most statistical methods correcting for publication bias in the literature
-either do not make use of an explicit statistical model or do not
-estimate the parameters $\theta_{0}$ and $\tau$. For instance, the
-funnel plot of \citet{Egger1997-rd} is a graphical method, while
-the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric
-method based on making the funnel plot symmetric. \citet{Stanley2005-ng,stanley2014meta}
-discuss various misspecified regression-based estimators of the corrected
-effect size $\theta$ based on the fixed effect Hedges' publication
-bias model. The estimating \emph{p}-curve method of \citet{Simonsohn2014-cn}
-and \emph{p}-uniform of \citet{Van_Assen2015-qs,Van_Aert2016-cu}
-are two methods for dealing with publication bias hailing from psychology.
-Both are based on a variant of the basic publication bias model, but
-with fixed instead of random effects, and both employ somewhat unusual
-estimation methods \citep{McShane2016-rb}. Since there is ample evidence
-of heterogeneity in meta-analysis, restricting oneself to the fixed
-effects meta-analysis is a mistake.
+The main benefit of Hedges' publication bias model (\ref{eq:hedges model}) is how it models \textit{p}-values based publication bias directly, there is no approximation involved.
+If you believe in the random effects meta-analysis model and the \textit{p}-value based publication bias scenario, Hedges' publication bias model is simply the correct model.
+Most statistical methods correcting for publication bias in the literature either do not make use of an explicit statistical model or do not estimate the parameters $\theta_{0}$ and $\tau$.
+For instance, the funnel plot of \citet{Egger1997-rd} is a graphical method, while the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric method based on making the funnel plot symmetric.
+\citet{Stanley2005-ng,stanley2014meta} discuss various misspecified regression-based estimators of the corrected effect size $\theta$ based on the fixed effect Hedges' publication bias model.
+The estimating \textit{p}-curve method of \citet{Simonsohn2014-cn} and \textit{p}-uniform of \citet{Van_Assen2015-qs,Van_Aert2016-cu} are two methods for dealing with publication bias hailing from psychology.
+Both are based on a variant of the basic publication bias model, but with fixed instead of random effects, and both employ somewhat unusual estimation methods \citep{McShane2016-rb}.
+Since there is ample evidence of heterogeneity in meta-analysis, restricting oneself to the fixed effects meta-analysis is a mistake.
 
 Hedges' model has some downsides. It models only bias due to selection
-of \emph{p}-values, not every source of bias, such as language bias
+of \textit{p}-values, not every source of bias, such as language bias
 \citep{Egger1998-kj}. Second, it may not be best model for biases
-with other causes than the publication process, such as \emph{p}-hacking
+with other causes than the publication process, such as \textit{p}-hacking
 \citep{simmons2011false}. \citet{moss2019modelling} propose a related
-model that may be more successful at correcting for \emph{p}-hacking.
+model that may be more successful at correcting for \textit{p}-hacking.
 
@@
 \label{prop:Mixture model corollary} Let $\mathcal{P}$ be a class
-of $K$-ary mixture distributions and $||[p]||$ be the assumption
-above. Assume there is a sequence $p_{n}=\sum_{k\leq K}\pi_{n}^{k}f_{n}^{k}$
+of $K$-ary mixture distributions and $||[p]||$ be as assumed above. Assume there is a sequence $p_{n}=\sum_{k\leq K}\pi_{n}^{k}f_{n}^{k}$
 and a subset $K'$ such that 
@@
 We employ Theorem \ref{thm:Gleser--Hwang}. By (i) and (iv), $p_{n}$
-converges pointwise to the density $\sum_{k\in K'}\pi_{n}^{k\star}f_{n}^{k\star}=p^{\star}$
-. That $\supp p\supseteq p^{\star}$ follows from (ii) and (iv). Finally,
+converges pointwise to the density $$\sum_{k\in K'}\pi_{n}^{k\star}f_{n}^{k\star}=p^{\star}.$$
+That $\supp p\supseteq p^{\star}$ follows from (ii) and (iv). Finally,
 from the assumption that$\left\Vert [p_{n}]\right\Vert =\left\Vert [f_{n}^{k}]\right\Vert $,

### 2020-08-15 infiniteci.tex
:pear: Corrected red lines.

@@
 That is, $\pi_{0}\in C$ if and only if we accept the null-hypothesis
-$H_{0}:\pi=\pi_{0}$, but will only need the formulation using rejection
+$H_{0}:\pi=\pi_{0}$, but we will only need the formulation using rejection
 sets in this paper. When confidence sets are defined in terms of rejection
@@
 The term\emph{ confidence interval} is far more common than confidence
-set, but this requires that $C$ of equation \ref{eq:c-confidence set}
+set, but this requires that the $C$ in equation \ref{eq:c-confidence set}
 is an interval, which we will not require here.
@@
 measure of a normal with mean $\mu$ and standard deviation $\sigma$.
-Furthermore, when $Q$ is a probability measure, $Q^{n}$ denotes
-the $n$-fold product measure of $Q$, corresponding to $n$ independent
-samples from $Q$. Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
+Here $Q^{n}$ denotes the $n$-fold product measure of $Q$, corresponding to $n$ independent samples from $Q$, when $Q$ is a probability measure. Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
 contain all normal probability measures with mean $\mu$ and some
@@
 interval is a confidence set of size $\alpha$ with partition $\{\pi(\mu)\},\mu\in\mathbb{R}$
-according to definition \ref{def:confidence set}.
+according to Definition \ref{def:confidence set}.
 \end{example}
@@
 to \citet{Fieller1940-lg}. His confidence set can be finite, the
-whole real line, or the union of two disjoint semi-infinite intervals
-\citep{Koschat1987-dk}, all with positive probability.
+whole real line, or the union of two disjoint semi-infinite intervals, all with positive probability \citep{Koschat1987-dk}.
 
 But it is not only Fieller's confidence set that might be infinitely
-long. The Gleser--Hwang theorem can be used to show that every confidence
+long. The Gleser--Hwang theorem can be used to show that \textit{every} confidence
 set for $\mu_{2}/\mu_{1}$ must be infinitely long with positive probability.
@@
 
-\citet{bahadur1956nonexistence} studies non-parametric testing of
+Another example is due to \citet{bahadur1956nonexistence}, who studies non-parametric testing of
 the mean, and concludes the mean cannot be meaningfully tested. They
@@
 
-Using the Gleswer--Hwang theorem, it is easy to verify every confidence
+Using the Gleswer--Hwang theorem, it is easy to verify that every confidence
 set has infinite diameter with positive probability. Define the partition
@@
 \begin{thm}
-\label{thm:simple publication bias} Assume $n$ independent samples
-from the basic publication bias model (\ref{eq:selection for significance model}).
-Then, for any $n$, any confidence set for $\theta_{0},\tau$, or
+\label{thm:simple publication bias} Assume we have $N$ independent samples
+from the basic publication bias model (\ref{eq:selection for significance model}). Then any confidence set for $\theta_{0},\tau$, or
 $(\theta_{0},\tau)$ with level $\alpha>0$ will have infinite diameter
@@
 converges to $f^{k\star}$ pointwise.
-\item For all mixtures $p$, $\supp p\supseteq\supp f^{k\star}$ for some
+\item For all mixtures $p$, $\supp p\supseteq\supp f^{k\star}$ for all
 $k\in K'$.
@@
 \begin{thm}
-\label{thm:general publication bias} Assume $n$ independent samples
-from the publication bias model (\ref{eq:selection for significance model}),
-where the selection probability $\rho$ is unknown and $\alpha$ is
-known. Then any confidence set for $\theta_{0},\tau$, or $(\theta_{0},\tau)$
-will have infinite diameter with positive probability.
+\label{thm:general publication bias} Assume we have $N$ independent samples from the publication bias model (\ref{eq:selection for significance model}), where the selection probability $\rho$ is unknown and $\alpha$ is known.
+Then any confidence set for $\theta_{0},\tau$, or $(\theta_{0},\tau)$ will have infinite diameter with positive probability.
 \end{thm}
@@
 \begin{proof}
-\label{proof:general publication bias} Let $n=1$ and consider confidence
-sets for $\theta_{0}$. Let $\Pi$ be the partition of $\mathcal{P}$
-where $p,q\in\pi$ if and only if they share the same $\theta_{0}$,
-and let $||[p]||=|\theta_{0}|$. Then $||f^{k}||=|\theta_{0}|$ from
-the mixture representation (\ref{eq:mixture model formulation}).
-Using Lemma \ref{lem:generalized shifted exponential}, we see that
-$f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$
-and $\sqrt{\tau^{2}+\sigma^{2}}=n^{1/2}$, so that (i), (ii), (iii)
-of Proposition \ref{prop:Mixture model corollary} are satisfied with
-$K'=K\backslash\{1\}$. The mixture probabilities for $k\neq K$ can
-be fixed at e.g. $\pi=1/(K-1)$, and (iv) is satisfied as well. The
-proofs for $||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$
-are similar and omitted. When $N>1$, expand the expression $\prod_{j=1}^{n}\sum_{k\leq K}\pi_{i}^{k}(\sigma_{j})f_{i}^{k}(\sigma_{j}),$and
-use the same reasoning as in the first part of this proof.
+\label{proof:general publication bias} Let $n=1$ and consider confidence sets for $\theta_{0}$.
+Let $\Pi$ be the partition of $\mathcal{P}$ where $p,q\in\pi$ if and only if they share the same $\theta_{0}$, and let $||[p]||=|\theta_{0}|$.
+Then $||f^{k}||=|\theta_{0}|$ from the mixture representation (\ref{eq:mixture model formulation}).
+Using Lemma \ref{lem:generalized shifted exponential}, we see that $f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$ and $\tau_n^{2} = n$, so that (i), (ii), (iii) of Proposition \ref{prop:Mixture model corollary} are satisfied with the set $K'=\{1,2,\ldots, K-1\}$.
+The mixture probabilities for $k\neq K$ can be fixed at e.g.
+$\pi=1/(K-1)$, and (iv) is satisfied as well.
+The proofs for $||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$ are similar and omitted.
+When $N>1$, expand the expression $\prod_{i=1}^{N}\sum_{k<K}\pi_{i}^{k}(\sigma_{i})f_{i}^{k}(\sigma_{i}),$ and use the same reasoning as in the first part of this proof.
 \end{proof}
@@
 \label{proof:Gleser--Hwang}We can assume without loss of generality
-that $\left\Vert [p_{n}]\right\Vert \geq n$, as we can choose a sub-sequence
+that $\left\Vert [p_{n}]\right\Vert \geq n$, as we can choose a suitable sub-sequence
 if we have to. By definition of the diameter $D$ (\ref{eq:diameter})
@@
 \[
-\{D\geq n\}=\{\omega\in\Omega\mid\textrm{there is a }\pi\textrm{ such that}\left\Vert \pi\right\Vert \geq n\textrm{ and }\omega\in R^{c}(\pi)\},
+\{D\geq n\}=\{\omega\in\Omega\mid\textrm{there is a }\pi\textrm{ such that}\left\Vert \pi\right\Vert \geq n\textrm{ and }\omega\in R^{c}(\pi)\}.
 \]
-and if $||[p_{n}]||\geq n$, then $R^{c}([p_{n}])\subseteq\{D\geq n\}$.
+It follows that, if $||[p_{n}]||\geq n$, then $R^{c}([p_{n}])\subseteq\{D\geq n\}$.
 Since we assume that $\left\Vert [p_{n}]\right\Vert \geq n$ and 
@@
 normal distributions become
-\begin{eqnarray*}
-\Phi[-(a+n)(n+c)^{-1/2}] & \approx & \frac{(n+c)^{1/2}}{n+a}\phi[-(a+n)(n+c)^{-1/2}],
-\end{eqnarray*}
+\begin{equation*}
+\Phi[-(a+n)(n+c)^{-1/2}] \approx \frac{(n+c)^{1/2}}{n+a}\phi[-(a+n)(n+c)^{-1/2}],
+\end{equation*}
 and using the same reasoning as above, we find that $\phi[-(a+n)(n+c)^{-1/2}]\approx\phi((n+c)^{1/2})\exp(-a)$
@@
 \end{proof}
-For convenience, we show the formula for the mixture probabilities
-$\pi_{i}$ here. Let $c_{j}=\Phi^{-1}(1-\alpha_{j})$ and define 
+These are the formula for the mixture probabilities
+$\pi_{i}$ here. Let $c_{k}=\Phi^{-1}(1-\alpha_{k})$ and define 
 \[
-c=\sum_{k=1}^{K}\rho^{k}[\Phi(c_{j-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{j};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
+c=\sum_{k=1}^{K}\rho^{k}[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
 \]
-Then $\pi^{K}=\rho^{k}c^{-1}$ and \label{eq:pi_i formula}
+Then $\pi^{K}=\rho^{K}c^{-1}$ and \label{eq:pi_i formula}
 \[
-\pi^{k}=c^{-1}(\rho^{k}-\rho^{k})[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})]
+\pi^{k}=c^{-1}(\rho^{k}-\rho^{k-1})[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
 \]

### 2020-08-17 infiniteci.tex
:pear: Changed mixture formulation.

@@
 \begin{equation}
-f(x_{i};\theta_{0},\sigma_{i})=\Phi\left(\frac{\theta_{0}-c_{\alpha}}{\sqrt{\sigma_{i}^{2}+\tau^{2}}}\right)^{-1}\phi(x;\theta_{0},\sqrt{\sigma_{i}^{2}+\tau^{2}})1[x_{i}/\sigma_{i}>c_{\alpha}],\label{eq:selection for significance model}
+f(x_{i};\theta_{0},\sigma_{i})=\Phi\left(\frac{\theta_{0}-c_{\alpha}}{\sqrt{\sigma_{i}^{2}+\tau^{2}}}\right)^{-1}\phi(x;\theta_{0},\sqrt{\sigma_{i}^{2}+\tau^{2}})1(x_{i}/\sigma_{i}>c_{\alpha}],\label{eq:selection for significance model}
 \end{equation}
@@
 \end{equation}
-Here $f^{K}$ is a normal density, $f^{k},k<K$ are normal densities
-truncated to $[\Phi^{-1}(1-\alpha_{k-1}),\Phi^{-1}(1-\alpha_k))$, and $\pi^{k}$ are mixture probabilities, i.e., $\pi^{k}>0$ for each $k$ and $\sum_{k=1}^{K}\pi^{k}=1$.
+Where $f^{k},k\leq K$ are normal densities
+truncated to $(\Phi^{-1}(1-\alpha_{k-1}),\Phi^{-1}(1-\alpha_k)]$, and $\pi^{k}$ are mixture probabilities, i.e., $\pi^{k}>0$ for each $k$ and $\sum_{k=1}^{K}\pi^{k}=1$.
 The mixture probabilities $\pi^{k}$ are functions of $(\theta_{0},\tau,\sigma_{i},\rho)$, see the appendix (p.
@@
 hard, introducing the heterogeneity parameter exacerbates the problem.
-The likelihood function has contours following approximately $\tau\propto\sqrt{|\theta|}$.
+The likelihood function has contours following approximately $\tau\propto|\theta|^{1/2}$.
 Figure \ref{fig:contour lines} shows the contour lines for the meta-analysis
@@
 \]
-where $p_{0}$ has mean $0$ and $q_{n^{2}}$ has mean $n^{2}$. Then
+where $q_{0}$ has mean $0$ and $q_{n^{2}}$ has mean $n^{2}$. Then
 $\left\Vert [p_{n}]\right\Vert =n$, the conditions of Theorem \ref{thm:Gleser--Hwang}
@@
 Let $f^{1},f^{2},\ldots,f^{K}$ be a sequence of densities, $\pi=(\pi^{1},\pi^{2},\ldots,\pi^{K})$
-a probability vector, and $p=\sum_{k\leq K}\pi^{k}f^{k}$ a mixture
-distribution. We will assume that the size of $[p]$ equals the size
-of any of its mixture components $[f^{k}]$ for some size $\left\Vert \cdot\right\Vert $,
+be a probability vector, and $p=\sum_{k\leq K}\pi^{k}f^{k}$ be a mixture distribution.
+We will assume that the size of $[p]$ equals the size of any of its mixture components $[f^{k}]$ for some size $\left\Vert \cdot\right\Vert $,
 i.e., $\left\Vert [p]\right\Vert =\left\Vert [f^{k}]\right\Vert $
@@
 converges to $f^{k\star}$ pointwise.
-\item For all mixtures $p$, $\supp p\supseteq\supp f^{k\star}$ for all
+\item For all mixtures $p$, $\supp p\supseteq\supp f^{k\star}$ for some
 $k\in K'$.
@@
 Then $||f^{k}||=|\theta_{0}|$ from the mixture representation (\ref{eq:mixture model formulation}).
-Using Lemma \ref{lem:generalized shifted exponential}, we see that $f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$ and $\tau_n^{2} = n$, so that (i), (ii), (iii) of Proposition \ref{prop:Mixture model corollary} are satisfied with the set $K'=\{1,2,\ldots, K-1\}$.
+Using Lemma \ref{lem:generalized shifted exponential}, we see that $f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$ and $\tau_n^{2} = n$, so that (i), (ii), (iii) of Proposition \ref{prop:Mixture model corollary} are satisfied with the set $K'=\{1,2,\ldots, K-1\}$, which is sufficient since we assume that $\rho$ is decreasing.
 The mixture probabilities for $k\neq K$ can be fixed at e.g.
@@
 These are the formula for the mixture probabilities
-$\pi_{i}$ here. Let $c_{k}=\Phi^{-1}(1-\alpha_{k})$ and define 
+$\pi_{i}$, see \eqref{eq:mixture model formulation}. Let $c_{k}=\Phi^{-1}(1-\alpha_{k})$ and define 
 \[
@@
 \]
-Then $\pi^{K}=\rho^{K}c^{-1}$ and \label{eq:pi_i formula}
+Then \label{eq:pi_i formula}
 \[
-\pi^{k}=c^{-1}(\rho^{k}-\rho^{k-1})[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
+\pi^{k}=c^{-1}\rho^{k}[\Phi(c_{k-1};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})-\Phi(c_{k};\theta_{0},(\tau^{2}+\sigma_{i}^{2})^{1/2})].
 \]

### 2020-08-17 infiniteci.tex
:pear: First check of proofs.

@@
 Then $||f^{k}||=|\theta_{0}|$ from the mixture representation (\ref{eq:mixture model formulation}).
-Using Lemma \ref{lem:generalized shifted exponential}, we see that $f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$ and $\tau_n^{2} = n$, so that (i), (ii), (iii) of Proposition \ref{prop:Mixture model corollary} are satisfied with the set $K'=\{1,2,\ldots, K-1\}$, which is sufficient since we assume that $\rho$ is decreasing.
-The mixture probabilities for $k\neq K$ can be fixed at e.g.
+Using Lemma \ref{lem:generalized shifted exponential}, we see that $f^{k},k<K$ converges pointwise to truncated exponentials when $\theta_{0}=-n$ and $\tau_n^{2} = n$, so that (i), (iii) of Proposition \ref{prop:Mixture model corollary} are satisfied with the set $K'=\{1,2,\ldots, K-1\}$.
+Moreover, since we assume that $\rho$ is decreasing, (ii) is satisfied as well.
+The mixture probabilities for $k \neq K$ can be fixed at e.g.
 $\pi=1/(K-1)$, and (iv) is satisfied as well.
 The proofs for $||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$ are similar and omitted.
+
 When $N>1$, expand the expression $\prod_{i=1}^{N}\sum_{k<K}\pi_{i}^{k}(\sigma_{i})f_{i}^{k}(\sigma_{i}),$ and use the same reasoning as in the first part of this proof.

### 2020-08-17 infiniteci.tex
:apple: Read to Example 2.

@@
 It turns out there are ridges in the likelihood function that can be linked to this behavior \citep{McShane2016-rb}, but it has not been stated in clear terms exactly what the consequences are for inferential procedures.
-The purpose of this note is to explain why Hedges' publication bias performs poorly, by showing there is no confidence set for the mean effect size that has infinite diameter with probability $0$.
+The purpose of this note is to explain why Hedges' publication bias performs poorly, by showing there is no confidence set for the mean effect size that has infinite diameter with probability zero.
 %In the terminology of \citet{berger1999integrated}, Hedges' publication bias model belongs to the \emph{Gleser--Hwang} class.
@@
 \end{eqnarray*}
-Here $x_{i}$ is the effect size and $\sigma_{i}$ is the standard deviation of the $i$th study, and $i=1,\ldots,N$.
+xzHere $x_{i}$ is the effect size and $\sigma_{i}$ is the standard deviation of the $i$th study,  $i=1,\ldots,N$.
 Following the convention in meta-analysis, we assume all $\sigma_{i}$s to be known.
-The mean parameter $\theta$ is the population effect size, $N(\theta_{0},\tau)$ is the effect size distribution, and $\tau$ is the heterogeneity parameter.
+The mean parameter $\theta_0$ is the population effect size, $N(\theta_{0},\tau)$ is the effect size distribution, and $\tau$ is the heterogeneity parameter.
 The purpose of the effect size distribution is to model the fact that most effect size estimates plugged into a meta-analysis do not appear to measure the same phenomenon.
@@
 \citet{hedges1992modeling} studies the selection model when $w$ is a step function with fixed steps.
-Let $\alpha$ be a vector with elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$ be a $K$-ary non-negative, non-increasing vector having its first element equal to $\rho_{1}=1$ for identifiability.
+Let $\alpha$ be a vector with elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$ be a $K$-ary non-negative, non-decreasing vector having its first element equal to $\rho_{1}=1$ for identifiability.
 Define the step function $w$ based on $\alpha$ and $\rho$ as
@@
 of \citet{Cuddy2018-kp} where the selection probabilities of the
-step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$.
-Only just around the maximum at $\hat{\theta}_{0}=0.55$ and $\hat{\sigma}=5\cdot10^{-7}$
+step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$ and $\alpha = (0, 0.025, 0.05, 1$. Only just around the maximum at $\hat{\theta}_{0}=0.55$ and $\hat{\sigma}=5\cdot10^{-7}$
 can the likelihood be approximated with a quadratic function.
@@
 When $p$ is a density associated with a $P\in\mathcal{P}$, we will
-use the standard notation $[p]$ to denote the unique $\pi$ containing
+use the standard notation $[p]$ to denote the unique part $\pi$ containing
 $P$. 
@@
 \label{exa:t-test} Consider the usual \emph{t}-confidence interval
-with $n$ observations. Here $\mathcal{P}$ contains all measures
+with $n$ observations. In this case, $\mathcal{P}$ contains all measures
 $P_{\mu,\sigma}^{n}$, where $P_{\mu,\sigma}$ is the probability
@@
 density truncated to $[a,b)$, where $b=\infty$ is allowed, with
-underlying mean $\theta_{n}=-n$ and standard deviation $\sigma_{n}^{2}=n^{2}+c$
+underlying mean $\theta_{n}=-n$ and standard deviation $\sigma_{n}^{2}=n+c$
 for some $c\in\mathbb{R}$. Then $f_{n}$ converges pointwise to $\exp(-x)/[\exp(-a)-\exp(-b)]$,
@@
 \begin{proof}[Proof of Lemma (\ref{lem:generalized shifted exponential})]
-\label{proof:generalized shifted exponential}Let $n^{2}>-c$, so
+\label{proof:generalized shifted exponential}Let $n>-c$, so
 that $\sigma_{n}^{2}>0$. Recall the well-known formula for the normal
-truncated to $[a,b]$,
+truncated to $[a,b]$, and substitute $\theta_n = -n$ and $\sigma^2_n = n + c$,
 \begin{eqnarray}
@@
 From Equation 5 of \citet{borjesson1979simple}, we know that $\Phi(-x)\approx\phi(x)/x$
-as $x$ grows. The part of (\ref{eq:truncated}) involving cumulative
-normal distributions become
+as $x$ grows. Then
 \begin{equation*}

### 2020-08-17 infiniteci.tex
:pear: Made arXiv version.

@@
-\documentclass[article]{ajs}
+% \documentclass[english]{article}
+% \usepackage[T1]{fontenc}
+% \usepackage[utf8]{inputenc}
+% \usepackage[english]{babel}
+% \usepackage{amsmath}
+% \usepackage{amsthm}
+% \usepackage{amssymb}
+% \usepackage{graphicx}
+% \usepackage{natbib}
+% \usepackage{enumitem}
+% \setlist[enumerate]{label = (\roman*)}
+
+% %%%%%%%%%%%%
+% %% Macros %%
+% %%%%%%%%%%%%
+
+% \providecommand{\tabularnewline}{\\}
+% \numberwithin{equation}{section}
+% \numberwithin{figure}{section}
+% \theoremstyle{plain}
+% \newtheorem{thm}{\protect\theoremname}
+% \theoremstyle{definition}
+% \newtheorem{defn}[thm]{\protect\definitionname}
+% \theoremstyle{definition}
+% \newtheorem{example}[thm]{\protect\examplename}
+% \theoremstyle{plain}
+% \newtheorem{lem}[thm]{\protect\lemmaname}
+% \providecommand{\definitionname}{Definition}
+% \providecommand{\examplename}{Example}
+% \providecommand{\lemmaname}{Lemma}
+% \providecommand{\theoremname}{Theorem}
+
+% \renewcommand{\sqrt}[1]{{(#1)^{1/2}}}
+% \DeclareMathOperator{\tr}{tr}
+% \DeclareMathOperator{\Tr}{Tr}
+% \DeclareMathOperator{\Var}{Var}
+% \DeclareMathOperator{\argmin}{argmin}
+% \DeclareMathOperator{\Cor}{Cor}
+% \DeclareMathOperator{\Cov}{Cov}
+% \DeclareMathOperator{\diag}{diag} 
+% \DeclareMathOperator{\argmax}{argmax}
+% \DeclareMathOperator{\supp}{supp}
+
+%%%%%%%%%%%%%%%%%%
+%% Declarations %%
+%%%%%%%%%%%%%%%%%%
+
+% \author{Jonas Moss \\ University of Oslo}
+% \title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
+
+% \Plainauthor{Jonas Moss} 
+% \Plaintitle{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model} 
+% \Shorttitle{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
+
+% \Abstract{
+% Meta-analysis, the statistical analysis of results from separate studies,
+% is a fundamental building block of science. But the assumptions of
+% classical meta-analysis models are not satisfied whenever publication
+% bias is present, which causes inconsistent parameter estimates. Hedges'
+% selection function model takes publication bias into account, but
+% estimating and inferring with this model is tough. Using a generalized
+% Gleser--Hwang theorem, we show there is no confidence set of guaranteed
+% finite diameter for the parameters of Hedges' selection model. This
+% result provides a partial explanation for why inference with Hedges'
+% selection model is fraught with difficulties.
+% }
+
+% \Keywords{meta-analysis, confidence intervals, file-drawer problem, publication bias, selection models, weight function models}
+% \Plainkeywords{meta-analysis, confidence intervals, file-drawer problem, publication bias, selection models, weight function models}
+
+%% publication information
+%% \Volume{50}
+%% \Issue{9}
+%% \Month{June}
+%% \Year{2012}
+%% \Submitdate{2012-06-04}
+%% \Acceptdate{2012-06-04}
+%% \setcounter{page}{1}
+% \Pages{1--xx}
+
+% \Address{
+%   Jonas Moss\\
+%   Department of Mathematics\\
+%   University of Oslo\\
+%   PB 1053, Blindern, NO-0316, Oslo, Norway\\
+%   E-mail: \email{jonasmgj@math.uio.no}
+% }
+
+%% LyX 2.3.4.4 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
+\documentclass[english,twoside]{article}
 \usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
+\usepackage[latin9]{inputenc}
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
-\usepackage{natbib}
-\usepackage{enumitem}
-\setlist[enumerate]{label = (\roman*)}
 
-%%%%%%%%%%%%
-%% Macros %%
-%%%%%%%%%%%%
+\makeatletter
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% Because html converters don't know tabularnewline
 \providecommand{\tabularnewline}{\\}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
 \numberwithin{equation}{section}
 \numberwithin{figure}{section}
+\usepackage[natbibapa]{apacite}
 \theoremstyle{plain}
@@
 \newtheorem{lem}[thm]{\protect\lemmaname}
-\providecommand{\definitionname}{Definition}
-\providecommand{\examplename}{Example}
-\providecommand{\lemmaname}{Lemma}
-\providecommand{\theoremname}{Theorem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage{infiniteci}
+
+\titletag{An arXiv preprint, v2}
+\makeatletter
+\titlerunning{\@title}
+\makeatother
+\authorrunning{Jonas Moss}
 
@@
 
-%%%%%%%%%%%%%%%%%%
-%% Declarations %%
-%%%%%%%%%%%%%%%%%%
+\usepackage{enumitem}
+\setlist[enumerate]{label = (\roman*)}
 
-\author{Jonas Moss \\ University of Oslo}
+\makeatother
+
+\usepackage{babel}
+\providecommand{\definitionname}{Definition}
+\providecommand{\examplename}{Example}
+\providecommand{\lemmaname}{Lemma}
+\providecommand{\theoremname}{Theorem}
+
+\begin{document}
 \title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
-
-\Plainauthor{Jonas Moss} 
-\Plaintitle{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model} 
-\Shorttitle{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
-
-\Abstract{
+\author{Jonas Moss \orcid{0000-0002-6876-6964}\\
+Department of Mathematics, University of Oslo\\
+PB 1053, Blindern, NO-0316, Oslo, Norway\emph{}\\
+\emph{jonasmgj@math.uio.no}}
+\maketitle
+\begin{abstract}
 Meta-analysis, the statistical analysis of results from separate studies,
@@
 selection model is fraught with difficulties.
-}
-
-\Keywords{meta-analysis, confidence intervals, file-drawer problem, publication bias, selection models, weight function models}
-\Plainkeywords{meta-analysis, confidence intervals, file-drawer problem, publication bias, selection models, weight function models}
-
-%% publication information
-%% \Volume{50}
-%% \Issue{9}
-%% \Month{June}
-%% \Year{2012}
-%% \Submitdate{2012-06-04}
-%% \Acceptdate{2012-06-04}
-%% \setcounter{page}{1}
-\Pages{1--xx}
-
-\Address{
-  Jonas Moss\\
-  Department of Mathematics\\
-  University of Oslo\\
-  PB 1053, Blindern, NO-0316, Oslo, Norway\\
-  E-mail: \email{jonasmgj@math.uio.no}
-}
-
-\begin{document}
+\end{abstract}
+\keywords{meta-analysis \and confidence intervals \and file-drawer  problem \and publication bias \and selection models \and weight function models}
 
@@
 of results. But there is ample evidence that the scientific literature
-is not unbiased, as studies with\emph{ }significant \textit{p}-values
+is not unbiased, as studies with significant \textit{p}-values
 tend to be published with a greater probability than other studies
@@
 The likelihood function has contours following approximately $\tau\propto|\theta|^{1/2}$.
-Figure \ref{fig:contour lines} shows the contour lines for the meta-analysis
-of \citet{Cuddy2018-kp} where the selection probabilities of the
-step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$ and $\alpha = (0, 0.025, 0.05, 1$. Only just around the maximum at $\hat{\theta}_{0}=0.55$ and $\hat{\sigma}=5\cdot10^{-7}$
-can the likelihood be approximated with a quadratic function.
-
-\begin{figure}
+\begin{figure}[t]
 \noindent \begin{centering}
-\includegraphics[scale=0.5]{chunks/cuddy}
+\includegraphics[scale = 0.5]{chunks/cuddy}
 \par\end{centering}
@@
 the simple publication model using power posing data of \citet{Cuddy2018-kp}. }
-
 \end{figure}
+Figure \ref{fig:contour lines} shows the contour lines for the meta-analysis of \citet{Cuddy2018-kp} where the selection probabilities of the step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$ and $\alpha = (0, 0.025, 0.05, 1$.
+Only just around the maximum at $\hat{\theta}_{0}=0.55$ and $\hat{\sigma}=5\cdot10^{-7}$
+can the likelihood be approximated with a quadratic function.
 
@@
 measure of a normal with mean $\mu$ and standard deviation $\sigma$.
-Here $Q^{n}$ denotes the $n$-fold product measure of $Q$, corresponding to $n$ independent samples from $Q$, when $Q$ is a probability measure. Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
+Here $Q^{n}$ denotes the $n$-fold product measure of $Q$, corresponding to $n$ independent samples from $Q$ when $Q$ is a probability measure. Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
 contain all normal probability measures with mean $\mu$ and some
@@
 \end{equation}
-That is, the diameter tells you the size of the largest accepted $\pi$.
+The diameter tells you the size of the largest accepted $\pi$.
 We will assume that $D$ is Borel measurable.
@@
 \label{thm:Gleser--Hwang} Suppose there is a sequence $\{p_{n}\}$
-of densities from $\mathcal{P}$ satisfying the following: 
+of densities derived from $\mathcal{P}$ satisfying the following: 
 \begin{enumerate}
@@
 Fieller's problem is the best known case of a badly behaved confidence
-set. Let $X,Y$ be an observation from a bivariate normal $N([\mu_{1},\mu_{2}],I\sigma^{2})$,
+set. Let $(X,Y)$ be an observation from a bivariate normal $N([\mu_{1},\mu_{2}],I\sigma^{2})$,
 where $\sigma^{2}$ is known. We want to form a confidence set for
@@
 
+\bibliographystyle{apacite}
 \bibliography{infiniteci}

### 2022-03-03 infiniteci.tex
First revision for Korean.

@@
 
-\titletag{An arXiv preprint, v2}
+\titletag{Submission to Journal of the Korean Statistical Society}
 \makeatletter
@@
 \author{Jonas Moss \orcid{0000-0002-6876-6964}\\
-Department of Mathematics, University of Oslo\\
-PB 1053, Blindern, NO-0316, Oslo, Norway\emph{}\\
-\emph{jonasmgj@math.uio.no}}
+Department of Data Science and Analytics \\
+BI Norwegian Business School\emph{}\\
+\emph{jonas.moss@bi.no}}
 \maketitle
@@
 selection function model takes publication bias into account, but
-estimating and inferring with this model is tough. Using a generalized
+estimating and inferring with this model is tough {\color{black} for some datasets}. Using a generalized
 Gleser--Hwang theorem, we show there is no confidence set of guaranteed
@@
 \theta_{i} & \sim & N(\theta_{0},\tau),\\
-x_{i}\mid\theta_{i},\sigma & \sim & N(\theta_{i},\sigma_{i}).
+x_{i}\mid\theta_{i},\sigma_i & \sim & N(\theta_{i},\sigma_{i}).
 \end{eqnarray*}
-xzHere $x_{i}$ is the effect size and $\sigma_{i}$ is the standard deviation of the $i$th study,  $i=1,\ldots,N$.
+Here $x_{i}$ is the effect size and $\sigma_{i}$ is the standard deviation of the $i$th study,  $i=1,\ldots,N$.
 Following the convention in meta-analysis, we assume all $\sigma_{i}$s to be known.
@@
 Let $w(u_{i})$ be a function of the \textit{p}-value $u_{i}=\Phi(-x_{i}/\sigma_{i})$ taking values in $[0,1]$. Then $w(u_{i})$ is a probability for every $u_{i}$, and the selection model
-
 \begin{equation}
@@
 \citet{hedges1992modeling} studies the selection model when $w$ is a step function with fixed steps.
-Let $\alpha$ be a vector with elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$ be a $K$-ary non-negative, non-decreasing vector having its first element equal to $\rho_{1}=1$ for identifiability.
+Let $\alpha$ be a vector with elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$ be a $K$-ary non-negative, non-increasing vector having its first element equal to $\rho_{1}=1$ for identifiability.
 Define the step function $w$ based on $\alpha$ and $\rho$ as
@@
 
+{\color{black}It is probably not possible to generalize the results of this paper to selection models that do no follow the step function model.
+Lemma \ref{lem:generalized shifted exponential}, about the truncated normal, is crucial in the proof of our main result, Theorem \ref{thm:general publication bias}.
+Truncated densities only appear in step function models, not models with continuous selection functions, such as the Probit selection function of \cite{Copas2013-qi} or the one-parameter selection functions of \cite{Preston2004-pv}.}
+
 Hedges' publication bias model allows both for non-significant studies to be published and allows the editor to act differently towards different cutoffs such as $\alpha=0.025$ and $\alpha=0.05$.
 In addition, the model can approximate any non-increasing selection function $w$ by increasing the number of steps.
+{\color{black}In applications, the parameters $\mu$, $\tau$, and $\rho$ are estimated from the data, while $\alpha$ is fixed by the researcher, for instance at $\alpha = (0.025, 0.05, 1)$.
+We recommend using these cutoffs, as it is well known that applied journals frequently demand statistical significance at this level.
+Since both two-sided and one-sided \emph{p}-values occur, we need to include $0.025$ in addition to $0.05$.}
 
@@
 
-Estimation of Hedges' model is difficult. \citet[Section 6.3]{Stanley2005-ng}
+{\color{black} Hedges' model can be hard to estimate, especially if the data is unfavourable}. \citet[Section 6.3]{Stanley2005-ng}
 discusses three problematic cases in economics when maximum likelihood
@@
 \end{figure}
-Figure \ref{fig:contour lines} shows the contour lines for the meta-analysis of \citet{Cuddy2018-kp} where the selection probabilities of the step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$ and $\alpha = (0, 0.025, 0.05, 1$.
+Figure \ref{fig:contour lines} shows the contour lines for the meta-analysis of \citet{Cuddy2018-kp} where the selection probabilities of the step function (\ref{eq:step function}) are fixed at $\rho=(1,0.6,0.1)$ and $\alpha = (0, 0.025, 0.05, 1)$.
 Only just around the maximum at $\hat{\theta}_{0}=0.55$ and $\hat{\sigma}=5\cdot10^{-7}$
 can the likelihood be approximated with a quadratic function.
+
+{\color{black} Estimation of Hedges' model is especially hard when almost all observations lie close to the the cutoffs.
+In our experience, estimation works well when the data is sufficiently well spread, for instance when some observations are far away from the cutoffs and there are observations that have failed to reach significance.
+As a simple example of a case when estimation fails to work, consider the observation vector $x = (1.96, 1.96, 1.96, 1.96, 1.96, 1.64, 1.64, 1.64, 1.64, 1.64, -1)$ when the standard deviation of each observation is $\sigma_i=1$.
+We employ $\alpha = (0, 0.025, 0.05, 1)$, which implies cutoffs at $\Phi^{-1}(0.975)$ and $\Phi^{-1}(0.95)$.
+In this case, $10$ out of $11$ observations are very close to the cutoffs.
+When we run the Hedges selection model on this data, using the $\mathtt{sel}$ function of the $\mathtt{R}$ package $\mathtt{metafor}$ \citet{Viechtbauer2010-cf}, the model does not converge.
+If the last observation is changed to $0$ instead of $-1$, the model converges, but the Hessian cannot be inverted, and the parameter estimate for $\theta_0$ equals $-1.8$.
+Situations similar to this one are most common when $n$ is small.}
 
@@
 $P$.
+{\color{black} Instead of partitions, we could have used a formulation with main parameters $\theta$ and nuisance parameters $\eta$, and defined the rejection set for $\theta$ as $\sup_{\eta}\sup_{\theta}P_{\theta,\eta}(R(\theta))\leq\alpha$.
+We have decided to use partitions for two reasons: First, there are no unambiguous nuisance and main parameters in our applications, making notation using nuisance parameters confusing.
+Second, the upcoming Theorem \ref{thm:Gleser--Hwang} can be applied in purely non-parametric situations, where the mention of nuisance and main parameters is even more confusing.}
 \begin{defn}
@@
 The following example should make Definition \ref{def:confidence set}
-familiar.
+clearer. 
 \begin{example}
@@
 measure of a normal with mean $\mu$ and standard deviation $\sigma$.
-Here $Q^{n}$ denotes the $n$-fold product measure of $Q$, corresponding to $n$ independent samples from $Q$ when $Q$ is a probability measure. Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
+Here $Q^{n}$ denotes the $n$-fold product measure of $Q$, corresponding to $n$ independent samples from $Q$ when $Q$ is a probability measure.
+{\color{black} The \emph{t}-confidence interval is an exact confidence interval for $\mu$ no matter what $\sigma>0$, the nuisance parameter, is.
+Since the test is exact, rejection sets $R(\mu)$ satisfy $P^n_{\mu,\sigma}(R(\mu))=\alpha$ for all $\sigma,\mu$.} We can formulate the confidence set in terms of partitions too.
+Let $\pi(\mu)=\{P_{\mu,\sigma}^{n}\mid\sigma>0\}$
 contain all normal probability measures with mean $\mu$ and some
 positive standard deviation. Then $\{\pi(\mu)\},\mu\in\mathbb{R}$
-defines a partition of $\mathcal{P}$. A two-sided \emph{t}-confidence
-interval is a confidence set of size $\alpha$ with partition $\{\pi(\mu)\},\mu\in\mathbb{R}$
+defines a partition of $\mathcal{P}$. Then the two-sided \emph{t}-confidence
+interval is a confidence set of size $\alpha$ with partition {\color{black}$\Pi = \{\pi(\mu)\},\mu\in\mathbb{R}$}
 according to Definition \ref{def:confidence set}.
@@
 
-Now we must find out how to measure the size of confidence sets. Let
-a \emph{size function} be any positive function $\left\Vert \cdot\right\Vert :\Pi\to[0,\infty)$.
-In the \emph{t}-confidence interval example above, $\left\Vert \cdot\right\Vert $
+{\color{black} Now we must find out how to measure the size of confidence sets.
+To make our results as general as possible, we will let the \emph{size function} be any non-negative function $\left\Vert \cdot\right\Vert :\Pi\to[0,\infty)$.
+In most cases, the size function will be a norm, but any non-negative function is a valid size function.
+For instance, in the \emph{t}-confidence interval example above, $\left\Vert \cdot\right\Vert $
 can be taken to be $\left\Vert \pi\right\Vert =|\mu|$ for the unique
-$\mu$ associated with each $\pi$.
+$\mu$ associated with each $\pi$. }
 
@@
 
-This is a modified Gleser--Hwang theorem \citep[Theorem 1]{gleser1987nonexistence}
-formulated in terms of partitions. Its proof is in the appendix (p.
+{\color{black} The original Gleser--Hwang theorem \citep[Theorem 1]{gleser1987nonexistence} is defined for pairs of parameters $\theta_1,\theta_2$, where $\theta_2$ is a nuisance parameter and the confidence set is constructed for a functional $\gamma(\theta_1)$.
+The following generalization does not require any nuisance parameters.
+Using partitions, it can be used both with and without nuisance parameters, as well as in non-parametric settings.} Its proof is in the appendix (p.
 \pageref{proof:Gleser--Hwang}).
@@
 long. The Gleser--Hwang theorem can be used to show that \textit{every} confidence
-set for $\mu_{2}/\mu_{1}$ must be infinitely long with positive probability.
+set for $E(Y)/E(X)$ must be infinitely long with positive probability.
 This result is almost independent of the distribution of $X$ and
@@
 
-Using the Gleswer--Hwang theorem, it is easy to verify that every confidence
+Using the Gleser--Hwang theorem, it is easy to verify that every confidence
 set has infinite diameter with positive probability. Define the partition
@@
 \begin{lem}[{\citet[Exercise 16.4(a)]{billingsley1995probability}}]
-\label{lem:Dominated covergence theorem} Suppose $a_{n},b_{n},f_{n}$
-converge to $a,b,f$ and $a_{n}\leq f_{n}\leq b_{n}$ for all $n$.
+\label{lem:Dominated covergence theorem} Suppose the functions $a_{n},b_{n},f_{n}$
+converge pointwise to $a,b,f$ and $a_{n}\leq f_{n}\leq b_{n}$ for all $n$.
 If $\int a_{n}d\mu\to\int ad\mu$ and $\int b_{n}d\mu\to\int bd\mu$,

### 2022-03-03 R/failed_convergence.R

@@ -1,0 +1,19 @@
+data1 <- cbind(yi = c(rep(1.96, 5), rep(1.65, 5), -1), vi = rep(1, 11))
+res <- rma(yi, vi, data = data, method = "ML", digits = 3)
+sel1 <- selmodel(res,
+  type = "stepfun", 
+  alternative = "greater",
+  steps = c(.025, .05, 1), 
+  verbose = TRUE
+)
+sel1
+
+data2 <- cbind(yi = c(rep(1.96, 5), rep(1.65, 5), 0), vi = rep(1, 11))
+res <- rma(yi, vi, data = data, method = "ML", digits = 3)
+sel2 <- selmodel(res,
+  type = "stepfun", 
+  alternative = "greater",
+  steps = c(.025, .05, 1), 
+  verbose = TRUE
+)
+sel2

### 2022-10-02 R/cuddy.R
Using eps.

@@ -32,7 +32,8 @@ z = outer(X = x, Y = y, FUN = FUN)
 
 solution = abs(nlm(objective, p = c(0.2, 0.01))$estimate) # 5.53-01 -4.99-07
 
-pdf("chunks/cuddy.pdf")
+setEPS()
+postscript("chunks/cuddy.eps")
 contour(
   x = x, 
   y = y, 

### 2022-10-02 response_1.tex

\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\title{Response to reviewer 1 on infinite CI}
\begin{document}
\maketitle
I wish to thank you for a very constructive review.

Major modifications to the manuscript are marked in red and copied into this document. There might be very slight (one the level of spelling error) deviations between the red blocks in this response document and the corresponding blocks in the manuscript.

\section*{Spelling and minor comments}Thank you for informing me about these. They have been fixed.

\section*{Response to comments}

\begin{quotation}The mathematical conditions are vaguely described. For example, see the definition of the size function on page 5, which allows any positive function. Since the size function determines the diameter, a more precise condition is needed there. In the original Gleser-Hwang theorem, the two sets of parameters are treated differently (In their paper, $\theta_1$ and $\theta_2$). In this article, there is no distinction between the two sets so that the conditions of Theorem 4 seem too concise.
\end{quotation}
I modified the relevant paragraph clarifying that, indeed, any non-negative size function is actually allowed. (We do not use any properties such as the triangle inequality or homogeneity.)

{\color{red} Now we must find out how to measure the size of confidence sets. To make our results as general as possible, we will let the \emph{size function} be any non-negative function $\left\Vert \cdot\right\Vert :\Pi\to[0,\infty)$. In most cases, the size function will be a norm, but any non-negative function is a valid size function. For instance, in the \emph{t}-confidence interval example above, $\left\Vert \cdot\right\Vert $
can be taken to be $\left\Vert \pi\right\Vert =|\mu|$ for the unique
$\mu$ associated with each $\pi$. }

It is true that Gleser--Hwang formulates their Theorem using two parameters, where one is a nuisance parameter and one is the parameter of interest. Their results do not depend on this detail, however, as we show in Theorem 4. We modified the sentence preceding Theorem 4 to make it clear:

{\color{red} The original Gleser--Hwang theorem is defined for pairs of parameters $\theta_1,\theta_2$, where $\theta_2$ is a nuisance parameter and the confidence set is constructed for a functional $\gamma(\theta_1)$. The following generalization does not require any nuisance parameters. Using partitions, it can be used both with and without nuisance parameters, as well as in non-parametric settings.}

\begin{quotation}
It will be very helpful to readers that the relationship between the modified Gleser--Hwang theorem and the numerical difficulty of Hedges’ selection model is clearly shown in numerical studies. If the current result should be supported by a numerical study, the key message of this paper becomes clear.
\end{quotation}

I appreciate this comment, as it should be made clear that the the difficulties with estimation are not universal, across all data sets. Estimation is difficult only if you're unlucky with the data you obtained. I slightly modified the abstract to make this clearer. More importantly, I added the following paragraph to the end of section 2:

{\color{red} Estimation of Hedges' model is especially hard when almost all observations lie close to the the cutoffs. In our experience, estimation works well when the data is sufficiently well spread, for instance when some observations are far away from the cutoffs and there are observations that have failed to reach significance. As a simple example of a case when estimation fails to work, consider the vector $x = (1.96, 1.96, 1.96, 1.96, 1.96, 1.64, 1.64, 1.64, 1.64, 1.64, -1)$ and the standard deviation of each observations is $\sigma_i=1$. We employ $\alpha = (0, 0.025, 0.05, 1)$, which implies cutoffs at $\Phi^{-1}(0.975)$ and $\Phi^{-1}(0.95)$. In this case, $10$ out of $11$ observations are very close to the cutoffs. When we run the Hedges selection model on this data, using the$\mathtt{sel}$ function of the $\mathtt{R}$ package $\mathtt{metafor}$ (Vichtbauer, 2010), the model does not converge. If the last observation is changed to $0$ instead of $-1$, the model converges, but the Hessian cannot be inverted, and the parameter estimate for $\theta_0$ equals $-1.8$. Situations similar to this one are most common when $n$ is small.}

(Of course, confidence sets are defined using universal quantification, and must take unlucky cases into account. The point of this paper is that confidence sets will be infinite \textit{if you're sufficiently unlucky}, no matter what the true parameter estimates are.)
\end{document}

### 2022-10-02 response_2.tex

\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\title{Response to reviewer 2 on infinite CI}
\begin{document}
\maketitle
I wish to thank you for your very constructive review.

Major modifications to the manuscript are marked in red and copied into this document. There might be very slight (one the level of spelling error) deviations between the red blocks in this response document and the corresponding blocks in the manuscript.

\section*{Spelling and minor comments}Thank you for informing me about these. They have been fixed.

\section*{Response to comments}

\begin{quote}
Could you clarify the motivation to focus on the step function defined
in (2.3)? As for the selection function w(·) defined in (2.2), there are
many options such as one-parameter selection function (Preston et al.
2004) and two-parameters selection function (Copas, 2013). Is it more
popular or just for some theoretical reason?
\end{quote}

That is a good questions! There is no reason to believe the results hold for the other selection models. I added the following paragraph to section 2:

{\color{red}It is not probably not possible to generalize the results of this paper to selection models that do no follow the step function model. Lemma 5, about the truncated normal, is crucial in the proof of our main result, Theorem 8. Such truncated functions only appear in step function models, not models with continuous selection functions, such as the Probit selection function of Copas (2013) or the one-parameter selection functions of Preston (2014).}

\begin{quote}
How can we decide $\mu$, $\alpha$ and $K$ defined in (2.3)? I feel that determining the values without data is very subjective.
\end{quote}

Only the values of $\alpha$ will have to be supplied by the researcher, as we estimate $\rho$ along with $\mu$ and $\tau$. We believe the most reasonable choice is $\alpha = 1, 0.05, 0.025$, which implies $K=3$. (In this paper, it's entirely possible to estimate $\alpha$ as well, if $K$ is known or estimated itself. That would not change the main message, that confidence intervals are infinitely large with positive probability. I don't think that such models are common enough to warrant an explicit mention though.)

I added the following paragraph to clarify:

{\color{red}In applications, the parameters $\mu$, $\tau$, and $\rho$ are estimated from the data, while $\alpha$ is fixed by the researcher, for instance at $\alpha = (0.025, 0.05, 1)$. We recommend using these cutoffs, as it is well known that applied journals frequently demand statistical significance at this level. Since both two-sided and one-sided p-values occur, we need to include $0.025$ in addition to $0.05$.}

\begin{quote}
In section 3, I would like the author to add a more detailed explanation of why partition $\Pi$ is necessary. For example, what is $\Pi$ in Example 2? What are the benefits of introducing $\Pi$ in the example?
\end{quote}

This comment addresses an important point! There are other ways to present our results than using partitions. A common way is to use nuisance parameters, but I prefer to avoid this approach, as it suggests that:
\begin{enumerate}
\item Unambiguous nuisance parameters exist. That isn't the case in this problem, as we may be interested in either the mean $\mu$, the heterogeneity parameter $\tau$, or $\mu$ and $\tau$  together. 
\item The Theorem is restricted to parametric distributions. This paper is about Hedges publication bias model, but Theorem 4 can be applied to other problems too, including non-parametric problems. 
\item The notion becomes more involved if we use nuisance parameters.
\end{enumerate}
To motivate the usage of partitions instead of nuisance parameters, I added the following immediately after introducing partitions.

{\color{red} Instead of partitions, we could have used a formulation with main parameters $\theta$ and nuisance parameters $\eta$, and defined the rejection set for $\theta$ as $\sup_{\eta}\sup_{\theta}P_{\theta,\eta}(R(\theta))\leq\alpha$. We have decided to use partitions for two reasons: First, there are no unambiguous nuisance and main parameters in our applications, making notation using nuisance parameters confusing. Second, the upcoming Theorem 8 can be applied in purely non-parametric situations, where the mention of nuisance and main parameters is even more confusing.}

In addition, I added {\color{red} The \emph{t}-confidence interval is an exact confidence interval for $\mu$ no matter what $\sigma>0$, the nuisance parameter, is. Since the test is exact, rejection sets $R(\mu)$ satisfy $P^n_{\mu,\sigma}(R(\mu))=\alpha$ for all $\sigma,\mu$.} to Example 2, along with an explicit mention that {\color{red} $\Pi = \{\pi(\mu)\},\mu\in\mathbb{R}$.}
\end{document}
